### 2021-03-17 My-Papers/SpecHunter/paper.tex
paper!

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
% \documentclass[acmsmall]{acmart}\settopmatter{}

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2018}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
% \setcopyright{acmcopyright}
% \setcopyright{acmlicensed}
% \setcopyright{rightsretained}
% \copyrightyear{2018}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
\citestyle{acmauthoryear}   %% For author/year citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format must update the '\documentclass' and
%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
%% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%% http://ctan.org/pkg/subcaption

\begin{document}

%% Title information
\title{SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net}        
%% when present, will be used in
%% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'
\subtitle{Subtitle}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{First1 Last1}
\authornote{with author1 note}          %% \authornote is optional;
%% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position1}
  \department{Department1}              %% \department is recommended
  \institution{Institution1}            %% \institution is required
  \streetaddress{Street1 Address1}
  \city{City1}
  \state{State1}
  \postcode{Post-Code1}
  \country{Country1}                    %% \country is recommended
}
\email{first1.last1@inst1.edu}          %% \email is recommended

%% Author with two affiliations and emails.
% \author{First2 Last2}
% \authornote{with author2 note}          %% \authornote is optional;
%                                         %% can be repeated if necessary
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
% \affiliation{
% \position{Position2a}
% \department{Department2a}             %% \department is recommended
% \institution{Institution2a}           %% \institution is required
% \streetaddress{Street2a Address2a}
% \city{City2a}
% \state{State2a}
% \postcode{Post-Code2a}
% \country{Country2a}                   %% \country is recommended
% }
%   \email{first2.last2@inst2a.com}         %% \email is recommended
%   \affiliation{
%   \position{Position2b}
%   \department{Department2b}             %% \department is recommended
%   \institution{Institution2b}           %% \institution is required
%   \streetaddress{Street3b Address2b}
%   \city{City2b}
%   \state{State2b}
%   \postcode{Post-Code2b}
%   \country{Country2b}                   %% \country is recommended
% }
%   \email{first2.last2@inst2b.org}         %% \email is recommended

%%   Abstract
%%   Note: \begin{abstract}...\end{abstract} environment must come
%%   before \maketitle command
\begin{abstract}
  % Taint analysis becomes a must for Java projects where foreign codes such as
  % external frameworks are frequently used in building them.
  % % Taint specification 추론이 왜 필요한지
  % For accurate taint analysis, the analyzer must first be told which methods are
  % sources, sinks, sanitizers, or none of them. However, Manually determining such
  % labels for every method used or defined in a project is a tedious task that
  % becomes nearly impossible if the codebase becomes large.
  % % 그러므로 우리의 아이디어를 제시한다
  % To alleviate such burden, we present Spechunter which, given a small
  % portion of the entire methods which are not deadcodes, finds out taint specifications
  % of the rest of the methods in a Java project built with frameworks.
  % % 우리 아이디어의 특징
  % Spechunter's uniqueness lies in its efficiency, achieved by only
  % drawing minimum manpower necessary for doing its job. This is possible due to its
  % interactive nature: it ends an ongoing interaction as soon as it determines that enough
  % evidence is obtained from the oracle. To achieve this, Spechunter relies on
  % building Bayesian networks and performing marginal inference on it given accumulating
  % evidence. Our experiments show that ...

  % 위의 버전은 영양가도 없으면서 너무 장황하다. Lets give it a full rewrite!

  SpecHunter is a tool for inferring taint specifications, aiming to serve any
  Java taint analyzers, enabling them to be more precise in finding out data
  flows from a source method to a sink method, without passing through a
  sanitizer. By asking questions to an external oracle on selected APIs used in
  a given Java application, it can acheive the following two goals. First,
  SpecHunter is language-agnostic, since it only focuses on the Java application at
  hand, and ignores whether or not the used APIs are implemented in languages
  other than Java. Therefore, it can be used for any Java application, regardless
  of what libraries or frameworks they use. Second, SpecHunter is
  efficient, because the APIs necessary for efficient propagation is automatically selected
  by SpecHunter itself. This allows the user to skip all trial-and-error in
  configurating the training set for a learning model, as required by previous
  machine learning approaches. Results of our experiments show that SpecHunter
  actually delivers the aforementioned promises, by running on applications with
  Scala and C++ libraries, with only questions asked to the user.  
\end{abstract}

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10011007.10011006.10011008</concept_id>
  <concept_desc>Software and its engineering~General programming languages</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003457.10003521.10003525</concept_id>
  <concept_desc>Social and professional topics~History of programming languages</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

\section{Introduction}
% A large portion of Java projects are built using frameworks such as Spring,
% Hibernate, or Android. These frameworks are foreign codes, so importing their
% APIs may introduce new security vulnerabilities. Finding out such security holes
% requires running taint analysis, which looks for a data flow starting from a
% source method to a sink method without passing through a sanitizer method.
% However, taint analyzers should be correctly told which method is a source,
% sink, sanitizer, or none of them at the first place, otherwise it may result in
% false negatives or false positives. However, manually labelling all methods used
% or defined in a project with the above four labels is a laborous task to be
% manually done, and becomes nearly impossible to do so if the codebase gets
% larger. Therefore, there have been previous works to lessen this burden.

% 2021-02-15 16:44:59에 다시 쓴 버전:

Taint analysis, whether static or dynamic, aims to find security vulnerabilities lurking
in the given program. These vulnerabilities include SQL injection, cross-site
scripting, and abused printf-arguments. They are typically formulated as a
data flow starting from a `source' method to a `sink' method, without the
flowing data being `sanitized' by an appropriate method. For such search to be
precise enough, the analyzer must first be told which methods are sources,
sinks, sanitizers, or none of them. However, going through the codebase
searching for imported APIs and labelling every one of them by hand becomes too
time-consuming as the codebase gets larger.

% TODO BibTeX을 쓸 줄 모르므로 일단 툴 이름으로 Reference로의 링크를 대신함
% Boldface들을 BibTeX으로 바꿀 것.
To aid such manpower, previous studies proposed methods such as supervised
learning (\textbf{SuSI}, \textbf{SWAN}), and semi-supervised learning (\textbf{Seldon}, \textbf{Merlin}).
However, works belonging to each camp suffers from their own limitations.

\paragraph{Shortcomings of Supervised Learning Camp.}

\textbf{SuSI} and \textbf{SWAN} both work in a similar way: they first train a learning model
such as a support vector machine with the actual library codes implementing
APIs. Here, the function bodies are interprocedurally analyzed with a Java
static analyzer to get the vectors of feature values. Then, they take a whole
library codebase into the pre-trained learning
model, and get the mapping from all APIs in the library to their respective
specifications. While they work nice against libraries written in pure Java
code such as Spring, they cannot work if a given application imports libraries
written in other languages other than Java. This is because in order to extract
the feature values they would have to be equipped with all the possible
languages the libraries would be in, and this is practically difficult.

% TODO: add an additional shortcoming: features should also be updated if a new
% library is provided

\paragraph{Shortcomings of Semi-Supervised Learning Camp.}

As a workaround to the above limitation, one can try a semi-supervised learning
approach. The state-of-the-art belonging to this camp is \textbf{Seldon}.
\textbf{Seldon} only takes the application code into consideration, thus it does
not care which language the library is written in. So, for example, Seldon can
figure out the label of an API function in a Python program, which is
actually implemented in C++. However, Seldon suffers from a common problem of
all machine-learning solutions, that it is largely dependent on quality dataset.
In fact, the authors reports that \textbf{Seldon}'s precision dropped by 14
percent-points by just providing half of the original specifications. Moreover,
this problem is shared with supervised learning solutions, those are also
data-driven solutions.
% Seldon 논문의 부분을 인용하고 싶은데... 형식을 모르겠네
% 해당 부분:
% Q6: Impact of Seed Specification. We also evaluated Sel-
% don’s precision for half the seed specification (considering
% only odd line numbers in App. B). This significantly reduces
% precision, by 14 percentage-points. Thus, we believe our
% seed specification strikes a good balance between manual
% effort and precision. We note that in the extreme case of an
% empty seed specification, Seldon will predict 0 specifications,
% because picking 0 for all variables is a trivial solution to its
% constraint system.

\paragraph{Our Tool: Real-Time Interactive Inference.}

Our tool, SpecHunter, works in a different manner than data-driven
approaches. Instead of training the model with some predetermined pairs of
methods and their labels to predict other methods' labels, we analyze the given
application to construct probabilistic graphical models of a certain type,
called Bayesian networks. They are special in that they provide a model of
conditional-probabilistic reasoning, which infers the marginal probabilities of
each random variables when some of them are instantiated to a certain value by
an external source. Therefore, we determine a structure of a Bayesian network by
running a static analysis on the given application code, and make the system ask
the user, the external entity, for evidence. Then, SpecHunter picks the most
influential node which has the most other nodes that depend upon it. This makes
the interaction session both effective and efficient.

The experiments show that ...   % TODO

\paragraph{Contributions.}

- We provide SpecHunter
- We provide src/sin/san/non ground truths
- We provide a taint analyzer (is it possible?)
- We make the tool open source (is it possible?)

\section{Overview}

\paragraph{Motivation}

Swan sucks: too much variance on its performance

\paragraph{Overview of our System}

\paragraph{Static Analysis}

\paragraph{Constructing Bayesian Networks}

\section{Evaluation}

\paragraph{Discussions}

\paragraph{Limitations}

\section{Related Work}

\section{Conclusion}

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
  %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}. Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

%% Bibliography
% \bibliography{bibfile}

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

\end{document}

### 2021-04-01 My-Papers/SpecHunter/paper.tex
Outlines and code example

@@
 %% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
-\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
+\documentclass[sigconf,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
 %% For double-blind review submission, w/ CCS and ACM Reference
@@
 %% http://ctan.org/pkg/subcaption
+
+\usepackage{listing}
 
@@
 \begin{abstract}
-  % Taint analysis becomes a must for Java projects where foreign codes such as
-  % external frameworks are frequently used in building them.
-  % % Taint specification 추론이 왜 필요한지
-  % For accurate taint analysis, the analyzer must first be told which methods are
-  % sources, sinks, sanitizers, or none of them. However, Manually determining such
-  % labels for every method used or defined in a project is a tedious task that
-  % becomes nearly impossible if the codebase becomes large.
-  % % 그러므로 우리의 아이디어를 제시한다
-  % To alleviate such burden, we present Spechunter which, given a small
-  % portion of the entire methods which are not deadcodes, finds out taint specifications
-  % of the rest of the methods in a Java project built with frameworks.
-  % % 우리 아이디어의 특징
-  % Spechunter's uniqueness lies in its efficiency, achieved by only
-  % drawing minimum manpower necessary for doing its job. This is possible due to its
-  % interactive nature: it ends an ongoing interaction as soon as it determines that enough
-  % evidence is obtained from the oracle. To achieve this, Spechunter relies on
-  % building Bayesian networks and performing marginal inference on it given accumulating
-  % evidence. Our experiments show that ...
-
-  % 위의 버전은 영양가도 없으면서 너무 장황하다. Lets give it a full rewrite!
-
-  SpecHunter is a tool for inferring taint specifications, aiming to serve any
-  Java taint analyzers, enabling them to be more precise in finding out data
-  flows from a source method to a sink method, without passing through a
-  sanitizer. By asking questions to an external oracle on selected APIs used in
-  a given Java application, it can acheive the following two goals. First,
-  SpecHunter is language-agnostic, since it only focuses on the Java application at
-  hand, and ignores whether or not the used APIs are implemented in languages
-  other than Java. Therefore, it can be used for any Java application, regardless
-  of what libraries or frameworks they use. Second, SpecHunter is
-  efficient, because the APIs necessary for efficient propagation is automatically selected
-  by SpecHunter itself. This allows the user to skip all trial-and-error in
-  configurating the training set for a learning model, as required by previous
-  machine learning approaches. Results of our experiments show that SpecHunter
-  actually delivers the aforementioned promises, by running on applications with
-  Scala and C++ libraries, with only questions asked to the user.  
+  SpecHunter is a tool for inferring taint specifications, aiming to aid anyone
+  trying to use a Java taint analyzer, but being overwhelmed by the number of APIs that
+  should be marked of their specifications to run it. SpecHunter aims to lessen this burden
+  by constructing a Bayesian network and performing live interaction with the user, in which
+  it systematically picks a method and asks the user of its specification. By taking an
+  interactive approach, SpecHunter can run on Java applications that use libraries that are
+  implemented in languages other than Java. Also, SpecHunter skips all trial-and-errors
+  in configurating the data-set required in using any of the traditional machine-learning approaches.
+  Our experiments show that SpecHunter actually delivers those promises.
 \end{abstract}
@@
 \section{Introduction}
-% A large portion of Java projects are built using frameworks such as Spring,
-% Hibernate, or Android. These frameworks are foreign codes, so importing their
-% APIs may introduce new security vulnerabilities. Finding out such security holes
-% requires running taint analysis, which looks for a data flow starting from a
-% source method to a sink method without passing through a sanitizer method.
-% However, taint analyzers should be correctly told which method is a source,
-% sink, sanitizer, or none of them at the first place, otherwise it may result in
-% false negatives or false positives. However, manually labelling all methods used
-% or defined in a project with the above four labels is a laborous task to be
-% manually done, and becomes nearly impossible to do so if the codebase gets
-% larger. Therefore, there have been previous works to lessen this burden.
-
-% 2021-02-15 16:44:59에 다시 쓴 버전:
-
 Taint analysis, whether static or dynamic, aims to find security vulnerabilities lurking
@@
 data flow starting from a `source' method to a `sink' method, without the
-flowing data being `sanitized' by an appropriate method. For such search to be
+flowing data being `sanitized' by a relevant method. For such search to be
 precise enough, the analyzer must first be told which methods are sources,
 sinks, sanitizers, or none of them. However, going through the codebase
-searching for imported APIs and labelling every one of them by hand becomes too
-time-consuming as the codebase gets larger.
+searching for imported APIs and labelling every one of them by hand quickly becomes tedious
+thing to do as the codebase gets larger.
 
@@
 model, and get the mapping from all APIs in the library to their respective
-specifications. While they work nice against libraries written in pure Java
+specifications. While they work nicely against libraries written in pure Java
 code such as Spring, they cannot work if a given application imports libraries
@@
 each random variables when some of them are instantiated to a certain value by
-an external source. Therefore, we determine a structure of a Bayesian network by
-running a static analysis on the given application code, and make the system ask
+an external source. Therefore, we first determine a structure of a Bayesian network
+by running a static analysis on the given application code, and make the system ask
 the user, the external entity, for evidence. Then, SpecHunter picks the most
-influential node which has the most other nodes that depend upon it. This makes
-the interaction session both effective and efficient.
+influential node which has the most dependent nodes. This makes the interaction
+session both effective and efficient.
 
-The experiments show that ...   % TODO
+The experiments show that SpecHunter effectively infers taint specifications for
+methods that are untold of its label, with \textbf{xx}\% precision when told only
+\textbf{17.7}\% of all APIs.
 
@@
 
-- We provide SpecHunter
-- We provide src/sin/san/non ground truths
-- We provide a taint analyzer (is it possible?)
-- We make the tool open source (is it possible?)
+\begin{itemize}
+  \item We provide SpecHunter
+  \item We provide src/sin/san/non ground truths
+  \item We provide a taint analyzer (is it possible?)
+  \item We make the tool open source (is it possible?)
+\end{itemize}
 
@@
 
-Swan sucks: too much variance on its performance
+Swan sucks: too much variance on its performance depending on dataset quality/quantity
 
-\paragraph{Overview of our System}
+\subsection{Overview of our System}
 
-\paragraph{Static Analysis}
+% 적당한 figure 하나 넣자
 
-\paragraph{Constructing Bayesian Networks}
+Figure 1 shows the overall workflow of SpecHunter. Given a Java application's
+source code, SpecHunter labels all API methods provided by the library the application
+uses. There are three main issues regarding building an effective interactive system:
+namely, constructing the network, effectively propagating the evidence given from the
+oracle, and making the system scale to run on large input applications.
+% Question: Should we define what "API" means?
+
+\subsection{Network Construction}
+
+% Network Construction은 반드시 Scalability and Efficiency와 연관되게 되어 있다.
+% 그 점을 유념하면서 쓰자: 적절한 pointer 달아 주기.
+Here we describe how we represent the input java project into a graph form, which will
+later be turned into a series of Bayesian networks. We hope to create a graph G=(V, E),
+where V is the set of all methods used or defined in the given application, and E is a
+subset of V * V, whose elements are gathered in three different ways.
+
+First, there are data-flow-edges. We perform a variant of a data-flow analysis on the
+given input application to calculate lifetimes of all access paths found in the entire code.
+% 여기서 간단한 예제 넣어주기
+
+\begin{figure}[t]
+  \begin{lstlisting}
+
+    public int m1() {
+      return 1;
+    }
+
+    public int m2(int u1) {
+      return ++u1;
+    }
+
+    public void m3(int u2) {
+      System.out.println(u2);
+    }
+
+    public void f() {
+      int x = m1();
+      g(x);
+    }
+
+    public void g(int y) {
+      int z = m2(y);
+      h(z);
+    }
+
+    public void h(int w) {
+      m3(w);
+    }
+
+  \end{lstlisting}
+\caption{Example Java program with a data flow.}
+vspace{-0.6em}
+\label{fig:sca}
+\end{figure}
+
+Second, there are call-edges.
+
+Last but not least, there are similarity-edges.
+
+\subsection{Graph Splitting}
+
+\subsection{Information Propagation}
 
@@
 
+\subsection{RQs}
+\begin{itemize}
+  \item How effective is SH in finding src/sin/san?  % I am really really worried about this
+  \item How efficient is SH?
+  \item Interaction user-study % possible?
+\end{itemize}
+
+% why is this meaningful? (with/without comparison)
+% at least mention comparison
+
 \paragraph{Discussions}
+How well are propagations working? (Quant, Qualit) .
+How stable is SpecHunter over multiple iterations?
+\paragraph{Limitations}
 
-\paragraph{Limitations}
+\paragraph{Threats to Validity.}
 

### 2021-04-03 My-Papers/SpecHunter/paper.tex
checkpoint

@@
 
-\usepackage{listing}
+\usepackage{listings}
+
+\lstset{
+  language=Java,
+  numbers=left,
+  stepnumber=1,
+  firstnumber=1,
+  numberfirstline=true
+}
 
@@
 
-\subsection{Network Construction}
+\subsubsection{Network Construction}
+
+\paragraph{Determining Edges}
 
@@
 % 그 점을 유념하면서 쓰자: 적절한 pointer 달아 주기.
-Here we describe how we represent the input java project into a graph form, which will
-later be turned into a series of Bayesian networks. We hope to create a graph G=(V, E),
-where V is the set of all methods used or defined in the given application, and E is a
-subset of V * V, whose elements are gathered in three different ways.
+Here we describe how we represent the input java project into a large graph form, which will
+later be turned into a series of Bayesian networks. How we splitt this large
+graph into several Bayesian networks will be discussed in the next section. % TODO 좀 더 자연스러운 포인터??
+We hope to create a graph $G=(V, E)$,
+where $V$ is the set of all methods used or defined in the given application, and $E$ is a
+subset of $V\times V$, whose elements are gathered in three different ways.
 
 First, there are data-flow-edges. We perform a variant of a data-flow analysis on the
-given input application to calculate lifetimes of all access paths found in the entire code.
+given input application to calculate lifetimes of all access paths found in the
+entire codes, starting from being defined and ending by being ``dead'', between
+which the access path may be ``redefined''.
 % 여기서 간단한 예제 넣어주기
 
-\begin{figure}[t]
-  \begin{lstlisting}
+\lstinputlisting[language=Java]{./Codes/SimpleExample.java}
 
-    public int m1() {
-      return 1;
-    }
+In the above example, a variable \texttt{x} is being defined to hold the value \texttt{1} in the method
+\texttt{f}, using another method \texttt{m1}. This value flows to \texttt{g}, where this
+value is redefined as \texttt{2} using the method \texttt{m2}. After this redefined
+value flows to method \texttt{m3} via \texttt{h}, it is no longer used after the call to
+\texttt{println}. Here, our goal is to capture this lifecycle. To compute these
+for all access paths in the program, we first run a static analysis designed as follows:
 
-    public int m2(int u1) {
-      return ++u1;
-    }
+% 무슨 environment를 써야 하나...? 일단 적어보쟈
 
-    public void m3(int u2) {
-      System.out.println(u2);
-    }
+\begin{align*}
+  A\in \mathbb{D} = \mathbb{C}\rightarrow\mathcal{P}(State)\\
+  s\in State = Procname\times Var\times Loc\times Alias\\
+  p\in Procname \subseteq Var\\
+  a\in Alias \subseteq \mathcal{P}(Var)
+\end{align*}
 
-    public void f() {
-      int x = m1();
-      g(x);
-    }
+For example, for an assignment statement \texttt{int a = b;} inside a procedure
+\texttt{f} at line 3, we obtain the tuple set \texttt{\{(f, a, 3, \{a, b\})\}}.
+The fourth component of the tuple means that \texttt{a} and \texttt{b} are
+aliases. After we create such tuples for each program point, we finally construct
+\emph{propagation chains} by threading the tuples via alias relations. The
+relevant generated tuples for our goal is:
 
-    public void g(int y) {
-      int z = m2(y);
-      h(z);
-    }
+\begin{itemize}
 
-    public void h(int w) {
-      m3(w);
-    }
+\item \texttt{\{(f, x, 14, \{x, y\})\}}
+\item \texttt{\{(g, y, 18, \{y, u1\})\}}
+\item \texttt{\{(m2, u1, 5, \{u1\})\}}
+\item \texttt{\{(m2, u1, 6, \{u1\})\}}
+\item \texttt{\{(g, z, 6, \{z, u1, w\})\}}
+\item \texttt{\{(g, w, 23, \{w, u2\})\}}
+\item \texttt{\{(m3, u2, 9, \{u2, println_1\})\}}
 
-  \end{lstlisting}
-\caption{Example Java program with a data flow.}
-vspace{-0.6em}
-\label{fig:sca}
-\end{figure}
+\end{itemize}
 
-Second, there are call-edges.
+where \texttt{println_1} is a Mangled parameter variable of \texttt{println}.
+Now, connecting the tuples with the aliases, we get two chains: \texttt{x -> y
+  -> u1} and \texttt{u1 -> z -> w -> u2 -> println_1}. Since \texttt{u1} is
+redefined in \texttt{m2}, we glue the two together to get the originally desired
+information: \texttt{x -> y -> u1 -> z -> w -> u2 -> println_1}. This translates
+into data-flow edges: \texttt{(f, g)}, \texttt{(f, h)}, and \texttt{(m3, println)}.
 
-Last but not least, there are similarity-edges.
+% 아 이거 실제로 돌려봐서 확인해야 할 거 같은뎅.. 실제로 이렇게 나오나...?
 
-\subsection{Graph Splitting}
+% TODO static callee가 무엇인지를 좀 알아와서 디테일을 추가할 것.
+Second, there are call-edges. Since we used Facebook's Infer (fbinfer.com/) to
+implement our static analysis, we used Infer's facility to compute static
+callees of a given method to draw the entire callgraph of a given application
+code. For each caller \texttt{f} and its callee \texttt{g}, we add an edge
+\texttt{(f, g)}.
 
-\subsection{Information Propagation}
+Last but not least, there are similarity-edges. The idea is to take any two
+methods and score its pairwise similarity, and leave only the pairs with score
+above a predefined threshold.
+% TODO syntactic, semantic feature 표 넣기
+
+\paragraph{Determining CPTs}
+
+% 여기서는 표를 좀 빡시게 그려야 한다. 셀도 좀 색칠하고...
+
+\subsubsection{Graph Splitting}
+
+\subsubsection{Information Propagation}
 
@@
 
-\paragraph{Threats to Validity.}
+\paragraph{Threats to Validity}
 

### 2021-04-04 My-Papers/SpecHunter/paper.tex
add similarity edges detail

@@
 
-% 무슨 environment를 써야 하나...? 일단 적어보쟈
-
 \begin{align*}
-  A\in \mathbb{D} = \mathbb{C}\rightarrow\mathcal{P}(State)\\
-  s\in State = Procname\times Var\times Loc\times Alias\\
-  p\in Procname \subseteq Var\\
-  a\in Alias \subseteq \mathcal{P}(Var)
+  A &\in \mathbb{D} &= \mathbb{C}\rightarrow\mathcal{P}(State)\\
+  s &\in State &= Procname\times Var\times Loc\times Alias\\
+  p &\in Procname &\subseteq Var\\
+  a &\in Alias &\subseteq \mathcal{P}(Var)
 \end{align*}
@@
 \begin{itemize}
-
 \item \texttt{\{(f, x, 14, \{x, y\})\}}
@@
 \item \texttt{\{(g, w, 23, \{w, u2\})\}}
-\item \texttt{\{(m3, u2, 9, \{u2, println_1\})\}}
-
+\item \texttt{\{(m3, u2, 9, \{u2, println\_1\})\}}
 \end{itemize}
 
-where \texttt{println_1} is a Mangled parameter variable of \texttt{println}.
-Now, connecting the tuples with the aliases, we get two chains: \texttt{x -> y
-  -> u1} and \texttt{u1 -> z -> w -> u2 -> println_1}. Since \texttt{u1} is
+>
+where \texttt{println\_1} is a Mangled parameter variable of \texttt{println}.
+Now, connecting the tuples with the aliases, we get two chains:
+\texttt{x -> y -> u1} and \texttt{u1 -> z -> w -> u2 -> println\_1}. Since \texttt{u1} is
 redefined in \texttt{m2}, we glue the two together to get the originally desired
-information: \texttt{x -> y -> u1 -> z -> w -> u2 -> println_1}. This translates
+information: \texttt{x -> y -> u1 -> z -> w -> u2 -> println\_1}. This translates
 into data-flow edges: \texttt{(f, g)}, \texttt{(f, h)}, and \texttt{(m3, println)}.
 
-% 아 이거 실제로 돌려봐서 확인해야 할 거 같은뎅.. 실제로 이렇게 나오나...?
+% TODO 아 이거 실제로 돌려봐서 확인해야 할 거 같은뎅.. 실제로 이렇게 나오나...?
 
@@
 methods and score its pairwise similarity, and leave only the pairs with score
-above a predefined threshold.
-% TODO syntactic, semantic feature 표 넣기
+above a predefined threshold. We measure them against two large groups of
+criteria: the ``syntactic features'' and ``semantic features''. For the
+syntactic features, we borrrowed largely from \textbf{Swan}'s features that
+check how names of methods or their return types are composed. The below
+figure % TODO: Figure 번호 달기...
+shows all the features we used.
+
+% TODO 표 삐져나간다..!!!!
+\begin{center}
+  \begin{tabular} { |c|c|c| }
+    \hline
+    Syntactic & Semantic\\
+    \hline
+    \hline
+    Both has parameters? & Both has at least one same callee?\\
+    Both has return type? & Both are making calls but not passing data?\\
+    Both contains same word in method name? & Both are being called but not being passed data?\\
+    Both contains same word in class name? & Both are making data flow calls?\\
+    Both has return type contained in parameter type? & Both are being passed data and passing data simultaneously?\\
+    Both has same return type? & Both are being passed data which gets dead in them?\\
+    Both has return type contained in method name? & Both has variable redefinitions?\\
+    \hline
+  \end{tabular}
+\end{center}
 

### 2021-04-04 My-Papers/SpecHunter/introduction.tex
separate subsubsections

--- 2021-04-01 My-Papers/SpecHunter/paper.tex
@@
-%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
-\documentclass[sigconf,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For double-blind review submission, w/ CCS and ACM Reference
-% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
-%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
-% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For single-blind review submission, w/ CCS and ACM Reference
-% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
-%% For final camera-ready submission, w/ required CCS and ACM Reference
-% \documentclass[acmsmall]{acmart}\settopmatter{}
-
-%% Journal information
-%% Supplied to authors by publisher for camera-ready submission;
-%% use defaults for review submission.
-\acmJournal{PACMPL}
-\acmVolume{1}
-\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
-\acmArticle{1}
-\acmYear{2018}
-\acmMonth{1}
-\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
-\startPage{1}
-
-%% Copyright information
-%% Supplied to authors (based on authors' rights management selection;
-%% see authors.acm.org) by publisher for camera-ready submission;
-%% use 'none' for review submission.
-\setcopyright{none}
-% \setcopyright{acmcopyright}
-% \setcopyright{acmlicensed}
-% \setcopyright{rightsretained}
-% \copyrightyear{2018}           %% If different from \acmYear
-
-%% Bibliography style
-\bibliographystyle{ACM-Reference-Format}
-%% Citation style
-%% Note: author/year citations are required for papers published as an
-%% issue of PACMPL.
-\citestyle{acmauthoryear}   %% For author/year citations
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%% Note: Authors migrating a paper from PACMPL format to traditional
-%% SIGPLAN proceedings format must update the '\documentclass' and
-%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Some recommended packages.
-\usepackage{booktabs}   %% For formal tables:
-%% http://ctan.org/pkg/booktabs
-\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
-%% http://ctan.org/pkg/subcaption
-
-\usepackage{listing}
-
-\begin{document}
-
-%% Title information
-\title{SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net}        
-%% when present, will be used in
-%% header instead of Full Title.
-\titlenote{with title note}             %% \titlenote is optional;
-%% can be repeated if necessary;
-%% contents suppressed with 'anonymous'
-\subtitle{Subtitle}                     %% \subtitle is optional
-\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
-%% can be repeated if necessary;
-%% contents suppressed with 'anonymous'
-
-%% Author information
-%% Contents and number of authors suppressed with 'anonymous'.
-%% Each author should be introduced by \author, followed by
-%% \authornote (optional), \orcid (optional), \affiliation, and
-%% \email.
-%% An author may have multiple affiliations and/or emails; repeat the
-%% appropriate command.
-%% Many elements are not rendered, but should be provided for metadata
-%% extraction tools.
-
-%% Author with single affiliation.
-\author{First1 Last1}
-\authornote{with author1 note}          %% \authornote is optional;
-%% can be repeated if necessary
-\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-\affiliation{
-  \position{Position1}
-  \department{Department1}              %% \department is recommended
-  \institution{Institution1}            %% \institution is required
-  \streetaddress{Street1 Address1}
-  \city{City1}
-  \state{State1}
-  \postcode{Post-Code1}
-  \country{Country1}                    %% \country is recommended
-}
-\email{first1.last1@inst1.edu}          %% \email is recommended
-
-%% Author with two affiliations and emails.
-% \author{First2 Last2}
-% \authornote{with author2 note}          %% \authornote is optional;
-%                                         %% can be repeated if necessary
-% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-% \affiliation{
-% \position{Position2a}
-% \department{Department2a}             %% \department is recommended
-% \institution{Institution2a}           %% \institution is required
-% \streetaddress{Street2a Address2a}
-% \city{City2a}
-% \state{State2a}
-% \postcode{Post-Code2a}
-% \country{Country2a}                   %% \country is recommended
-% }
-%   \email{first2.last2@inst2a.com}         %% \email is recommended
-%   \affiliation{
-%   \position{Position2b}
-%   \department{Department2b}             %% \department is recommended
-%   \institution{Institution2b}           %% \institution is required
-%   \streetaddress{Street3b Address2b}
-%   \city{City2b}
-%   \state{State2b}
-%   \postcode{Post-Code2b}
-%   \country{Country2b}                   %% \country is recommended
-% }
-%   \email{first2.last2@inst2b.org}         %% \email is recommended
-
-%%   Abstract
-%%   Note: \begin{abstract}...\end{abstract} environment must come
-%%   before \maketitle command
-\begin{abstract}
-  SpecHunter is a tool for inferring taint specifications, aiming to aid anyone
-  trying to use a Java taint analyzer, but being overwhelmed by the number of APIs that
-  should be marked of their specifications to run it. SpecHunter aims to lessen this burden
-  by constructing a Bayesian network and performing live interaction with the user, in which
-  it systematically picks a method and asks the user of its specification. By taking an
-  interactive approach, SpecHunter can run on Java applications that use libraries that are
-  implemented in languages other than Java. Also, SpecHunter skips all trial-and-errors
-  in configurating the data-set required in using any of the traditional machine-learning approaches.
-  Our experiments show that SpecHunter actually delivers those promises.
-\end{abstract}
-
-%% 2012 ACM Computing Classification System (CSS) concepts
-%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
-\begin{CCSXML}
-  <ccs2012>
-  <concept>
-  <concept_id>10011007.10011006.10011008</concept_id>
-  <concept_desc>Software and its engineering~General programming languages</concept_desc>
-  <concept_significance>500</concept_significance>
-  </concept>
-  <concept>
-  <concept_id>10003456.10003457.10003521.10003525</concept_id>
-  <concept_desc>Social and professional topics~History of programming languages</concept_desc>
-  <concept_significance>300</concept_significance>
-  </concept>
-  </ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Software and its engineering~General programming languages}
-\ccsdesc[300]{Social and professional topics~History of programming languages}
-%% End of generated code
-
-%% Keywords
-%% comma separated list
-\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission
-
-%% \maketitle
-%% Note: \maketitle command must come after title commands, author
-%% commands, abstract environment, Computing Classification System
-%% environment and commands, and keywords command.
-\maketitle
-
 \section{Introduction}
@@
 \end{itemize}
-
-\section{Overview}
-
-\paragraph{Motivation}
-
-Swan sucks: too much variance on its performance depending on dataset quality/quantity
-
-\subsection{Overview of our System}
-
-% 적당한 figure 하나 넣자
-
-Figure 1 shows the overall workflow of SpecHunter. Given a Java application's
-source code, SpecHunter labels all API methods provided by the library the application
-uses. There are three main issues regarding building an effective interactive system:
-namely, constructing the network, effectively propagating the evidence given from the
-oracle, and making the system scale to run on large input applications.
-% Question: Should we define what "API" means?
-
-\subsection{Network Construction}
-
-% Network Construction은 반드시 Scalability and Efficiency와 연관되게 되어 있다.
-% 그 점을 유념하면서 쓰자: 적절한 pointer 달아 주기.
-Here we describe how we represent the input java project into a graph form, which will
-later be turned into a series of Bayesian networks. We hope to create a graph G=(V, E),
-where V is the set of all methods used or defined in the given application, and E is a
-subset of V * V, whose elements are gathered in three different ways.
-
-First, there are data-flow-edges. We perform a variant of a data-flow analysis on the
-given input application to calculate lifetimes of all access paths found in the entire code.
-% 여기서 간단한 예제 넣어주기
-
-\begin{figure}[t]
-  \begin{lstlisting}
-
-    public int m1() {
-      return 1;
-    }
-
-    public int m2(int u1) {
-      return ++u1;
-    }
-
-    public void m3(int u2) {
-      System.out.println(u2);
-    }
-
-    public void f() {
-      int x = m1();
-      g(x);
-    }
-
-    public void g(int y) {
-      int z = m2(y);
-      h(z);
-    }
-
-    public void h(int w) {
-      m3(w);
-    }
-
-  \end{lstlisting}
-\caption{Example Java program with a data flow.}
-vspace{-0.6em}
-\label{fig:sca}
-\end{figure}
-
-Second, there are call-edges.
-
-Last but not least, there are similarity-edges.
-
-\subsection{Graph Splitting}
-
-\subsection{Information Propagation}
-
-\section{Evaluation}
-
-\subsection{RQs}
-\begin{itemize}
-  \item How effective is SH in finding src/sin/san?  % I am really really worried about this
-  \item How efficient is SH?
-  \item Interaction user-study % possible?
-\end{itemize}
-
-% why is this meaningful? (with/without comparison)
-% at least mention comparison
-
-\paragraph{Discussions}
-How well are propagations working? (Quant, Qualit) .
-How stable is SpecHunter over multiple iterations?
-\paragraph{Limitations}
-
-\paragraph{Threats to Validity.}
-
-\section{Related Work}
-
-\section{Conclusion}
-
-%% Acknowledgments
-\begin{acks}                            %% acks environment is optional
-  %% contents suppressed with 'anonymous'
-  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
-  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
-  %% acknowledge financial support and will be used by metadata
-  %% extraction tools.
-  This material is based upon work supported by the
-  \grantsponsor{GS100000001}{National Science
-    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
-  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
-  No.~\grantnum{GS100000001}{mmmmmmm}. Any opinions, findings, and
-  conclusions or recommendations expressed in this material are those
-  of the author and do not necessarily reflect the views of the
-  National Science Foundation.
-\end{acks}
-
-%% Bibliography
-% \bibliography{bibfile}
-
-%% Appendix
-\appendix
-\section{Appendix}
-
-Text of appendix \ldots
-
-\end{document}

### 2021-04-04 My-Papers/SpecHunter/overview.tex
separate subsubsections

--- 2021-04-04 My-Papers/SpecHunter/paper.tex
@@
-%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
-\documentclass[sigconf,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For double-blind review submission, w/ CCS and ACM Reference
-% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
-%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
-% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For single-blind review submission, w/ CCS and ACM Reference
-% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
-%% For final camera-ready submission, w/ required CCS and ACM Reference
-% \documentclass[acmsmall]{acmart}\settopmatter{}
-
-%% Journal information
-%% Supplied to authors by publisher for camera-ready submission;
-%% use defaults for review submission.
-\acmJournal{PACMPL}
-\acmVolume{1}
-\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
-\acmArticle{1}
-\acmYear{2018}
-\acmMonth{1}
-\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
-\startPage{1}
-
-%% Copyright information
-%% Supplied to authors (based on authors' rights management selection;
-%% see authors.acm.org) by publisher for camera-ready submission;
-%% use 'none' for review submission.
-\setcopyright{none}
-% \setcopyright{acmcopyright}
-% \setcopyright{acmlicensed}
-% \setcopyright{rightsretained}
-% \copyrightyear{2018}           %% If different from \acmYear
-
-%% Bibliography style
-\bibliographystyle{ACM-Reference-Format}
-%% Citation style
-%% Note: author/year citations are required for papers published as an
-%% issue of PACMPL.
-\citestyle{acmauthoryear}   %% For author/year citations
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%% Note: Authors migrating a paper from PACMPL format to traditional
-%% SIGPLAN proceedings format must update the '\documentclass' and
-%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Some recommended packages.
-\usepackage{booktabs}   %% For formal tables:
-%% http://ctan.org/pkg/booktabs
-\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
-%% http://ctan.org/pkg/subcaption
-
-\usepackage{listings}
-
-\lstset{
-  language=Java,
-  numbers=left,
-  stepnumber=1,
-  firstnumber=1,
-  numberfirstline=true
-}
-
-\begin{document}
-
-%% Title information
-\title{SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net}        
-%% when present, will be used in
-%% header instead of Full Title.
-\titlenote{with title note}             %% \titlenote is optional;
-%% can be repeated if necessary;
-%% contents suppressed with 'anonymous'
-\subtitle{Subtitle}                     %% \subtitle is optional
-\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
-%% can be repeated if necessary;
-%% contents suppressed with 'anonymous'
-
-%% Author information
-%% Contents and number of authors suppressed with 'anonymous'.
-%% Each author should be introduced by \author, followed by
-%% \authornote (optional), \orcid (optional), \affiliation, and
-%% \email.
-%% An author may have multiple affiliations and/or emails; repeat the
-%% appropriate command.
-%% Many elements are not rendered, but should be provided for metadata
-%% extraction tools.
-
-%% Author with single affiliation.
-\author{First1 Last1}
-\authornote{with author1 note}          %% \authornote is optional;
-%% can be repeated if necessary
-\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-\affiliation{
-  \position{Position1}
-  \department{Department1}              %% \department is recommended
-  \institution{Institution1}            %% \institution is required
-  \streetaddress{Street1 Address1}
-  \city{City1}
-  \state{State1}
-  \postcode{Post-Code1}
-  \country{Country1}                    %% \country is recommended
-}
-\email{first1.last1@inst1.edu}          %% \email is recommended
-
-%% Author with two affiliations and emails.
-% \author{First2 Last2}
-% \authornote{with author2 note}          %% \authornote is optional;
-%                                         %% can be repeated if necessary
-% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-% \affiliation{
-% \position{Position2a}
-% \department{Department2a}             %% \department is recommended
-% \institution{Institution2a}           %% \institution is required
-% \streetaddress{Street2a Address2a}
-% \city{City2a}
-% \state{State2a}
-% \postcode{Post-Code2a}
-% \country{Country2a}                   %% \country is recommended
-% }
-%   \email{first2.last2@inst2a.com}         %% \email is recommended
-%   \affiliation{
-%   \position{Position2b}
-%   \department{Department2b}             %% \department is recommended
-%   \institution{Institution2b}           %% \institution is required
-%   \streetaddress{Street3b Address2b}
-%   \city{City2b}
-%   \state{State2b}
-%   \postcode{Post-Code2b}
-%   \country{Country2b}                   %% \country is recommended
-% }
-%   \email{first2.last2@inst2b.org}         %% \email is recommended
-
-%%   Abstract
-%%   Note: \begin{abstract}...\end{abstract} environment must come
-%%   before \maketitle command
-\begin{abstract}
-  SpecHunter is a tool for inferring taint specifications, aiming to aid anyone
-  trying to use a Java taint analyzer, but being overwhelmed by the number of APIs that
-  should be marked of their specifications to run it. SpecHunter aims to lessen this burden
-  by constructing a Bayesian network and performing live interaction with the user, in which
-  it systematically picks a method and asks the user of its specification. By taking an
-  interactive approach, SpecHunter can run on Java applications that use libraries that are
-  implemented in languages other than Java. Also, SpecHunter skips all trial-and-errors
-  in configurating the data-set required in using any of the traditional machine-learning approaches.
-  Our experiments show that SpecHunter actually delivers those promises.
-\end{abstract}
-
-%% 2012 ACM Computing Classification System (CSS) concepts
-%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
-\begin{CCSXML}
-  <ccs2012>
-  <concept>
-  <concept_id>10011007.10011006.10011008</concept_id>
-  <concept_desc>Software and its engineering~General programming languages</concept_desc>
-  <concept_significance>500</concept_significance>
-  </concept>
-  <concept>
-  <concept_id>10003456.10003457.10003521.10003525</concept_id>
-  <concept_desc>Social and professional topics~History of programming languages</concept_desc>
-  <concept_significance>300</concept_significance>
-  </concept>
-  </ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Software and its engineering~General programming languages}
-\ccsdesc[300]{Social and professional topics~History of programming languages}
-%% End of generated code
-
-%% Keywords
-%% comma separated list
-\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission
-
-%% \maketitle
-%% Note: \maketitle command must come after title commands, author
-%% commands, abstract environment, Computing Classification System
-%% environment and commands, and keywords command.
-\maketitle
-
-\section{Introduction}
-Taint analysis, whether static or dynamic, aims to find security vulnerabilities lurking
-in the given program. These vulnerabilities include SQL injection, cross-site
-scripting, and abused printf-arguments. They are typically formulated as a
-data flow starting from a `source' method to a `sink' method, without the
-flowing data being `sanitized' by a relevant method. For such search to be
-precise enough, the analyzer must first be told which methods are sources,
-sinks, sanitizers, or none of them. However, going through the codebase
-searching for imported APIs and labelling every one of them by hand quickly becomes tedious
-thing to do as the codebase gets larger.
-
-% TODO BibTeX을 쓸 줄 모르므로 일단 툴 이름으로 Reference로의 링크를 대신함
-% Boldface들을 BibTeX으로 바꿀 것.
-To aid such manpower, previous studies proposed methods such as supervised
-learning (\textbf{SuSI}, \textbf{SWAN}), and semi-supervised learning (\textbf{Seldon}, \textbf{Merlin}).
-However, works belonging to each camp suffers from their own limitations.
-
-\paragraph{Shortcomings of Supervised Learning Camp.}
-
-\textbf{SuSI} and \textbf{SWAN} both work in a similar way: they first train a learning model
-such as a support vector machine with the actual library codes implementing
-APIs. Here, the function bodies are interprocedurally analyzed with a Java
-static analyzer to get the vectors of feature values. Then, they take a whole
-library codebase into the pre-trained learning
-model, and get the mapping from all APIs in the library to their respective
-specifications. While they work nicely against libraries written in pure Java
-code such as Spring, they cannot work if a given application imports libraries
-written in other languages other than Java. This is because in order to extract
-the feature values they would have to be equipped with all the possible
-languages the libraries would be in, and this is practically difficult.
-
-% TODO: add an additional shortcoming: features should also be updated if a new
-% library is provided
-
-\paragraph{Shortcomings of Semi-Supervised Learning Camp.}
-
-As a workaround to the above limitation, one can try a semi-supervised learning
-approach. The state-of-the-art belonging to this camp is \textbf{Seldon}.
-\textbf{Seldon} only takes the application code into consideration, thus it does
-not care which language the library is written in. So, for example, Seldon can
-figure out the label of an API function in a Python program, which is
-actually implemented in C++. However, Seldon suffers from a common problem of
-all machine-learning solutions, that it is largely dependent on quality dataset.
-In fact, the authors reports that \textbf{Seldon}'s precision dropped by 14
-percent-points by just providing half of the original specifications. Moreover,
-this problem is shared with supervised learning solutions, those are also
-data-driven solutions.
-% Seldon 논문의 부분을 인용하고 싶은데... 형식을 모르겠네
-% 해당 부분:
-% Q6: Impact of Seed Specification. We also evaluated Sel-
-% don’s precision for half the seed specification (considering
-% only odd line numbers in App. B). This significantly reduces
-% precision, by 14 percentage-points. Thus, we believe our
-% seed specification strikes a good balance between manual
-% effort and precision. We note that in the extreme case of an
-% empty seed specification, Seldon will predict 0 specifications,
-% because picking 0 for all variables is a trivial solution to its
-% constraint system.
-
-\paragraph{Our Tool: Real-Time Interactive Inference.}
-
-Our tool, SpecHunter, works in a different manner than data-driven
-approaches. Instead of training the model with some predetermined pairs of
-methods and their labels to predict other methods' labels, we analyze the given
-application to construct probabilistic graphical models of a certain type,
-called Bayesian networks. They are special in that they provide a model of
-conditional-probabilistic reasoning, which infers the marginal probabilities of
-each random variables when some of them are instantiated to a certain value by
-an external source. Therefore, we first determine a structure of a Bayesian network
-by running a static analysis on the given application code, and make the system ask
-the user, the external entity, for evidence. Then, SpecHunter picks the most
-influential node which has the most dependent nodes. This makes the interaction
-session both effective and efficient.
-
-The experiments show that SpecHunter effectively infers taint specifications for
-methods that are untold of its label, with \textbf{xx}\% precision when told only
-\textbf{17.7}\% of all APIs.
-
-\paragraph{Contributions.}
-
-\begin{itemize}
-  \item We provide SpecHunter
-  \item We provide src/sin/san/non ground truths
-  \item We provide a taint analyzer (is it possible?)
-  \item We make the tool open source (is it possible?)
-\end{itemize}
-
 \section{Overview}
@@
 
-\subsubsection{Graph Splitting}
-
-\subsubsection{Information Propagation}
-
-\section{Evaluation}
-
-\subsection{RQs}
-\begin{itemize}
-\item How effective is SH in finding src/sin/san?  % I am really really worried about this
-\item How efficient is SH?
-\item Interaction user-study % possible?
-\end{itemize}
-
-% why is this meaningful? (with/without comparison)
-% at least mention comparison
-
-\paragraph{Discussions}
-How well are propagations working? (Quant, Qualit) .
-How stable is SpecHunter over multiple iterations?
-\paragraph{Limitations}
-
-\paragraph{Threats to Validity}
-
-\section{Related Work}
-
-\section{Conclusion}
-
-%% Acknowledgments
-\begin{acks}                            %% acks environment is optional
-  %% contents suppressed with 'anonymous'
-  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
-  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
-  %% acknowledge financial support and will be used by metadata
-  %% extraction tools.
-  This material is based upon work supported by the
-  \grantsponsor{GS100000001}{National Science
-    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
-  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
-  No.~\grantnum{GS100000001}{mmmmmmm}. Any opinions, findings, and
-  conclusions or recommendations expressed in this material are those
-  of the author and do not necessarily reflect the views of the
-  National Science Foundation.
-\end{acks}
-
-%% Bibliography
-% \bibliography{bibfile}
-
-%% Appendix
-\appendix
-\section{Appendix}
-
-Text of appendix \ldots
-
-\end{document}
+After we determine which and which methods should be connected with a directed
+edge, we then define a conditional probability table for each directed edge.

### 2021-04-04 My-Papers/SpecHunter/overview.tex
checkpoint

@@
 
-% TODO 아 이거 실제로 돌려봐서 확인해야 할 거 같은뎅.. 실제로 이렇게 나오나...?
+% TODO 아 이거 실제로 돌려봐서 확인해야 할 거 같은데.. 실제로 이렇게 나오나...?
 
@@
 
+By combining all three kinds of edges, we get a finished graph where every node
+is represents a node, and every edge represent how one method relates to another.
+
 \paragraph{Determining CPTs}
 
-% 여기서는 표를 좀 빡시게 그려야 한다. 셀도 좀 색칠하고...
+After we determine which and which methods should be connected with a directed
+edge, we then define a conditional probability table (CPT) for each directed
+edge. This step is essential since CPTs are essential components of Bayesian
+Networks and we want our big graph to be broken down into small
+Bayesian networks. Each node should have its own CPT, and it express how the
+node's marginal distribution depends
+on those of the parent nodes. We use largely two different CPT schemas:
+that of the dataflow-edges and those of the call- and similarity-edges.
+Regardless of the schemas, the CPT's size is $4\times 4^n$, where $n$ is the
+number of parent nodes of a node. The below figure demonstrates a CPT of a node
+with two parent nodes, each shooting a data-flow edge to this node.
 
-After we determine which and which methods should be connected with a directed
-edge, we then define a conditional probability table for each directed edge.
+% TODO 텍스트로만 써 놓은 걸 실제로 색칠하기.
+% VH -> Red, High -> Orange,
+% Low -> Green, VL -> Blue
+\begin{center}
+  \begin{tabular} { |c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c| }
+    \hline
+    low  & vl   & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & vl   & vl  \\
+    high & low  & high & high & vl   & low  & vl   & vl   & high & low  & cell & high & high & low  & high & high\\
+    high & vl   & low  & high & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & high & vl   & low  & high\\
+    high & vl   & high & vh   & vl   & vl   & vl   & low  & high & vl   & high & vh   & high & vl   & high & vh  \\
+    \hline
+\end{tabular}
+\end{center}
+
+In the above table, red cells should contain very high probabilities, orange
+cells should contain relatively high probabilities, whereas green cells should
+be assigned low probabilities, and blue cells should be of very low probability.
+The idea is this: by the definitions of ``source'', ``sanitizer'', and ``sink'',
+data must flow from a source to a sink through possibly a sanitizer, but it
+cannot flow in any other sequence of such methods. For example, data cannot
+possibly flow from a sink through a source to a sanitizer. Therefore, we encode
+this sequence into a tabular form containing probabilities like the above.

### 2021-04-04 My-Papers/SpecHunter/overview.tex
checkpoint: tables

@@
     \hline
+    vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl  \\
+    high & vl   & high & high & vl   & vl   & vl   & vl   & high & vl   & high & high & high & vl   & high & high\\
+    high & vl   & vl   & high & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & high & vl   & vl   & high\\
+    high & vl   & high & high & vl   & vl   & vl   & vl   & high & vl   & high & high & high & vl   & high & high\\
+    \hline
+  \end{tabular}
+\end{center}
+
+Let us first state with the data-flow schemas. In the above table, red cells
+should contain very high probabilities, orange
+cells should contain relatively high probabilities, whereas green cells should
+be assigned low probabilities, and blue cells should be of very low probabilities.
+The idea is this: by the definitions of ``source'', ``sanitizer'', and ``sink'',
+data must flow from a source to a sink through possibly a sanitizer, but it
+cannot flow in any other sequence of such methods. (For example, data cannot
+possibly flow from a sink through a source to a sanitizer.) Also, we note that
+any number of ``none'' methods, which are none of the three, can be interleaved
+freely between a source and a sanitizer, and between a sanitizer and a sink.
+Therefore, we encode these possibilities into a tabular form containing probabilities
+like the above.
+
+For the call-edges and similarity-edges, we use the same schema for both. The
+below figure shows how we assign probabilities when a node has two parents, each
+shooting call-edges or similarity-edges to the node.
+
+% TODO 텍스트로만 써 놓은 걸 실제로 색칠하기.
+% VH -> Red, High -> Orange,
+% Low -> Green, VL -> Blue
+\begin{center}
+  \begin{tabular} { |c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c| }
+    \hline
+    high & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl  & vl   & vl   & vl \\
+    vl   & vl   & vl   & vl   & vl   & high & vl   & vl   & vl   & vl   & vl   & vl   & vl  & vl   & vl   & vl \\
+    vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & high & vl   & vl  & vl   & vl   & vl \\
+    vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl  & vl   & vl   & high \\
+    \hline
+  \end{tabular}
+\end{center}
+% TODO 구현 상으로는 위의 high cell이 low cell로 되어 있는데, 나중에 *꼭*
+% 바꾸자. high cell로 두는 게 맞는 것 같다.
+
+% explanation: why do we make similarity edges share this schema with call edges?
+Combining these together, we can express the case of a node with two parents,
+one shooting a data-flow edge while another shoots a call- or similarity edge.
+
+% TODO 텍스트로만 써 놓은 걸 실제로 색칠하기.
+% VH -> Red, High -> Orange,
+% Low -> Green, VL -> Blue
+\begin{center}
+  \begin{tabular} { |c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c| }
+    \hline
     low  & vl   & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & vl   & vl  \\
@@
 \end{center}
-
-In the above table, red cells should contain very high probabilities, orange
-cells should contain relatively high probabilities, whereas green cells should
-be assigned low probabilities, and blue cells should be of very low probability.
-The idea is this: by the definitions of ``source'', ``sanitizer'', and ``sink'',
-data must flow from a source to a sink through possibly a sanitizer, but it
-cannot flow in any other sequence of such methods. For example, data cannot
-possibly flow from a sink through a source to a sanitizer. Therefore, we encode
-this sequence into a tabular form containing probabilities like the above.
+% TODO 여기도 구현 상으로는 위의 high cell이 low cell로 되어 있는데, 나중에 *꼭*
+% 바꾸자. high cell로 두는 게 맞는 것 같다.

### 2021-04-04 My-Papers/SpecHunter/overview.tex
started working on the "Graph splitting" section

@@
 
-\subsubsection{Network Construction}
+\subsection{Network Construction}
 
@@
     vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & high & vl   & vl  & vl   & vl   & vl  \\
-    vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl  & vl   & vl   & high \\
+    vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl  & vl   & vl   & high\\
     \hline
@@
 % 바꾸자. high cell로 두는 게 맞는 것 같다.
+
+So, we are ready to turn chopped graphs into small, yet full-blown Bayesian
+networks.
+
+\subsection{Graph Splitting}
+
+\paragraph{Splitting Graphs}
+
+% TODO: self_question_n_answer.py가 interaction 한번에 얼마나 걸리는지를 측정해
+% 그래프로 그리기
+After we are done making the initial graph, we chop it down to small graphs of
+size under a certain threshold, which will later be converted into Bayesian
+networks. This breaking down is necessary since the time consumed during loopy
+belief propagation and D-separation algorithms, which will be discussed later
+in the next section, gets increasingly inefficient as the graph size increases. Since we are aiming
+to reduce the time for a single interaction under \emph{xx??} seconds, we
+decided that the optimal threshold for a graph is \emph{180??}. The algorithm
+for this task is described in figure \emph{??}. This algorithm relies heavily on
+the Kernighan-Lin partitioning algorithm, % TODO: should we cite the algorithm's paper?
+which partitions the given graph $G=(V, E)$ into two graphs $G_1=(V_1,E_1)$ and
+$G_2=(V_2, E_2)$, such that $V_1$ and $V_2$ are almost equal and the edges
+connecting $G_1$ and $G_2$ are minimized. % TODO: read the Kernighan-Lin paper!
+% is it really 'minimized'??
+
+\paragraph{Decycling, and controlling in-edges}
+
+Since Bayesian networks are DAGs, we need to eliminate all cycles before we turn
+the splitted graphs into Bayesian networks.
+
+\subsection{Information Propagation}

### 2021-04-04 My-Papers/SpecHunter/overview.tex
checkpoint

@@
 
-So, we are ready to turn chopped graphs into small, yet full-blown Bayesian
-networks.
+Since a CPT has a constraint that the sum of probabilities assigned to each cell
+of a column is 1, we can come up with the following formula to calculate a
+concrete probability value for a cell's relative magnitude of probability.
+Suppose we call four cells of a column $cell_1$, $cell_2$, $cell_3$, $cell_4$,
+then the probability value of one of the four cells is:
 
-\subsection{Graph Splitting}
+\begin{equation*}
+  prob(cell) = \frac{mag(cell)\times coeff(mag(cell))}{\sum_{i=1}^{4}mag(cell)\times coeff(mag(cell_i))}
+\end{equation*}
+
+where $mag$ is the score based on relative magnitude: we give $1$ to cells whose
+probability should be ``very low'', and $4$ to cells whose probability should be
+``very high''. $coeff$ of a relative magnitude is a constant that is multiplied
+to the magnitude score. It helps to widen the gap between probabilities assigned
+to cells in a column, bearing different relative magnitudes.
+
+\subsection{Graph Manipulation}
+
+% TODO cite networkx 
+Here, we explain how we cut the big graph into a handful of small ones, and
+further preprocess them before turning each into a Bayesian network. We used
+\emph{networkx}'s implementation for each core algorithms: Kernighan-Lin
+bisection and cycle detection.
 
@@
 $G_2=(V_2, E_2)$, such that $V_1$ and $V_2$ are almost equal and the edges
-connecting $G_1$ and $G_2$ are minimized. % TODO: read the Kernighan-Lin paper!
+connecting $G_1$ and $G_2$ are minimized. % TODO: at least skim the Kernighan-Lin paper!
 % is it really 'minimized'??
 
-\paragraph{Decycling, and controlling in-edges}
+\paragraph{Decycling, and Controlling in-edges}
 
-Since Bayesian networks are DAGs, we need to eliminate all cycles before we turn
-the splitted graphs into Bayesian networks.
+Since Bayesian networks are directed acyclic graphs (DAGs), we need to eliminate
+all cycles before we turn the splitted graphs into Bayesian networks. We first
+use \emph{networkx}'s cycle
+detection algorithm which pinpoints the set of edges forming a cycle by
+searching the graph in a depth-manner for this task. We then randomly pick one of
+such edges causing a cycle and delete it. Repeatedly applying the two
+operations until the algorithm fails to detect a cycle, we transform the
+splitted graphs into DAGs.      % TODO 이거 figure로 굳이 뺄 필요 없겠지...?
+
+% 'incoming edge가 너무 많아서도, 너무 적어서도 안 된다.'
+Next, we control the number of incoming edges of each node. It is already
+mentioned that the size of a node's CPT is exponential to the number of its
+parent nodes. To our empirical knowledge, if the number of incoming edges (hence
+the number of parent nodes) becomes more than 6, the process of converting the
+graph into a Bayesian network becomes drastically intractable. Therefore, we
+use a simple algorithm to deal with those.
+
+After all these processing, we are finally ready to turn chopped graphs into
+small, yet full-blown Bayesian networks.
 
 \subsection{Information Propagation}
+
+Here, we expound on the core inference algorithm.

### 2021-04-04 My-Papers/SpecHunter/overview.tex
graph manipulation

@@
 
+% TODO
 Swan sucks: too much variance on its performance depending on dataset quality/quantity
@@
 
-Let us first state with the data-flow schemas. In the above table, red cells
+Let us first start with the data-flow schemas. In the above table, red cells
 should contain very high probabilities, orange
@@
 operations until the algorithm fails to detect a cycle, we transform the
-splitted graphs into DAGs.      % TODO 이거 figure로 굳이 뺄 필요 없겠지...?
+splitted graphs into DAGs.
 
@@
 graph into a Bayesian network becomes drastically intractable. Therefore, we
-use a simple algorithm to deal with those.
+reduce the number of parents of such ``rich nodes'' by making the parents of the
+rich node shoot a similarity edge not to the rich node in question, but to some
+other node that is not yet rich.
 
-After all these processing, we are finally ready to turn chopped graphs into
+Also, we minimize the number of ``isolated nodes'' that have no incoming edges
+nor outgoing edges. Since these nodes' marginal probabilities are independent of
+those of any other nodes, their marginals never get updated if any other nodes'
+marginals get updated. Thus, they are one of the major factors that make the
+inference inefficient. We control the number of isolated nodes of a splitted
+graph by sticking the isolated node $n_1$ to a node $n_2$ of other graph if both
+were connected in the initial graph either by edge $(n_1, n_2)$ or $(n_2, n_1)$.
+
+After all these preprocessing, we are finally ready to turn chopped graphs into
 small, yet full-blown Bayesian networks.
@@
 
-Here, we expound on the core inference algorithm.
+Here, we expound on the core inference algorithm. The inference algorithm is
+largely

### 2021-04-04 My-Papers/SpecHunter/overview.tex
started writing information propagation

@@
 
-% 'incoming edge가 너무 많아서도, 너무 적어서도 안 된다.'
 Next, we control the number of incoming edges of each node. It is already
@@
 After all these preprocessing, we are finally ready to turn chopped graphs into
-small, yet full-blown Bayesian networks.
+small, yet full-blown Bayesian networks. Each node corresponds to a random
+variable $\text{The taint specification of method} M$, whose possible values are
+$source$, $sink$, $sanitizer$, and $none$. Now, they are waiting for an external
+oracle to instantiate its value to one of these four.
 
@@
 
-Here, we expound on the core inference algorithm. The inference algorithm is
-largely
+Here, we expound on the core inference algorithm. Inference on the Bayesian
+network is divided into two parts: local propagation and global propagation.
+Local propagations pass information given by the oracle within a single graph,
+whereas global propagations pass the information from one graph to another.

### 2021-04-05 My-Papers/SpecHunter/overview.tex
checkpoint

@@
 Local propagations pass information given by the oracle within a single graph,
-whereas global propagations pass the information from one graph to another.
+whereas global propagations pass the information from one graph or several to
+another. The Python library \emph{Pomegranate} is used to convert graphs into
+Bayesian networks and perform local propagations.   % TODO: cite pomegranate
+
+\paragraph{Local Propagations}
+
+\subparagraph{Picking the Next Node}
+
+We pick the next node based on an algorithm called D-separation
+
+\subparagraph{Overview of the Local Propagation Algorithm}
+
+Local propagations rely on loopy belief propagation algorithm (loopy BP): it is an
+approximate version of an exact belief propagation algorithm (sum-product
+algorithm), defined on Bayesian networks. Loopy BP may not converge,
+nevertheless it provides a nice approximation to the original BP algorithm.
+% TODO: cite https://www.jmlr.org/papers/volume6/ihler05a/ihler05a.pdf
+Since the algorithm may not converge, we set the maximum number of iterations to
+100, the default value set by \emph{Pomegranate}.
+
+% TODO: should we explain a little on loopy BP?
+
+% where should we insert the details of using d-separation?
+
+Figure \emph{xx??} shows our local propagation algorithm. D-separation is used
+when we pick the next node to ask of its specification.
+
+% insert algorithm here
+
+\paragraph{Global Propagations}
+
+Global propagations rely on a process which we call ``knowledge transfer''. It
+relies on the

### 2021-04-05 My-Papers/SpecHunter/overview.tex
writing more overview

@@
 
-We pick the next node based on an algorithm called D-separation
+We pick the next node based on an decision procedure called \emph{D-separation}.
+This algorithm, given the following:
+
+\begin{itemize}
+\item A Bayesian Network (hence, a DAG),
+\item A set of nodes $x$,
+\item Another set of nodes $y$,
+\item Yet another set of nodes $z$,
+\end{itemize}
+
+tells if nodes of $x$ may be probabilistically independent of those in $y$. We
+utilize this algorithm like the following: For all nodes in a Bayesian network in
+hand, we set $x$ as a singleton set of node $n_1$, $y$ as a singleton set of
+node $n_2$, and $z$ as the set of all nodes that we have asked of its value so
+far. This way, we can count the number of nodes that are sure to be
+probabilisitically dependent to that node.
+
+% 이 알고리즘은 그냥 말로 설명하려고 했는데 figure로 따로 빼야겠다.
+
+% nx.d_separated(graph_for_reference, {node}, {other_node}, set(current_asked))
+
+We use \emph{networkx}'s implementation of D-separation.
 
@@
 Global propagations rely on a process which we call ``knowledge transfer''. It
-relies on the
+relies on three major relations:
+
+\begin{itemize}
+\item
+\item
+\item
+\end{itemize}

### 2021-04-05 My-Papers/SpecHunter/evaluation.tex
minors

--- 2021-04-01 My-Papers/SpecHunter/paper.tex
@@
-%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
-\documentclass[sigconf,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For double-blind review submission, w/ CCS and ACM Reference
-% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
-%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
-% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For single-blind review submission, w/ CCS and ACM Reference
-% \documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
-%% For final camera-ready submission, w/ required CCS and ACM Reference
-% \documentclass[acmsmall]{acmart}\settopmatter{}
-
-%% Journal information
-%% Supplied to authors by publisher for camera-ready submission;
-%% use defaults for review submission.
-\acmJournal{PACMPL}
-\acmVolume{1}
-\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
-\acmArticle{1}
-\acmYear{2018}
-\acmMonth{1}
-\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
-\startPage{1}
-
-%% Copyright information
-%% Supplied to authors (based on authors' rights management selection;
-%% see authors.acm.org) by publisher for camera-ready submission;
-%% use 'none' for review submission.
-\setcopyright{none}
-% \setcopyright{acmcopyright}
-% \setcopyright{acmlicensed}
-% \setcopyright{rightsretained}
-% \copyrightyear{2018}           %% If different from \acmYear
-
-%% Bibliography style
-\bibliographystyle{ACM-Reference-Format}
-%% Citation style
-%% Note: author/year citations are required for papers published as an
-%% issue of PACMPL.
-\citestyle{acmauthoryear}   %% For author/year citations
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%% Note: Authors migrating a paper from PACMPL format to traditional
-%% SIGPLAN proceedings format must update the '\documentclass' and
-%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Some recommended packages.
-\usepackage{booktabs}   %% For formal tables:
-%% http://ctan.org/pkg/booktabs
-\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
-%% http://ctan.org/pkg/subcaption
-
-\usepackage{listing}
-
-\begin{document}
-
-%% Title information
-\title{SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net}        
-%% when present, will be used in
-%% header instead of Full Title.
-\titlenote{with title note}             %% \titlenote is optional;
-%% can be repeated if necessary;
-%% contents suppressed with 'anonymous'
-\subtitle{Subtitle}                     %% \subtitle is optional
-\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
-%% can be repeated if necessary;
-%% contents suppressed with 'anonymous'
-
-%% Author information
-%% Contents and number of authors suppressed with 'anonymous'.
-%% Each author should be introduced by \author, followed by
-%% \authornote (optional), \orcid (optional), \affiliation, and
-%% \email.
-%% An author may have multiple affiliations and/or emails; repeat the
-%% appropriate command.
-%% Many elements are not rendered, but should be provided for metadata
-%% extraction tools.
-
-%% Author with single affiliation.
-\author{First1 Last1}
-\authornote{with author1 note}          %% \authornote is optional;
-%% can be repeated if necessary
-\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-\affiliation{
-  \position{Position1}
-  \department{Department1}              %% \department is recommended
-  \institution{Institution1}            %% \institution is required
-  \streetaddress{Street1 Address1}
-  \city{City1}
-  \state{State1}
-  \postcode{Post-Code1}
-  \country{Country1}                    %% \country is recommended
-}
-\email{first1.last1@inst1.edu}          %% \email is recommended
-
-%% Author with two affiliations and emails.
-% \author{First2 Last2}
-% \authornote{with author2 note}          %% \authornote is optional;
-%                                         %% can be repeated if necessary
-% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-% \affiliation{
-% \position{Position2a}
-% \department{Department2a}             %% \department is recommended
-% \institution{Institution2a}           %% \institution is required
-% \streetaddress{Street2a Address2a}
-% \city{City2a}
-% \state{State2a}
-% \postcode{Post-Code2a}
-% \country{Country2a}                   %% \country is recommended
-% }
-%   \email{first2.last2@inst2a.com}         %% \email is recommended
-%   \affiliation{
-%   \position{Position2b}
-%   \department{Department2b}             %% \department is recommended
-%   \institution{Institution2b}           %% \institution is required
-%   \streetaddress{Street3b Address2b}
-%   \city{City2b}
-%   \state{State2b}
-%   \postcode{Post-Code2b}
-%   \country{Country2b}                   %% \country is recommended
-% }
-%   \email{first2.last2@inst2b.org}         %% \email is recommended
-
-%%   Abstract
-%%   Note: \begin{abstract}...\end{abstract} environment must come
-%%   before \maketitle command
-\begin{abstract}
-  SpecHunter is a tool for inferring taint specifications, aiming to aid anyone
-  trying to use a Java taint analyzer, but being overwhelmed by the number of APIs that
-  should be marked of their specifications to run it. SpecHunter aims to lessen this burden
-  by constructing a Bayesian network and performing live interaction with the user, in which
-  it systematically picks a method and asks the user of its specification. By taking an
-  interactive approach, SpecHunter can run on Java applications that use libraries that are
-  implemented in languages other than Java. Also, SpecHunter skips all trial-and-errors
-  in configurating the data-set required in using any of the traditional machine-learning approaches.
-  Our experiments show that SpecHunter actually delivers those promises.
-\end{abstract}
-
-%% 2012 ACM Computing Classification System (CSS) concepts
-%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
-\begin{CCSXML}
-  <ccs2012>
-  <concept>
-  <concept_id>10011007.10011006.10011008</concept_id>
-  <concept_desc>Software and its engineering~General programming languages</concept_desc>
-  <concept_significance>500</concept_significance>
-  </concept>
-  <concept>
-  <concept_id>10003456.10003457.10003521.10003525</concept_id>
-  <concept_desc>Social and professional topics~History of programming languages</concept_desc>
-  <concept_significance>300</concept_significance>
-  </concept>
-  </ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Software and its engineering~General programming languages}
-\ccsdesc[300]{Social and professional topics~History of programming languages}
-%% End of generated code
-
-%% Keywords
-%% comma separated list
-\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission
-
-%% \maketitle
-%% Note: \maketitle command must come after title commands, author
-%% commands, abstract environment, Computing Classification System
-%% environment and commands, and keywords command.
-\maketitle
-
-\section{Introduction}
-Taint analysis, whether static or dynamic, aims to find security vulnerabilities lurking
-in the given program. These vulnerabilities include SQL injection, cross-site
-scripting, and abused printf-arguments. They are typically formulated as a
-data flow starting from a `source' method to a `sink' method, without the
-flowing data being `sanitized' by a relevant method. For such search to be
-precise enough, the analyzer must first be told which methods are sources,
-sinks, sanitizers, or none of them. However, going through the codebase
-searching for imported APIs and labelling every one of them by hand quickly becomes tedious
-thing to do as the codebase gets larger.
-
-% TODO BibTeX을 쓸 줄 모르므로 일단 툴 이름으로 Reference로의 링크를 대신함
-% Boldface들을 BibTeX으로 바꿀 것.
-To aid such manpower, previous studies proposed methods such as supervised
-learning (\textbf{SuSI}, \textbf{SWAN}), and semi-supervised learning (\textbf{Seldon}, \textbf{Merlin}).
-However, works belonging to each camp suffers from their own limitations.
-
-\paragraph{Shortcomings of Supervised Learning Camp.}
-
-\textbf{SuSI} and \textbf{SWAN} both work in a similar way: they first train a learning model
-such as a support vector machine with the actual library codes implementing
-APIs. Here, the function bodies are interprocedurally analyzed with a Java
-static analyzer to get the vectors of feature values. Then, they take a whole
-library codebase into the pre-trained learning
-model, and get the mapping from all APIs in the library to their respective
-specifications. While they work nicely against libraries written in pure Java
-code such as Spring, they cannot work if a given application imports libraries
-written in other languages other than Java. This is because in order to extract
-the feature values they would have to be equipped with all the possible
-languages the libraries would be in, and this is practically difficult.
-
-% TODO: add an additional shortcoming: features should also be updated if a new
-% library is provided
-
-\paragraph{Shortcomings of Semi-Supervised Learning Camp.}
-
-As a workaround to the above limitation, one can try a semi-supervised learning
-approach. The state-of-the-art belonging to this camp is \textbf{Seldon}.
-\textbf{Seldon} only takes the application code into consideration, thus it does
-not care which language the library is written in. So, for example, Seldon can
-figure out the label of an API function in a Python program, which is
-actually implemented in C++. However, Seldon suffers from a common problem of
-all machine-learning solutions, that it is largely dependent on quality dataset.
-In fact, the authors reports that \textbf{Seldon}'s precision dropped by 14
-percent-points by just providing half of the original specifications. Moreover,
-this problem is shared with supervised learning solutions, those are also
-data-driven solutions.
-% Seldon 논문의 부분을 인용하고 싶은데... 형식을 모르겠네
-% 해당 부분:
-% Q6: Impact of Seed Specification. We also evaluated Sel-
-% don’s precision for half the seed specification (considering
-% only odd line numbers in App. B). This significantly reduces
-% precision, by 14 percentage-points. Thus, we believe our
-% seed specification strikes a good balance between manual
-% effort and precision. We note that in the extreme case of an
-% empty seed specification, Seldon will predict 0 specifications,
-% because picking 0 for all variables is a trivial solution to its
-% constraint system.
-
-\paragraph{Our Tool: Real-Time Interactive Inference.}
-
-Our tool, SpecHunter, works in a different manner than data-driven
-approaches. Instead of training the model with some predetermined pairs of
-methods and their labels to predict other methods' labels, we analyze the given
-application to construct probabilistic graphical models of a certain type,
-called Bayesian networks. They are special in that they provide a model of
-conditional-probabilistic reasoning, which infers the marginal probabilities of
-each random variables when some of them are instantiated to a certain value by
-an external source. Therefore, we first determine a structure of a Bayesian network
-by running a static analysis on the given application code, and make the system ask
-the user, the external entity, for evidence. Then, SpecHunter picks the most
-influential node which has the most dependent nodes. This makes the interaction
-session both effective and efficient.
-
-The experiments show that SpecHunter effectively infers taint specifications for
-methods that are untold of its label, with \textbf{xx}\% precision when told only
-\textbf{17.7}\% of all APIs.
-
-\paragraph{Contributions.}
-
-\begin{itemize}
-  \item We provide SpecHunter
-  \item We provide src/sin/san/non ground truths
-  \item We provide a taint analyzer (is it possible?)
-  \item We make the tool open source (is it possible?)
-\end{itemize}
-
-\section{Overview}
-
-\paragraph{Motivation}
-
-Swan sucks: too much variance on its performance depending on dataset quality/quantity
-
-\subsection{Overview of our System}
-
-% 적당한 figure 하나 넣자
-
-Figure 1 shows the overall workflow of SpecHunter. Given a Java application's
-source code, SpecHunter labels all API methods provided by the library the application
-uses. There are three main issues regarding building an effective interactive system:
-namely, constructing the network, effectively propagating the evidence given from the
-oracle, and making the system scale to run on large input applications.
-% Question: Should we define what "API" means?
-
-\subsection{Network Construction}
-
-% Network Construction은 반드시 Scalability and Efficiency와 연관되게 되어 있다.
-% 그 점을 유념하면서 쓰자: 적절한 pointer 달아 주기.
-Here we describe how we represent the input java project into a graph form, which will
-later be turned into a series of Bayesian networks. We hope to create a graph G=(V, E),
-where V is the set of all methods used or defined in the given application, and E is a
-subset of V * V, whose elements are gathered in three different ways.
-
-First, there are data-flow-edges. We perform a variant of a data-flow analysis on the
-given input application to calculate lifetimes of all access paths found in the entire code.
-% 여기서 간단한 예제 넣어주기
-
-\begin{figure}[t]
-  \begin{lstlisting}
-
-    public int m1() {
-      return 1;
-    }
-
-    public int m2(int u1) {
-      return ++u1;
-    }
-
-    public void m3(int u2) {
-      System.out.println(u2);
-    }
-
-    public void f() {
-      int x = m1();
-      g(x);
-    }
-
-    public void g(int y) {
-      int z = m2(y);
-      h(z);
-    }
-
-    public void h(int w) {
-      m3(w);
-    }
-
-  \end{lstlisting}
-\caption{Example Java program with a data flow.}
-vspace{-0.6em}
-\label{fig:sca}
-\end{figure}
-
-Second, there are call-edges.
-
-Last but not least, there are similarity-edges.
-
-\subsection{Graph Splitting}
-
-\subsection{Information Propagation}
-
 \section{Evaluation}
@@
 
+\subsection{Quantitative}
+
+\subsection{Qualitative}
+
 \paragraph{Discussions}
@@
 
-\paragraph{Threats to Validity.}
-
-\section{Related Work}
-
-\section{Conclusion}
-
-%% Acknowledgments
-\begin{acks}                            %% acks environment is optional
-  %% contents suppressed with 'anonymous'
-  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
-  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
-  %% acknowledge financial support and will be used by metadata
-  %% extraction tools.
-  This material is based upon work supported by the
-  \grantsponsor{GS100000001}{National Science
-    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
-  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
-  No.~\grantnum{GS100000001}{mmmmmmm}. Any opinions, findings, and
-  conclusions or recommendations expressed in this material are those
-  of the author and do not necessarily reflect the views of the
-  National Science Foundation.
-\end{acks}
-
-%% Bibliography
-% \bibliography{bibfile}
-
-%% Appendix
-\appendix
-\section{Appendix}
-
-Text of appendix \ldots
-
-\end{document}
+\paragraph{Threats to Validity}

### 2021-04-15 Code/benchmarks/realworld/FFI/javacv/platform/src/test/java/org/bytedeco/javacv/FrameGrabberChangingResolutionTest.java
add benchs

@@ -1,0 +1,270 @@
+/*
+ * Copyright (C) 2016-2017 Samuel Audet
+ *
+ * Licensed either under the Apache License, Version 2.0, or (at your option)
+ * under the terms of the GNU General Public License as published by
+ * the Free Software Foundation (subject to the "Classpath" exception),
+ * either version 2, or any later version (collectively, the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *     http://www.gnu.org/licenses/
+ *     http://www.gnu.org/software/classpath/license.html
+ *
+ * or as provided in the LICENSE.txt file that accompanied this code.
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+package org.bytedeco.javacv;
+
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.nio.FloatBuffer;
+import java.nio.ShortBuffer;
+import org.bytedeco.javacpp.Loader;
+import org.bytedeco.javacpp.indexer.UByteIndexer;
+import org.junit.Test;
+
+import static org.bytedeco.ffmpeg.global.avcodec.*;
+import static org.bytedeco.ffmpeg.global.avutil.*;
+import static org.junit.Assert.*;
+
+/**
+ * Complex Test case for FrameGrabber classes - change the resolution during runtime.
+ * Also uses other classes from JavaCV.
+ *
+ * @author Samuel Audet, Michael Fritscher
+ */
+public class FrameGrabberChangingResolutionTest {
+    private File tempFile = new File(Loader.getTempDir(), "test.mkv");
+    private File tempTargetFile = new File(Loader.getTempDir(), "target.mkv");
+    private boolean endRequested;
+
+    private void makeTestfile() throws Exception {
+        FFmpegFrameRecorder recorder = new FFmpegFrameRecorder(new FileOutputStream(tempFile), 640, 480, 2);
+        recorder.setFormat("matroska"); // mp4 doesn't support streaming
+        recorder.setPixelFormat(AV_PIX_FMT_YUV420P);
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/javacv/platform/src/test/java/org/bytedeco/javacv/FrameGrabberTest.java

@@ -1,0 +1,450 @@
+/*
+ * Copyright (C) 2016-2017 Samuel Audet
+ *
+ * Licensed either under the Apache License, Version 2.0, or (at your option)
+ * under the terms of the GNU General Public License as published by
+ * the Free Software Foundation (subject to the "Classpath" exception),
+ * either version 2, or any later version (collectively, the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *     http://www.gnu.org/licenses/
+ *     http://www.gnu.org/software/classpath/license.html
+ *
+ * or as provided in the LICENSE.txt file that accompanied this code.
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+package org.bytedeco.javacv;
+
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.nio.FloatBuffer;
+import java.nio.ShortBuffer;
+import java.util.Random;
+import org.bytedeco.javacpp.Loader;
+import org.bytedeco.javacpp.PointerScope;
+import org.bytedeco.javacpp.indexer.UByteIndexer;
+import org.junit.Test;
+
+import static org.bytedeco.ffmpeg.global.avcodec.*;
+import static org.bytedeco.ffmpeg.global.avutil.*;
+import static org.junit.Assert.*;
+
+/**
+ * Test cases for FrameGrabber classes. Also uses other classes from JavaCV.
+ *
+ * @author Samuel Audet
+ */
+public class FrameGrabberTest {
+
+    @Test
+    public void testFFmpegFrameGrabber() {
+        System.out.println("FFmpegFrameGrabber");
+
+        File tempFile = new File(Loader.getTempDir(), "test.mkv");
+        try {
+            FFmpegFrameRecorder recorder = new FFmpegFrameRecorder(new FileOutputStream(tempFile), 640, 480, 2);
+            recorder.setFormat("matroska"); // mp4 doesn't support streaming
+            recorder.setPixelFormat(AV_PIX_FMT_BGR24);
+            recorder.setVideoCodecName("jpegls");
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/javacv/src/main/java/org/bytedeco/javacv/FFmpegFrameGrabber.java

@@ -1,0 +1,1437 @@
+/*
+ * Copyright (C) 2009-2020 Samuel Audet
+ *
+ * Licensed either under the Apache License, Version 2.0, or (at your option)
+ * under the terms of the GNU General Public License as published by
+ * the Free Software Foundation (subject to the "Classpath" exception),
+ * either version 2, or any later version (collectively, the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *     http://www.gnu.org/licenses/
+ *     http://www.gnu.org/software/classpath/license.html
+ *
+ * or as provided in the LICENSE.txt file that accompanied this code.
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ *
+ *
+ * Based on the avcodec_sample.0.5.0.c file available at
+ * http://web.me.com/dhoerl/Home/Tech_Blog/Entries/2009/1/22_Revised_avcodec_sample.c_files/avcodec_sample.0.5.0.c
+ * by Martin Böhme, Stephen Dranger, and David Hoerl
+ * as well as on the decoding_encoding.c file included in FFmpeg 0.11.1,
+ * which is covered by the following copyright notice:
+ *
+ * Copyright (c) 2001 Fabrice Bellard
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to deal
+ * in the Software without restriction, including without limitation the rights
+ * to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+ * copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/javacv/src/main/java/org/bytedeco/javacv/FFmpegFrameRecorder.java

@@ -1,0 +1,1349 @@
+/*
+ * Copyright (C) 2009-2020 Samuel Audet
+ *
+ * Licensed either under the Apache License, Version 2.0, or (at your option)
+ * under the terms of the GNU General Public License as published by
+ * the Free Software Foundation (subject to the "Classpath" exception),
+ * either version 2, or any later version (collectively, the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *     http://www.gnu.org/licenses/
+ *     http://www.gnu.org/software/classpath/license.html
+ *
+ * or as provided in the LICENSE.txt file that accompanied this code.
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ *
+ *
+ * Based on the output-example.c file included in FFmpeg 0.6.5
+ * as well as on the decoding_encoding.c file included in FFmpeg 0.11.1,
+ * which are covered by the following copyright notice:
+ *
+ * Libavformat API example: Output a media file in any supported
+ * libavformat format. The default codecs are used.
+ *
+ * Copyright (c) 2001,2003 Fabrice Bellard
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to deal
+ * in the Software without restriction, including without limitation the rights
+ * to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+ * copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL
+ * THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/DefaultKafkaRestContext.java

@@ -1,0 +1,104 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.v2.KafkaConsumerManager;
+import org.apache.kafka.clients.admin.Admin;
+import org.apache.kafka.clients.admin.AdminClient;
+import org.apache.kafka.clients.producer.KafkaProducer;
+import org.apache.kafka.clients.producer.Producer;
+import org.apache.kafka.common.serialization.ByteArraySerializer;
+
+/**
+ * Shared, global state for the REST proxy server, including configuration and connection pools.
+ * ProducerPool, AdminClientWrapper and KafkaConsumerManager instances are initialized lazily
+ * if required.
+ */
+public class DefaultKafkaRestContext implements KafkaRestContext {
+
+  private final KafkaRestConfig config;
+  private KafkaConsumerManager kafkaConsumerManager;
+
+  private Admin adminClient;
+  private Producer<byte[], byte[]> producer;
+
+  /**
+   * @deprecated Use {@link #DefaultKafkaRestContext(KafkaRestConfig)} instead.
+   */
+  @Deprecated
+  public DefaultKafkaRestContext(
+      KafkaRestConfig config,
+      ProducerPool producerPool,
+      KafkaConsumerManager kafkaConsumerManager
+  ) {
+    this(config);
+  }
+
+  public DefaultKafkaRestContext(KafkaRestConfig config) {
+    this.config = requireNonNull(config);
+  }
+
+  @Override
+  public KafkaRestConfig getConfig() {
+    return config;
+  }
+
+  @Override
+  public ProducerPool getProducerPool() {
+    return new ProducerPool(getProducer());
+  }
+
+  @Override
+  public synchronized KafkaConsumerManager getKafkaConsumerManager() {
+    if (kafkaConsumerManager == null) {
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/ProducerPool.java

@@ -1,0 +1,39 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest;
+
+import static java.util.Objects.requireNonNull;
+
+import org.apache.kafka.clients.producer.Producer;
+
+/**
+ * @deprecated This class only exists to satisfy the {@link KafkaRestContext} interface. It is soon
+ *             to be deleted. Access the producer directly, either via {@link
+ *             KafkaRestContext#getProducer()} or via injection of {@code Producer<byte[], byte[]>}.
+ */
+@Deprecated
+public final class ProducerPool {
+
+  private final Producer<byte[], byte[]> producer;
+
+  public ProducerPool(Producer<byte[], byte[]> producer) {
+    this.producer = requireNonNull(producer);
+  }
+
+  public Producer<byte[], byte[]> getProducer() {
+    return producer;
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/backends/kafka/KafkaModule.java

@@ -1,0 +1,107 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.backends.kafka;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.KafkaRestContext;
+import io.confluent.kafkarest.extension.KafkaRestContextProvider;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import org.apache.kafka.clients.admin.Admin;
+import org.apache.kafka.clients.producer.Producer;
+import org.glassfish.hk2.api.Factory;
+import org.glassfish.hk2.api.TypeLiteral;
+import org.glassfish.hk2.utilities.binding.AbstractBinder;
+import org.glassfish.jersey.process.internal.RequestScoped;
+
+/**
+ * A module to configure access to Kafka.
+ *
+ * <p>Right now this module does little but delegate to {@link KafkaRestContext}, since access to
+ * Kafka is currently being configured there. It's the author's intention to move such logic here,
+ * and eliminate {@code KafkaRestContext}, once dependence injection is properly used elsewhere.</p>
+ */
+public final class KafkaModule extends AbstractBinder {
+
+  @Override
+  protected void configure() {
+    bindFactory(KafkaRestContextFactory.class)
+        .to(KafkaRestContext.class)
+        .in(RequestScoped.class);
+
+    bindFactory(AdminFactory.class)
+        .to(Admin.class)
+        .in(RequestScoped.class);
+
+    bindFactory(ProducerFactory.class)
+        .to(new TypeLiteral<Producer<byte[], byte[]>>() { })
+        .in(RequestScoped.class);
+  }
+
+  private static final class KafkaRestContextFactory implements Factory<KafkaRestContext> {
+
+    @Override
+    public KafkaRestContext provide() {
+      return KafkaRestContextProvider.getCurrentContext();
+    }
+
+    @Override
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/controllers/ControllersModule.java

@@ -1,0 +1,47 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.controllers;
+
+import org.glassfish.hk2.utilities.binding.AbstractBinder;
+
+/**
+ * A module to install the various controllers required by the application.
+ */
+public final class ControllersModule extends AbstractBinder {
+
+  protected void configure() {
+    bind(AclManagerImpl.class).to(AclManager.class);
+    bind(BrokerConfigManagerImpl.class).to(BrokerConfigManager.class);
+    bind(BrokerManagerImpl.class).to(BrokerManager.class);
+    bind(ClusterConfigManagerImpl.class).to(ClusterConfigManager.class);
+    bind(ClusterManagerImpl.class).to(ClusterManager.class);
+    bind(ConsumerAssignmentManagerImpl.class).to(ConsumerAssignmentManager.class);
+    bind(ConsumerGroupLagManagerImpl.class).to(ConsumerGroupLagManager.class);
+    bind(ConsumerGroupManagerImpl.class).to(ConsumerGroupManager.class);
+    bind(ConsumerLagManagerImpl.class).to(ConsumerLagManager.class);
+    bind(ConsumerManagerImpl.class).to(ConsumerManager.class);
+    bindAsContract(NoSchemaRecordSerializer.class);
+    bind(PartitionManagerImpl.class).to(PartitionManager.class);
+    bind(ProduceControllerImpl.class).to(ProduceController.class);
+    bind(ReassignmentManagerImpl.class).to(ReassignmentManager.class);
+    bind(RecordSerializerFacade.class).to(RecordSerializer.class);
+    bind(ReplicaManagerImpl.class).to(ReplicaManager.class);
+    bind(SchemaManagerImpl.class).to(SchemaManager.class);
+    bindAsContract(SchemaRecordSerializer.class);
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/controllers/PartitionManager.java

@@ -1,0 +1,52 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.controllers;
+
+import io.confluent.kafkarest.entities.Partition;
+import java.util.List;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+
+/**
+ * A service to manage Kafka {@link Partition Partitions}.
+ */
+public interface PartitionManager {
+
+  /**
+   * Returns the list of Kafka {@link Partition Partitions} belonging to the {@link
+   * io.confluent.kafkarest.entities.Topic} with the given {@code topicName}.
+   */
+  CompletableFuture<List<Partition>> listPartitions(String clusterId, String topicName);
+
+  /**
+   * Returns the list of Kafka {@link Partition Partitions} belonging to the {@link
+   * io.confluent.kafkarest.entities.Topic} with the given {@code topicName}, in the {@link
+   * io.confluent.kafkarest.entities.Cluster} that this application is connected to.
+   */
+  CompletableFuture<List<Partition>> listLocalPartitions(String topicName);
+
+  /**
+   * Returns the Kafka {@link Partition} with the given {@code partitionId}.
+   */
+  CompletableFuture<Optional<Partition>> getPartition(
+      String clusterId, String topicName, int partitionId);
+
+  /**
+   * Returns the Kafka {@link Partition} with the given {@code partitionId}, belonging to the {@link
+   * io.confluent.kafkarest.entities.Cluster} that this application is connected to.
+   */
+  CompletableFuture<Optional<Partition>> getLocalPartition(String topicName, int partitionId);
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/controllers/PartitionManagerImpl.java

@@ -1,0 +1,143 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.controllers;
+
+import static io.confluent.kafkarest.controllers.Entities.checkEntityExists;
+import static io.confluent.kafkarest.controllers.Entities.findEntityByKey;
+import static java.util.Collections.emptyList;
+import static java.util.Objects.requireNonNull;
+import static java.util.concurrent.CompletableFuture.completedFuture;
+
+import io.confluent.kafkarest.common.CompletableFutures;
+import io.confluent.kafkarest.common.KafkaFutures;
+import io.confluent.kafkarest.entities.Partition;
+import io.confluent.kafkarest.entities.Topic;
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+import javax.inject.Inject;
+import org.apache.kafka.clients.admin.Admin;
+import org.apache.kafka.clients.admin.ListOffsetsOptions;
+import org.apache.kafka.clients.admin.ListOffsetsResult;
+import org.apache.kafka.clients.admin.ListOffsetsResult.ListOffsetsResultInfo;
+import org.apache.kafka.clients.admin.OffsetSpec;
+import org.apache.kafka.common.TopicPartition;
+
+final class PartitionManagerImpl implements PartitionManager {
+
+  private final Admin adminClient;
+  private final TopicManager topicManager;
+
+  @Inject
+  PartitionManagerImpl(Admin adminClient, TopicManager topicManager) {
+    this.adminClient = requireNonNull(adminClient);
+    this.topicManager = requireNonNull(topicManager);
+  }
+
+  @Override
+  public CompletableFuture<List<Partition>> listPartitions(String clusterId, String topicName) {
+    return topicManager.getTopic(clusterId, topicName)
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/controllers/TopicConfigManager.java

@@ -1,0 +1,58 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.controllers;
+
+import io.confluent.kafkarest.entities.AlterConfigCommand;
+import io.confluent.kafkarest.entities.TopicConfig;
+import java.util.List;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+
+/**
+ * A service to manage Kafka {@link TopicConfig TopicConfigs}.
+ */
+public interface TopicConfigManager {
+
+  /**
+   * Returns the list of Kafka {@link TopicConfig TopicConfigs} belonging to the
+   * {@link io.confluent.kafkarest.entities.Topic} with the given {@code topicName}.
+   */
+  CompletableFuture<List<TopicConfig>> listTopicConfigs(String clusterId, String topicName);
+
+  /**
+   * Returns the Kafka {@link TopicConfig} with the given {@code name}.
+   */
+  CompletableFuture<Optional<TopicConfig>> getTopicConfig(
+      String clusterId, String topicName, String name);
+
+  /**
+   * Updates the Kafka {@link TopicConfig} with the given {@code name} to the given {@code
+   * newValue}.
+   */
+  CompletableFuture<Void> updateTopicConfig(
+      String clusterId, String topicName, String name, String newValue);
+
+  /**
+   * Resets the Kafka {@link TopicConfig} with the given {@code name} to its default value.
+   */
+  CompletableFuture<Void> resetTopicConfig(String clusterId, String topicName, String name);
+
+  /**
+   * Atomically alters the Kafka {@link TopicConfig Topic Configs} according to {@code commands}.
+   */
+  CompletableFuture<Void> alterTopicConfigs(
+      String clusterId, String topicName, List<AlterConfigCommand> commands);
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/controllers/TopicManagerImpl.java

@@ -1,0 +1,208 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.controllers;
+
+import static io.confluent.kafkarest.controllers.Entities.checkEntityExists;
+import static java.util.Collections.emptyList;
+import static java.util.Collections.singletonList;
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.common.KafkaFutures;
+import io.confluent.kafkarest.entities.Partition;
+import io.confluent.kafkarest.entities.PartitionReplica;
+import io.confluent.kafkarest.entities.Topic;
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Map;
+import java.util.Optional;
+import java.util.Set;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import org.apache.kafka.clients.admin.Admin;
+import org.apache.kafka.clients.admin.NewTopic;
+import org.apache.kafka.clients.admin.TopicDescription;
+import org.apache.kafka.clients.admin.TopicListing;
+import org.apache.kafka.common.Node;
+import org.apache.kafka.common.TopicPartitionInfo;
+
+final class TopicManagerImpl implements TopicManager {
+
+  private final Admin adminClient;
+  private final ClusterManager clusterManager;
+
+  @Inject
+  TopicManagerImpl(Admin adminClient, ClusterManager clusterManager) {
+    this.adminClient = requireNonNull(adminClient);
+    this.clusterManager = requireNonNull(clusterManager);
+  }
+
+  @Override
+  public CompletableFuture<List<Topic>> listTopics(String clusterId) {
+    return clusterManager.getCluster(clusterId)
+        .thenApply(cluster -> checkEntityExists(cluster, "Cluster %s cannot be found.", clusterId))
+        .thenCompose(
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/converters/AvroConverter.java

@@ -1,0 +1,60 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.converters;
+
+import com.fasterxml.jackson.databind.ObjectMapper;
+import com.fasterxml.jackson.databind.node.NullNode;
+import io.confluent.kafka.schemaregistry.avro.AvroSchemaUtils;
+import java.io.IOException;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+/**
+ * Provides conversion of JSON to/from Avro.
+ */
+public final class AvroConverter implements SchemaConverter {
+
+  private static final Logger log = LoggerFactory.getLogger(AvroConverter.class);
+
+  private static final ObjectMapper JSON_MAPPER = new ObjectMapper();
+
+  /**
+   * Converts Avro data (including primitive types) to their equivalent JsonNode representation.
+   *
+   * @param value the value to convert
+   * @return an object containing the root JsonNode representing the converted object and the size
+   *     in bytes of the data when serialized
+   */
+  @Override
+  public JsonNodeAndSize toJson(Object value) {
+    try {
+      byte[] bytes = AvroSchemaUtils.toJson(value);
+      if (bytes == null) {
+        return new JsonNodeAndSize(NullNode.getInstance(), 0);
+      }
+      return new JsonNodeAndSize(JSON_MAPPER.readTree(bytes), bytes.length);
+    } catch (IOException e) {
+      // These can be generated by Avro's JSON encoder, the output stream operations, and the
+      // Jackson ObjectMapper.readTree() call.
+      log.error("Jackson failed to deserialize JSON generated by Avro's JSON encoder: ", e);
+      throw new ConversionException("Failed to convert Avro to JSON: " + e.getMessage());
+    } catch (RuntimeException e) {
+      // Catch-all since it's possible for, e.g., Avro to throw many different RuntimeExceptions
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/converters/JsonSchemaConverter.java

@@ -1,0 +1,56 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.converters;
+
+import com.fasterxml.jackson.databind.ObjectMapper;
+import io.confluent.kafka.schemaregistry.json.JsonSchemaUtils;
+import java.io.IOException;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+/**
+ * Provides conversion of JSON to/from JSON Schema.
+ */
+public final class JsonSchemaConverter implements SchemaConverter {
+
+  private static final Logger log = LoggerFactory.getLogger(JsonSchemaConverter.class);
+
+  private static final ObjectMapper JSON_MAPPER = new ObjectMapper();
+
+  /**
+   * Converts JSON Schema data to their equivalent JsonNode representation.
+   *
+   * @param value the value to convert
+   * @return an object containing the root JsonNode representing the converted object and the size
+   *     in bytes of the data when serialized
+   */
+  @Override
+  public JsonNodeAndSize toJson(Object value) {
+    try {
+      byte[] bytes = JsonSchemaUtils.toJson(value);
+      if (bytes == null) {
+        return new JsonNodeAndSize(null, 0);
+      }
+      return new JsonNodeAndSize(JSON_MAPPER.readTree(bytes), bytes.length);
+    } catch (IOException e) {
+      log.error("Jackson failed to deserialize JSON: ", e);
+      throw new ConversionException("Failed to convert JSON Schema to JSON: " + e.getMessage());
+    } catch (RuntimeException e) {
+      log.error("Unexpected exception converting JSON Schema to JSON: ", e);
+      throw new ConversionException("Failed to convert JSON Schema to JSON: " + e.getMessage());
+    }
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/converters/SchemaConverter.java

@@ -1,0 +1,52 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.converters;
+
+import com.fasterxml.jackson.databind.JsonNode;
+
+/**
+ * Provides conversion of JSON to/from an object for a specific schema type.
+ */
+public interface SchemaConverter {
+
+  /**
+   * Converts data (including primitive types) to their equivalent JsonNode representation.
+   *
+   * @param value the value to convert
+   * @return an object containing the root JsonNode representing the converted object and the size
+   *     in bytes of the data when serialized
+   */
+  JsonNodeAndSize toJson(Object value);
+
+  final class JsonNodeAndSize {
+
+    private final JsonNode json;
+    private final long size;
+
+    public JsonNodeAndSize(JsonNode json, long size) {
+      this.json = json;
+      this.size = size;
+    }
+
+    public JsonNode getJson() {
+      return json;
+    }
+
+    public long getSize() {
+      return size;
+    }
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/Cluster.java

@@ -1,0 +1,78 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities;
+
+import com.google.auto.value.AutoValue;
+import com.google.common.collect.ImmutableList;
+import java.util.List;
+import javax.annotation.Nullable;
+
+/**
+ * A Kafka cluster.
+ */
+@AutoValue
+public abstract class Cluster {
+
+  Cluster() {
+  }
+
+  public abstract String getClusterId();
+
+  @Nullable
+  public abstract Broker getController();
+
+  public abstract ImmutableList<Broker> getBrokers();
+
+  public static Builder builder() {
+    return new AutoValue_Cluster.Builder();
+  }
+
+  public static Cluster create(
+      String clusterId, @Nullable Broker controller, List<Broker> brokers) {
+    return builder()
+        .setClusterId(clusterId)
+        .setController(controller)
+        .addAllBrokers(brokers)
+        .build();
+  }
+
+  public Builder toBuilder() {
+    return builder()
+        .setClusterId(getClusterId())
+        .setController(getController())
+        .addAllBrokers(getBrokers());
+  }
+
+  @AutoValue.Builder
+  public abstract static class Builder {
+
+    Builder() {
+    }
+
+    public abstract Builder setClusterId(String clusterId);
+
+    public abstract Builder setController(Broker controller);
+
+    abstract ImmutableList.Builder<Broker> brokersBuilder();
+
+    public final Builder addAllBrokers(Iterable<Broker> brokers) {
+      brokersBuilder().addAll(brokers);
+      return this;
+    }
+
+    public abstract Cluster build();
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/ConsumerGroup.java

@@ -1,0 +1,136 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities;
+
+import com.google.auto.value.AutoValue;
+import com.google.common.collect.ImmutableList;
+import com.google.common.collect.ImmutableMap;
+import java.util.List;
+import java.util.stream.Collectors;
+import org.apache.kafka.clients.admin.ConsumerGroupDescription;
+import org.apache.kafka.common.ConsumerGroupState;
+
+@AutoValue
+public abstract class ConsumerGroup {
+
+  ConsumerGroup() {
+  }
+
+  public abstract String getClusterId();
+
+  public abstract String getConsumerGroupId();
+
+  public abstract boolean isSimple();
+
+  public abstract String getPartitionAssignor();
+
+  public abstract State getState();
+
+  public abstract Broker getCoordinator();
+
+  public abstract ImmutableList<Consumer> getConsumers();
+
+  public final ImmutableMap<Partition, Consumer> getPartitionAssignment() {
+    ImmutableMap.Builder<Partition, Consumer> partitionAssignment = ImmutableMap.builder();
+    for (Consumer consumer : getConsumers()) {
+      for (Partition partition : consumer.getAssignedPartitions()) {
+        partitionAssignment.put(partition, consumer);
+      }
+    }
+    return partitionAssignment.build();
+  }
+
+  public static Builder builder() {
+    return new AutoValue_ConsumerGroup.Builder();
+  }
+
+  public static ConsumerGroup fromConsumerGroupDescription(
+      String clusterId, ConsumerGroupDescription description) {
+    return builder()
+        .setClusterId(clusterId)
+        .setConsumerGroupId(description.groupId())
+        .setSimple(description.isSimpleConsumerGroup())
+        // I have only seen partitionAssignor="" in all my tests, no matter what I do.
+        // TODO: Investigate how to actually get partition assignor.
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/ConsumerInstanceConfig.java

@@ -1,0 +1,70 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities;
+
+import com.google.auto.value.AutoValue;
+import javax.annotation.Nullable;
+
+@AutoValue
+public abstract class ConsumerInstanceConfig {
+
+  ConsumerInstanceConfig() {
+  }
+
+  @Nullable
+  public abstract String getId();
+
+  @Nullable
+  public abstract String getName();
+
+  public abstract EmbeddedFormat getFormat();
+
+  @Nullable
+  public abstract String getAutoOffsetReset();
+
+  @Nullable
+  public abstract String getAutoCommitEnable();
+
+  @Nullable
+  public abstract Integer getResponseMinBytes();
+
+  @Nullable
+  public abstract Integer getRequestWaitMs();
+
+  public static ConsumerInstanceConfig create(EmbeddedFormat format) {
+    return create(
+        /* id= */ null,
+        /* name= */ null,
+        format,
+        /* autoOffsetReset= */ null,
+        /* autoCommitEnable= */ null,
+        /* responseMinBytes= */ null,
+        /* requestWaitMs= */ null);
+  }
+
+  public static ConsumerInstanceConfig create(
+      @Nullable String id,
+      @Nullable String name,
+      EmbeddedFormat format,
+      @Nullable String autoOffsetReset,
+      @Nullable String autoCommitEnable,
+      @Nullable Integer responseMinBytes,
+      @Nullable Integer requestWaitMs
+  ) {
+    return new AutoValue_ConsumerInstanceConfig(
+        id, name, format, autoOffsetReset, autoCommitEnable, responseMinBytes, requestWaitMs);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/EmbeddedFormat.java

@@ -1,0 +1,103 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities;
+
+import io.confluent.kafka.schemaregistry.SchemaProvider;
+import io.confluent.kafka.schemaregistry.avro.AvroSchemaProvider;
+import io.confluent.kafka.schemaregistry.json.JsonSchemaProvider;
+import io.confluent.kafka.schemaregistry.protobuf.ProtobufSchemaProvider;
+
+/**
+ * Permitted formats for ProduceRecords embedded in produce requests/consume responses, e.g.
+ * base64-encoded binary, JSON-encoded Avro, etc. Each of these correspond to a content type, a
+ * ProduceRecord implementation, a Producer in the ProducerPool (with corresponding Kafka
+ * serializer), ConsumerRecord implementation, and a serializer for any instantiated consumers.
+ *
+ * <p>Note that for each type, it's assumed that the key and value can be handled by the same
+ * serializer. This means each serializer should handle both it's complex type (e.g.
+ * Indexed/Generic/SpecificRecord for Avro) and boxed primitive types (Integer, Boolean, etc.).
+ */
+public enum EmbeddedFormat {
+  BINARY {
+    @Override
+    public boolean requiresSchema() {
+      return false;
+    }
+
+    @Override
+    public SchemaProvider getSchemaProvider() {
+      throw new UnsupportedOperationException();
+    }
+  },
+
+  JSON {
+    @Override
+    public boolean requiresSchema() {
+      return false;
+    }
+
+    @Override
+    public SchemaProvider getSchemaProvider() {
+      throw new UnsupportedOperationException();
+    }
+  },
+
+  AVRO {
+    private final SchemaProvider schemaProvider = new AvroSchemaProvider();
+
+    @Override
+    public boolean requiresSchema() {
+      return true;
+    }
+
+    @Override
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/ProduceRecord.java

@@ -1,0 +1,40 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities;
+
+import com.google.auto.value.AutoValue;
+import javax.annotation.Nullable;
+
+@AutoValue
+public abstract class ProduceRecord<K, V> {
+
+  ProduceRecord() {
+  }
+
+  @Nullable
+  public abstract K getKey();
+
+  @Nullable
+  public abstract V getValue();
+
+  @Nullable
+  public abstract Integer getPartition();
+
+  public static <K, V> ProduceRecord<K, V> create(
+      @Nullable K key, @Nullable V value, @Nullable Integer partition) {
+    return new AutoValue_ProduceRecord<>(key, value, partition);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/RegisteredSchema.java

@@ -1,0 +1,34 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities;
+
+import com.google.auto.value.AutoValue;
+import io.confluent.kafka.schemaregistry.ParsedSchema;
+
+@AutoValue
+public abstract class RegisteredSchema {
+
+  RegisteredSchema() {
+  }
+
+  public abstract int getSchemaId();
+
+  public abstract ParsedSchema getSchema();
+
+  public static RegisteredSchema create(int schemaId, ParsedSchema schema) {
+    return new AutoValue_RegisteredSchema(schemaId, schema);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/ConsumerGroupData.java

@@ -1,0 +1,118 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonProperty;
+import com.google.auto.value.AutoValue;
+import io.confluent.kafkarest.entities.ConsumerGroup;
+import io.confluent.kafkarest.entities.ConsumerGroup.State;
+
+@AutoValue
+public abstract class ConsumerGroupData extends Resource {
+
+  ConsumerGroupData() {
+  }
+
+  @JsonProperty("cluster_id")
+  public abstract String getClusterId();
+
+  @JsonProperty("consumer_group_id")
+  public abstract String getConsumerGroupId();
+
+  @JsonProperty("is_simple")
+  public abstract boolean isSimple();
+
+  @JsonProperty("partition_assignor")
+  public abstract String getPartitionAssignor();
+
+  @JsonProperty("state")
+  public abstract State getState();
+
+  @JsonProperty("coordinator")
+  public abstract Relationship getCoordinator();
+
+  @JsonProperty("consumers")
+  public abstract Relationship getConsumers();
+
+  @JsonProperty("lag")
+  public abstract Relationship getLag();
+
+  public static Builder builder() {
+    return new AutoValue_ConsumerGroupData.Builder().setKind("KafkaConsumerGroup");
+  }
+
+  public static Builder fromConsumerGroup(ConsumerGroup consumerGroup) {
+    return builder()
+        .setClusterId(consumerGroup.getClusterId())
+        .setConsumerGroupId(consumerGroup.getConsumerGroupId())
+        .setSimple(consumerGroup.isSimple())
+        .setPartitionAssignor(consumerGroup.getPartitionAssignor())
+        .setState(consumerGroup.getState());
+  }
+
+  @JsonCreator
+  static ConsumerGroupData fromJson(
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/CreateTopicRequest.java

@@ -1,0 +1,114 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonProperty;
+import com.google.auto.value.AutoValue;
+import com.google.common.collect.ImmutableList;
+import java.util.Collections;
+import java.util.List;
+import java.util.Map;
+import java.util.Optional;
+import javax.annotation.Nullable;
+
+@AutoValue
+public abstract class CreateTopicRequest {
+
+  CreateTopicRequest() {
+  }
+
+  @JsonProperty("topic_name")
+  public abstract String getTopicName();
+
+  @JsonProperty("partitions_count")
+  public abstract Optional<Integer> getPartitionsCount();
+
+  @JsonProperty("replication_factor")
+  public abstract Optional<Short> getReplicationFactor();
+
+  @JsonProperty("replicas_assignments")
+  public abstract Map<Integer, List<Integer>> getReplicasAssignments();
+
+  @JsonProperty("configs")
+  public abstract ImmutableList<ConfigEntry> getConfigs();
+
+  public static Builder builder() {
+    return new AutoValue_CreateTopicRequest.Builder()
+        .setReplicasAssignments(Collections.emptyMap());
+  }
+
+  @JsonCreator
+  static CreateTopicRequest fromJson(
+      @JsonProperty("topic_name") String topicName,
+      @JsonProperty("partitions_count") @Nullable Integer partitionsCount,
+      @JsonProperty("replication_factor") @Nullable Short replicationFactor,
+      @JsonProperty("replicas_assignments") @Nullable
+          Map<Integer, List<Integer>> replicasAssignments,
+      @JsonProperty("configs") @Nullable List<ConfigEntry> configs
+  ) {
+    return builder()
+        .setTopicName(topicName)
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/CreateTopicResponse.java

@@ -1,0 +1,39 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonValue;
+import com.google.auto.value.AutoValue;
+
+@AutoValue
+public abstract class CreateTopicResponse {
+
+  CreateTopicResponse() {
+  }
+
+  @JsonValue
+  public abstract TopicData getValue();
+
+  public static CreateTopicResponse create(TopicData value) {
+    return new AutoValue_CreateTopicResponse(value);
+  }
+
+  @JsonCreator
+  static CreateTopicResponse fromJson(TopicData value) {
+    return create(value);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/GetReplicaResponse.java

@@ -1,0 +1,39 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonValue;
+import com.google.auto.value.AutoValue;
+
+@AutoValue
+public abstract class GetReplicaResponse {
+
+  GetReplicaResponse() {
+  }
+
+  @JsonValue
+  public abstract ReplicaData getValue();
+
+  public static GetReplicaResponse create(ReplicaData value) {
+    return new AutoValue_GetReplicaResponse(value);
+  }
+
+  @JsonCreator
+  static GetReplicaResponse fromJson(ReplicaData value) {
+    return create(value);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/GetTopicConfigResponse.java

@@ -1,0 +1,39 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonValue;
+import com.google.auto.value.AutoValue;
+
+@AutoValue
+public abstract class GetTopicConfigResponse {
+
+  GetTopicConfigResponse() {
+  }
+
+  @JsonValue
+  public abstract TopicConfigData getValue();
+
+  public static GetTopicConfigResponse create(TopicConfigData value) {
+    return new AutoValue_GetTopicConfigResponse(value);
+  }
+
+  @JsonCreator
+  static GetTopicConfigResponse fromJson(TopicConfigData value) {
+    return create(value);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/ListBrokersResponse.java

@@ -1,0 +1,39 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonValue;
+import com.google.auto.value.AutoValue;
+
+@AutoValue
+public abstract class ListBrokersResponse {
+
+  ListBrokersResponse() {
+  }
+
+  @JsonValue
+  public abstract BrokerDataList getValue();
+
+  public static ListBrokersResponse create(BrokerDataList value) {
+    return new AutoValue_ListBrokersResponse(value);
+  }
+
+  @JsonCreator
+  static ListBrokersResponse fromJson(BrokerDataList value) {
+    return create(value);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/ListClustersResponse.java

@@ -1,0 +1,39 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonValue;
+import com.google.auto.value.AutoValue;
+
+@AutoValue
+public abstract class ListClustersResponse {
+
+  ListClustersResponse() {
+  }
+
+  @JsonValue
+  public abstract ClusterDataList getValue();
+
+  public static ListClustersResponse create(ClusterDataList value) {
+    return new AutoValue_ListClustersResponse(value);
+  }
+
+  @JsonCreator
+  static ListClustersResponse fromJson(ClusterDataList value) {
+    return create(value);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/ListReplicasResponse.java

@@ -1,0 +1,39 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonValue;
+import com.google.auto.value.AutoValue;
+
+@AutoValue
+public abstract class ListReplicasResponse {
+
+  ListReplicasResponse() {
+  }
+
+  @JsonValue
+  public abstract ReplicaDataList getValue();
+
+  public static ListReplicasResponse create(ReplicaDataList value) {
+    return new AutoValue_ListReplicasResponse(value);
+  }
+
+  @JsonCreator
+  static ListReplicasResponse fromJson(ReplicaDataList value) {
+    return create(value);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/ReplicaData.java

@@ -1,0 +1,111 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonProperty;
+import com.google.auto.value.AutoValue;
+import io.confluent.kafkarest.entities.PartitionReplica;
+
+@AutoValue
+public abstract class ReplicaData extends Resource {
+
+  ReplicaData() {
+  }
+
+  @JsonProperty("cluster_id")
+  public abstract String getClusterId();
+
+  @JsonProperty("topic_name")
+  public abstract String getTopicName();
+
+  @JsonProperty("partition_id")
+  public abstract int getPartitionId();
+
+  @JsonProperty("broker_id")
+  public abstract int getBrokerId();
+
+  @JsonProperty("is_leader")
+  public abstract boolean isLeader();
+
+  @JsonProperty("is_in_sync")
+  public abstract boolean isInSync();
+
+  @JsonProperty("broker")
+  public abstract Relationship getBroker();
+
+  public static Builder builder() {
+    return new AutoValue_ReplicaData.Builder().setKind("KafkaReplica");
+  }
+
+  public static Builder fromPartitionReplica(PartitionReplica replica) {
+    return builder()
+        .setClusterId(replica.getClusterId())
+        .setTopicName(replica.getTopicName())
+        .setPartitionId(replica.getPartitionId())
+        .setBrokerId(replica.getBrokerId())
+        .setLeader(replica.isLeader())
+        .setInSync(replica.isInSync());
+  }
+
+  @JsonCreator
+  static ReplicaData fromJson(
+      @JsonProperty("kind") String kind,
+      @JsonProperty("metadata") Metadata metadata,
+      @JsonProperty("cluster_id") String clusterId,
+      @JsonProperty("topic_name") String topicName,
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/TopicData.java

@@ -1,0 +1,109 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonProperty;
+import com.google.auto.value.AutoValue;
+import io.confluent.kafkarest.entities.Topic;
+
+@AutoValue
+public abstract class TopicData extends Resource {
+
+  TopicData() {
+  }
+
+  @JsonProperty("cluster_id")
+  public abstract String getClusterId();
+
+  @JsonProperty("topic_name")
+  public abstract String getTopicName();
+
+  @JsonProperty("is_internal")
+  public abstract boolean isInternal();
+
+  @JsonProperty("replication_factor")
+  public abstract int getReplicationFactor();
+
+  @JsonProperty("partitions")
+  public abstract Relationship getPartitions();
+
+  @JsonProperty("configs")
+  public abstract Relationship getConfigs();
+
+  @JsonProperty("partition_reassignments")
+  public abstract Relationship getPartitionReassignments();
+
+  public static Builder builder() {
+    return new AutoValue_TopicData.Builder().setKind("KafkaTopic");
+  }
+
+  public static Builder fromTopic(Topic topic) {
+    return builder()
+        .setClusterId(topic.getClusterId())
+        .setTopicName(topic.getName())
+        .setInternal(topic.isInternal())
+        .setReplicationFactor(topic.getReplicationFactor());
+  }
+
+  @JsonCreator
+  static TopicData fromJson(
+      @JsonProperty("kind") String kind,
+      @JsonProperty("metadata") Metadata metadata,
+      @JsonProperty("cluster_id") String clusterId,
+      @JsonProperty("topic_name") String topicName,
+      @JsonProperty("is_internal") boolean isInternal,
+      @JsonProperty("replication_factor") int replicationFactor,
+      @JsonProperty("partitions") Relationship partitions,
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/entities/v3/UpdateTopicConfigRequest.java

@@ -1,0 +1,41 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.entities.v3;
+
+import com.fasterxml.jackson.annotation.JsonCreator;
+import com.fasterxml.jackson.annotation.JsonProperty;
+import com.google.auto.value.AutoValue;
+import java.util.Optional;
+import javax.annotation.Nullable;
+
+@AutoValue
+public abstract class UpdateTopicConfigRequest {
+
+  UpdateTopicConfigRequest() {
+  }
+
+  @JsonProperty("value")
+  public abstract Optional<String> getValue();
+
+  public static UpdateTopicConfigRequest create(@Nullable String value) {
+    return new AutoValue_UpdateTopicConfigRequest(Optional.ofNullable(value));
+  }
+
+  @JsonCreator
+  static UpdateTopicConfigRequest fromJson(@JsonProperty("value") @Nullable String value) {
+    return create(value);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/extension/EnumConverterProvider.java

@@ -1,0 +1,123 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.extension;
+
+import static java.util.Objects.requireNonNull;
+
+import com.fasterxml.jackson.annotation.JsonValue;
+import com.google.common.collect.HashBasedTable;
+import com.google.common.collect.Table;
+import com.google.common.collect.Tables;
+import java.lang.annotation.Annotation;
+import java.lang.reflect.InvocationTargetException;
+import java.lang.reflect.Method;
+import java.lang.reflect.Type;
+import java.util.Arrays;
+import java.util.List;
+import java.util.stream.Collectors;
+import javax.ws.rs.ext.ParamConverter;
+import javax.ws.rs.ext.ParamConverterProvider;
+
+public final class EnumConverterProvider implements ParamConverterProvider {
+
+  private static final Table<Class<?>, String, Enum<?>> enumMapper =
+      Tables.synchronizedTable(HashBasedTable.create());
+
+  @Override
+  @SuppressWarnings({"unchecked", "rawtypes"})
+  public <T> ParamConverter<T> getConverter(
+      Class<T> rawType, Type genericType, Annotation[] annotations) {
+    if (!Enum.class.isAssignableFrom(rawType)) {
+      return null;
+    }
+
+    ParamConverter<T> converter = (ParamConverter<T>) new EnumConverter<>((Class<Enum>) rawType);
+    if (enumMapper.containsRow(rawType)) {
+      return converter;
+    }
+
+    List<Method> jsonValueMethods =
+        Arrays.stream(rawType.getMethods())
+            .filter(method -> method.getAnnotation(JsonValue.class) != null)
+            .collect(Collectors.toList());
+
+    if (jsonValueMethods.size() > 1) {
+      throw new RuntimeException(
+          "Multiple methods annotated with @JsonValue in " + rawType.getName());
+    }
+
+    if (jsonValueMethods.isEmpty()) {
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/extension/KafkaRestContextProvider.java

@@ -1,0 +1,68 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.extension;
+
+import io.confluent.kafkarest.DefaultKafkaRestContext;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.KafkaRestContext;
+import java.util.concurrent.atomic.AtomicBoolean;
+
+public class KafkaRestContextProvider {
+
+  private static KafkaRestContext defaultContext = null;
+  private static KafkaRestConfig defaultAppConfig = null;
+  private static final InheritableThreadLocal<KafkaRestContext> restContextInheritableThreadLocal =
+      new InheritableThreadLocal<>();
+
+  private static final AtomicBoolean initialized = new AtomicBoolean();
+
+  public static void initialize(KafkaRestConfig appConfig) {
+    if (initialized.compareAndSet(false, true)) {
+      defaultContext = new DefaultKafkaRestContext(appConfig);
+      defaultAppConfig = appConfig;
+    }
+  }
+
+  public static KafkaRestConfig getDefaultAppConfig() {
+    return defaultAppConfig;
+  }
+
+  public static KafkaRestContext getDefaultContext() {
+    return defaultContext;
+  }
+
+  public static KafkaRestContext getCurrentContext() {
+    if (restContextInheritableThreadLocal.get() != null) {
+      return restContextInheritableThreadLocal.get();
+    } else {
+      return defaultContext;
+    }
+  }
+
+  public static void setCurrentContext(KafkaRestContext kafkaRestContext) {
+    restContextInheritableThreadLocal.set(kafkaRestContext);
+  }
+
+  public static void clearCurrentContext() {
+    restContextInheritableThreadLocal.remove();
+  }
+
+  public static synchronized void clean() {
+    defaultContext.shutdown();
+    defaultContext = null;
+    initialized.set(false);
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/AsyncResponses.java

@@ -1,0 +1,130 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources;
+
+import java.lang.annotation.Annotation;
+import java.util.Arrays;
+import java.util.concurrent.CompletableFuture;
+import java.util.concurrent.CompletionException;
+import java.util.function.Function;
+import javax.annotation.Nullable;
+import javax.ws.rs.container.AsyncResponse;
+import javax.ws.rs.core.Response;
+import javax.ws.rs.core.Response.ResponseBuilder;
+
+/**
+ * Utilities to deal with {@link AsyncResponse}.
+ */
+public final class AsyncResponses {
+
+  private AsyncResponses() {
+  }
+
+  /**
+   * Resumes the given {@code asyncResponse} with the result of {@code entity}.
+   */
+  public static <T> void asyncResume(AsyncResponse asyncResponse, CompletableFuture<T> entity) {
+    AsyncResponseBuilder.<T>from(Response.ok()).entity(entity).asyncResume(asyncResponse);
+  }
+
+  /**
+   * A analogous of {@link AsyncResponse} for {@link ResponseBuilder}.
+   */
+  public static final class AsyncResponseBuilder<T> {
+
+    private final ResponseBuilder responseBuilder;
+
+    @Nullable
+    private CompletableFuture<? extends T> entityFuture;
+
+    @Nullable
+    private Annotation[] entityAnnotations;
+
+    @Nullable
+    private Function<? super T, Response.Status> statusFunction;
+
+    private AsyncResponseBuilder(ResponseBuilder responseBuilder) {
+      this.responseBuilder = responseBuilder.clone();
+    }
+
+    /**
+     * Returns a new {@link AsyncResponseBuilder} that when resumed, will return a response built
+     * from the given {@code responseBuilder}.
+     */
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/ResourcesFeature.java

@@ -1,0 +1,46 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.KafkaRestContext;
+import io.confluent.kafkarest.resources.v2.V2ResourcesFeature;
+import io.confluent.kafkarest.resources.v3.V3ResourcesFeature;
+import javax.ws.rs.core.Feature;
+import javax.ws.rs.core.FeatureContext;
+
+public final class ResourcesFeature implements Feature {
+  private final KafkaRestContext context;
+  private final KafkaRestConfig config;
+
+  public ResourcesFeature(KafkaRestContext context, KafkaRestConfig config) {
+    this.context = requireNonNull(context);
+    this.config = requireNonNull(config);
+  }
+
+  @Override
+  public boolean configure(FeatureContext configurable) {
+    if (config.isV2ApiEnabled()) {
+      configurable.register(new V2ResourcesFeature(context));
+    }
+    if (config.isV3ApiEnabled()) {
+      configurable.register(V3ResourcesFeature.class);
+    }
+    return true;
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v2/ProduceToPartitionAction.java

@@ -1,0 +1,162 @@
+/*
+ * Copyright 2021 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v2;
+
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.controllers.ProduceController;
+import io.confluent.kafkarest.controllers.RecordSerializer;
+import io.confluent.kafkarest.controllers.SchemaManager;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.v2.ProduceRequest;
+import io.confluent.kafkarest.entities.v2.ProduceResponse;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses.AsyncResponseBuilder;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.validation.Valid;
+import javax.validation.constraints.NotNull;
+import javax.ws.rs.Consumes;
+import javax.ws.rs.POST;
+import javax.ws.rs.Path;
+import javax.ws.rs.PathParam;
+import javax.ws.rs.Produces;
+import javax.ws.rs.container.AsyncResponse;
+import javax.ws.rs.container.Suspended;
+import javax.ws.rs.core.Response;
+
+@Path("/topics/{topic}/partitions")
+@Consumes({
+    Versions.KAFKA_V2_JSON_BINARY,
+    Versions.KAFKA_V2_JSON_JSON,
+    Versions.KAFKA_V2_JSON_AVRO,
+    Versions.KAFKA_V2_JSON_JSON_SCHEMA,
+    Versions.KAFKA_V2_JSON_PROTOBUF
+})
+@Produces({Versions.KAFKA_V2_JSON})
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v2/RootResource.java

@@ -1,0 +1,54 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v2;
+
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.HashMap;
+import java.util.Map;
+import javax.validation.Valid;
+import javax.ws.rs.Consumes;
+import javax.ws.rs.GET;
+import javax.ws.rs.POST;
+import javax.ws.rs.Path;
+import javax.ws.rs.Produces;
+
+@Path("/")
+@Produces({Versions.KAFKA_V2_JSON_WEIGHTED})
+@Consumes({Versions.KAFKA_V2_JSON})
+@ResourceName("api.v2.root.*")
+public final class RootResource {
+
+  @GET
+  @PerformanceMetric("root.get+v2")
+  @ResourceName("api.v2.root.get")
+  public Map<String, String> get() {
+    // Currently this just provides an endpoint that's a nop and can be used to check for liveness
+    // and can be used for tests that need to test the server setup rather than the functionality
+    // of a specific resource. Some APIs provide a listing of endpoints as their root resource; it
+    // might be nice to provide that.
+    return new HashMap<>();
+  }
+
+  @POST
+  @PerformanceMetric("root.post+v2")
+  @ResourceName("api.v2.root.post")
+  public Map<String, String> post(@Valid Map<String, String> request) {
+    // This version allows testing with posted entities
+    return new HashMap<>();
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/AclsResource.java

@@ -1,0 +1,291 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.AclManager;
+import io.confluent.kafkarest.entities.Acl;
+import io.confluent.kafkarest.entities.Acl.Operation;
+import io.confluent.kafkarest.entities.Acl.PatternType;
+import io.confluent.kafkarest.entities.Acl.Permission;
+import io.confluent.kafkarest.entities.Acl.ResourceType;
+import io.confluent.kafkarest.entities.v3.AclData;
+import io.confluent.kafkarest.entities.v3.AclDataList;
+import io.confluent.kafkarest.entities.v3.CreateAclRequest;
+import io.confluent.kafkarest.entities.v3.DeleteAclsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.entities.v3.SearchAclsResponse;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.resources.AsyncResponses.AsyncResponseBuilder;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.net.URI;
+import java.util.Comparator;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.validation.Valid;
+import javax.ws.rs.BadRequestException;
+import javax.ws.rs.Consumes;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/BrokerConfigsResource.java

@@ -1,0 +1,196 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.BrokerConfigManager;
+import io.confluent.kafkarest.entities.BrokerConfig;
+import io.confluent.kafkarest.entities.v3.BrokerConfigData;
+import io.confluent.kafkarest.entities.v3.BrokerConfigDataList;
+import io.confluent.kafkarest.entities.v3.GetBrokerConfigResponse;
+import io.confluent.kafkarest.entities.v3.ListBrokerConfigsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.entities.v3.UpdateBrokerConfigRequest;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.resources.AsyncResponses.AsyncResponseBuilder;
+import io.confluent.kafkarest.response.CrnFactory;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.Comparator;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.validation.Valid;
+import javax.ws.rs.Consumes;
+import javax.ws.rs.DELETE;
+import javax.ws.rs.GET;
+import javax.ws.rs.NotFoundException;
+import javax.ws.rs.PUT;
+import javax.ws.rs.Path;
+import javax.ws.rs.PathParam;
+import javax.ws.rs.Produces;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/ClustersResource.java

@@ -1,0 +1,147 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.ClusterManager;
+import io.confluent.kafkarest.entities.Cluster;
+import io.confluent.kafkarest.entities.v3.ClusterData;
+import io.confluent.kafkarest.entities.v3.ClusterDataList;
+import io.confluent.kafkarest.entities.v3.GetClusterResponse;
+import io.confluent.kafkarest.entities.v3.ListClustersResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.response.CrnFactory;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.ws.rs.GET;
+import javax.ws.rs.NotFoundException;
+import javax.ws.rs.Path;
+import javax.ws.rs.PathParam;
+import javax.ws.rs.Produces;
+import javax.ws.rs.container.AsyncResponse;
+import javax.ws.rs.container.Suspended;
+import javax.ws.rs.core.MediaType;
+
+@Path("/v3/clusters")
+@ResourceName("api.v3.clusters.*")
+public final class ClustersResource {
+
+  private final Provider<ClusterManager> clusterManager;
+  private final CrnFactory crnFactory;
+  private final UrlFactory urlFactory;
+
+  @Inject
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/ConsumerAssignmentsResource.java

@@ -1,0 +1,189 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.ConsumerAssignmentManager;
+import io.confluent.kafkarest.entities.ConsumerAssignment;
+import io.confluent.kafkarest.entities.v3.ConsumerAssignmentData;
+import io.confluent.kafkarest.entities.v3.ConsumerAssignmentDataList;
+import io.confluent.kafkarest.entities.v3.GetConsumerAssignmentResponse;
+import io.confluent.kafkarest.entities.v3.ListConsumerAssignmentsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.Resource.Relationship;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.response.CrnFactory;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.Comparator;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.ws.rs.GET;
+import javax.ws.rs.NotFoundException;
+import javax.ws.rs.Path;
+import javax.ws.rs.PathParam;
+import javax.ws.rs.Produces;
+import javax.ws.rs.container.AsyncResponse;
+import javax.ws.rs.container.Suspended;
+import javax.ws.rs.core.MediaType;
+
+@Path(
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/ConsumerGroupsResource.java

@@ -1,0 +1,159 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.ConsumerGroupManager;
+import io.confluent.kafkarest.entities.ConsumerGroup;
+import io.confluent.kafkarest.entities.v3.ConsumerGroupData;
+import io.confluent.kafkarest.entities.v3.ConsumerGroupDataList;
+import io.confluent.kafkarest.entities.v3.GetConsumerGroupResponse;
+import io.confluent.kafkarest.entities.v3.ListConsumerGroupsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.Resource.Relationship;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.response.CrnFactory;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.ws.rs.GET;
+import javax.ws.rs.NotFoundException;
+import javax.ws.rs.Path;
+import javax.ws.rs.PathParam;
+import javax.ws.rs.Produces;
+import javax.ws.rs.container.AsyncResponse;
+import javax.ws.rs.container.Suspended;
+import javax.ws.rs.core.MediaType;
+
+@Path("/v3/clusters/{clusterId}/consumer-groups")
+@ResourceName("api.v3.consumer-groups.*")
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/ConsumersResource.java

@@ -1,0 +1,157 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.ConsumerManager;
+import io.confluent.kafkarest.entities.Consumer;
+import io.confluent.kafkarest.entities.v3.ConsumerData;
+import io.confluent.kafkarest.entities.v3.ConsumerDataList;
+import io.confluent.kafkarest.entities.v3.GetConsumerResponse;
+import io.confluent.kafkarest.entities.v3.ListConsumersResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.Resource.Relationship;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.response.CrnFactory;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.Comparator;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.ws.rs.GET;
+import javax.ws.rs.NotFoundException;
+import javax.ws.rs.Path;
+import javax.ws.rs.PathParam;
+import javax.ws.rs.Produces;
+import javax.ws.rs.container.AsyncResponse;
+import javax.ws.rs.container.Suspended;
+import javax.ws.rs.core.MediaType;
+
+@Path("/v3/clusters/{clusterId}/consumer-groups/{consumerGroupId}/consumers")
+@ResourceName("api.v3.consumers.*")
+public final class ConsumersResource {
+
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/PartitionsResource.java

@@ -1,0 +1,188 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.PartitionManager;
+import io.confluent.kafkarest.entities.Partition;
+import io.confluent.kafkarest.entities.v3.GetPartitionResponse;
+import io.confluent.kafkarest.entities.v3.ListPartitionsResponse;
+import io.confluent.kafkarest.entities.v3.PartitionData;
+import io.confluent.kafkarest.entities.v3.PartitionDataList;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.response.CrnFactory;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.ws.rs.GET;
+import javax.ws.rs.NotFoundException;
+import javax.ws.rs.Path;
+import javax.ws.rs.PathParam;
+import javax.ws.rs.Produces;
+import javax.ws.rs.container.AsyncResponse;
+import javax.ws.rs.container.Suspended;
+import javax.ws.rs.core.MediaType;
+
+@Path("/v3/clusters/{clusterId}/topics/{topicName}/partitions")
+@ResourceName("api.v3.partitions.*")
+public final class PartitionsResource {
+
+  private final Provider<PartitionManager> partitionManager;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/ReplicasResource.java

@@ -1,0 +1,158 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.ReplicaManager;
+import io.confluent.kafkarest.entities.PartitionReplica;
+import io.confluent.kafkarest.entities.v3.GetReplicaResponse;
+import io.confluent.kafkarest.entities.v3.ListReplicasResponse;
+import io.confluent.kafkarest.entities.v3.ReplicaData;
+import io.confluent.kafkarest.entities.v3.ReplicaDataList;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.response.CrnFactory;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.ws.rs.GET;
+import javax.ws.rs.NotFoundException;
+import javax.ws.rs.Path;
+import javax.ws.rs.PathParam;
+import javax.ws.rs.Produces;
+import javax.ws.rs.container.AsyncResponse;
+import javax.ws.rs.container.Suspended;
+import javax.ws.rs.core.MediaType;
+
+@Path("/v3/clusters/{clusterId}/topics/{topicName}/partitions/{partitionId}/replicas")
+@ResourceName("api.v3.replicas.*")
+public final class ReplicasResource {
+
+  private final Provider<ReplicaManager> replicaManager;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/SearchReplicasByBrokerAction.java

@@ -1,0 +1,136 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Comparator.comparing;
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.ReplicaManager;
+import io.confluent.kafkarest.entities.PartitionReplica;
+import io.confluent.kafkarest.entities.v3.ReplicaData;
+import io.confluent.kafkarest.entities.v3.ReplicaDataList;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.entities.v3.SearchReplicasByBrokerResponse;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.response.CrnFactory;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.ws.rs.GET;
+import javax.ws.rs.Path;
+import javax.ws.rs.PathParam;
+import javax.ws.rs.Produces;
+import javax.ws.rs.container.AsyncResponse;
+import javax.ws.rs.container.Suspended;
+import javax.ws.rs.core.MediaType;
+
+@Path("/v3/clusters/{clusterId}/brokers/{brokerId}/partition-replicas")
+@ResourceName("api.v3.replicas.*")
+public final class SearchReplicasByBrokerAction {
+
+  private final Provider<ReplicaManager> replicaManager;
+  private final CrnFactory crnFactory;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/TopicsResource.java

@@ -1,0 +1,239 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.Collections.emptyList;
+import static java.util.Objects.requireNonNull;
+
+import io.confluent.kafkarest.controllers.TopicManager;
+import io.confluent.kafkarest.entities.Topic;
+import io.confluent.kafkarest.entities.v3.CreateTopicRequest;
+import io.confluent.kafkarest.entities.v3.CreateTopicRequest.ConfigEntry;
+import io.confluent.kafkarest.entities.v3.CreateTopicResponse;
+import io.confluent.kafkarest.entities.v3.GetTopicResponse;
+import io.confluent.kafkarest.entities.v3.ListTopicsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.entities.v3.TopicData;
+import io.confluent.kafkarest.entities.v3.TopicDataList;
+import io.confluent.kafkarest.extension.ResourceBlocklistFeature.ResourceName;
+import io.confluent.kafkarest.resources.AsyncResponses;
+import io.confluent.kafkarest.resources.AsyncResponses.AsyncResponseBuilder;
+import io.confluent.kafkarest.response.CrnFactory;
+import io.confluent.kafkarest.response.UrlFactory;
+import io.confluent.rest.annotations.PerformanceMetric;
+import java.net.URI;
+import java.util.Comparator;
+import java.util.List;
+import java.util.Map;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+import java.util.stream.Collectors;
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.validation.Valid;
+import javax.ws.rs.Consumes;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/resources/v3/V3ResourcesFeature.java

@@ -1,0 +1,48 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import javax.ws.rs.core.Feature;
+import javax.ws.rs.core.FeatureContext;
+
+public final class V3ResourcesFeature implements Feature {
+
+  @Override
+  public boolean configure(FeatureContext configurable) {
+    configurable.register(AclsResource.class);
+    configurable.register(AlterBrokerConfigBatchAction.class);
+    configurable.register(AlterClusterConfigBatchAction.class);
+    configurable.register(AlterTopicConfigBatchAction.class);
+    configurable.register(BrokerConfigsResource.class);
+    configurable.register(BrokersResource.class);
+    configurable.register(ClusterConfigsResource.class);
+    configurable.register(ClustersResource.class);
+    configurable.register(ConsumerAssignmentsResource.class);
+    configurable.register(ConsumerGroupLagsResource.class);
+    configurable.register(ConsumerGroupsResource.class);
+    configurable.register(ConsumersResource.class);
+    configurable.register(ConsumerLagsResource.class);
+    configurable.register(GetReassignmentAction.class);
+    configurable.register(ListAllReassignmentsAction.class);
+    configurable.register(SearchReassignmentsByTopicAction.class);
+    configurable.register(PartitionsResource.class);
+    configurable.register(ReplicasResource.class);
+    configurable.register(SearchReplicasByBrokerAction.class);
+    configurable.register(TopicConfigsResource.class);
+    configurable.register(TopicsResource.class);
+    return true;
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/response/FakeUrlFactory.java

@@ -1,0 +1,38 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.response;
+
+/**
+ * A fake {@link UrlFactory} to be used in tests.
+ */
+public final class FakeUrlFactory implements UrlFactory {
+
+  private static final char SEPARATOR = '/';
+
+  @Override
+  public String create(String... segments) {
+    UrlBuilder urlBuilder = newUrlBuilder();
+    for (String segment : segments) {
+      urlBuilder.appendPathSegment(segment);
+    }
+    return urlBuilder.build();
+  }
+
+  @Override
+  public UrlBuilder newUrlBuilder() {
+    return new UrlBuilder(/* baseUrl= */ "");
+  }
+}

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/response/UrlFactoryImpl.java

@@ -1,0 +1,158 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.response;
+
+import io.confluent.kafkarest.config.ConfigModule.AdvertisedListenersConfig;
+import io.confluent.kafkarest.config.ConfigModule.HostNameConfig;
+import io.confluent.kafkarest.config.ConfigModule.ListenersConfig;
+import io.confluent.kafkarest.config.ConfigModule.PortConfig;
+import java.net.URI;
+import java.util.List;
+import java.util.Optional;
+import java.util.stream.Stream;
+import javax.inject.Inject;
+import javax.ws.rs.core.Context;
+import javax.ws.rs.core.UriInfo;
+
+public final class UrlFactoryImpl implements UrlFactory {
+
+  private static final char SEPARATOR = '/';
+
+  private final String baseUrl;
+
+  @Inject
+  public UrlFactoryImpl(
+      @HostNameConfig String hostNameConfig,
+      @PortConfig Integer portConfig,
+      @AdvertisedListenersConfig List<URI> advertisedListenersConfig,
+      @ListenersConfig List<URI> listenersConfig,
+      @Context UriInfo requestUriInfo
+  ) {
+    baseUrl =
+        computeBaseUrl(
+            hostNameConfig, portConfig, advertisedListenersConfig, listenersConfig, requestUriInfo);
+  }
+
+  @Override
+  public String create(String... segments) {
+    UrlBuilder urlBuilder = newUrlBuilder();
+    for (String component : segments) {
+      String stripped = trimSeparator(component);
+      if (!stripped.isEmpty()) {
+        urlBuilder.appendPathSegment(stripped);
+      }
+    }
+    return urlBuilder.build();
+  }
+
+  @Override
+  public UrlBuilder newUrlBuilder() {
+    return new UrlBuilder(baseUrl);
+  }
+
+  private static String computeBaseUrl(
+      String hostNameConfig,
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/v2/JsonKafkaConsumerState.java

@@ -1,0 +1,73 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.v2;
+
+import com.fasterxml.jackson.databind.ObjectMapper;
+import io.confluent.kafkarest.ConsumerInstanceId;
+import io.confluent.kafkarest.ConsumerRecordAndSize;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.entities.ConsumerInstanceConfig;
+import org.apache.kafka.clients.consumer.Consumer;
+import org.apache.kafka.clients.consumer.ConsumerRecord;
+import org.apache.kafka.common.errors.SerializationException;
+
+public class JsonKafkaConsumerState extends KafkaConsumerState<byte[], byte[], Object, Object> {
+
+  private static final ObjectMapper objectMapper = new ObjectMapper();
+
+  public JsonKafkaConsumerState(
+      KafkaRestConfig config,
+      ConsumerInstanceConfig consumerInstanceConfig,
+      ConsumerInstanceId instanceId,
+      Consumer consumer) {
+    super(config, consumerInstanceConfig, instanceId, consumer);
+  }
+
+  @Override
+  public ConsumerRecordAndSize<Object, Object> createConsumerRecord(
+      ConsumerRecord<byte[], byte[]> record) {
+    long approxSize = 0;
+
+    Object key = null;
+    Object value = null;
+
+    // The extra serialization here is unfortunate. We could use @JsonRawValue
+    // and just use the raw bytes, but that risks returning invalid data to the user
+    // if their data is not actually JSON encoded.
+
+    if (record.key() != null) {
+      approxSize += record.key().length;
+      key = deserialize(record.key());
+    }
+
+    if (record.value() != null) {
+      approxSize += record.value().length;
+      value = deserialize(record.value());
+    }
+
+    return new ConsumerRecordAndSize<>(
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/v2/KafkaConsumerManager.java

@@ -1,0 +1,790 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.v2;
+
+import static io.confluent.kafkarest.KafkaRestConfig.CONSUMER_MAX_THREADS_CONFIG;
+
+import io.confluent.kafkarest.ConsumerInstanceId;
+import io.confluent.kafkarest.ConsumerReadCallback;
+import io.confluent.kafkarest.Errors;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.converters.AvroConverter;
+import io.confluent.kafkarest.converters.JsonSchemaConverter;
+import io.confluent.kafkarest.converters.ProtobufConverter;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.v2.ConsumerAssignmentRequest;
+import io.confluent.kafkarest.entities.v2.ConsumerAssignmentResponse;
+import io.confluent.kafkarest.entities.v2.ConsumerCommittedRequest;
+import io.confluent.kafkarest.entities.v2.ConsumerCommittedResponse;
+import io.confluent.kafkarest.entities.ConsumerInstanceConfig;
+import io.confluent.kafkarest.entities.v2.ConsumerOffsetCommitRequest;
+import io.confluent.kafkarest.entities.v2.ConsumerSeekRequest;
+import io.confluent.kafkarest.entities.v2.ConsumerSeekToRequest;
+import io.confluent.kafkarest.entities.v2.ConsumerSubscriptionRecord;
+import io.confluent.kafkarest.entities.v2.ConsumerSubscriptionResponse;
+import io.confluent.kafkarest.entities.TopicPartitionOffset;
+import io.confluent.rest.exceptions.RestNotFoundException;
+import io.confluent.rest.exceptions.RestServerErrorException;
+import java.time.Clock;
+import java.time.Duration;
+import java.time.Instant;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/main/java/io/confluent/kafkarest/v2/SchemaKafkaConsumerState.java

@@ -1,0 +1,60 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.v2;
+
+import com.fasterxml.jackson.databind.JsonNode;
+import io.confluent.kafkarest.ConsumerInstanceId;
+import io.confluent.kafkarest.ConsumerRecordAndSize;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.converters.SchemaConverter;
+import io.confluent.kafkarest.entities.ConsumerInstanceConfig;
+import org.apache.kafka.clients.consumer.Consumer;
+import org.apache.kafka.clients.consumer.ConsumerRecord;
+
+/**
+ * Schema-specific implementation of KafkaConsumerState, which decodes
+ * into Objects or primitive types.
+ */
+public final class SchemaKafkaConsumerState
+    extends KafkaConsumerState<Object, Object, JsonNode, JsonNode> {
+
+  private final SchemaConverter schemaConverter;
+
+  public SchemaKafkaConsumerState(
+      KafkaRestConfig config,
+      ConsumerInstanceConfig consumerInstanceConfig,
+      ConsumerInstanceId instanceId,
+      Consumer consumer,
+      SchemaConverter schemaConverter) {
+    super(config, consumerInstanceConfig, instanceId, consumer);
+    this.schemaConverter = schemaConverter;
+  }
+
+  @Override
+  public ConsumerRecordAndSize<JsonNode, JsonNode> createConsumerRecord(
+      ConsumerRecord<Object, Object> record) {
+    SchemaConverter.JsonNodeAndSize keyNode = schemaConverter.toJson(record.key());
+    SchemaConverter.JsonNodeAndSize valueNode = schemaConverter.toJson(record.value());
+    return new ConsumerRecordAndSize<>(
+        io.confluent.kafkarest.entities.ConsumerRecord.create(
+            record.topic(),
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/TestUtils.java

@@ -1,0 +1,322 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+package io.confluent.kafkarest;
+
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertTrue;
+
+import com.fasterxml.jackson.databind.JsonNode;
+import com.fasterxml.jackson.databind.ObjectMapper;
+import com.google.protobuf.ByteString;
+import io.confluent.kafkarest.entities.EntityUtils;
+import io.confluent.kafkarest.entities.ProduceRecord;
+import io.confluent.kafkarest.entities.v2.PartitionOffset;
+import io.confluent.rest.entities.ErrorMessage;
+import java.time.Duration;
+import java.util.Collection;
+import java.util.Collections;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+import java.util.Properties;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.atomic.AtomicInteger;
+import java.util.concurrent.locks.LockSupport;
+import java.util.function.Supplier;
+import javax.ws.rs.core.GenericType;
+import javax.ws.rs.core.Response;
+import org.apache.avro.generic.IndexedRecord;
+import org.apache.kafka.clients.CommonClientConfigs;
+import org.apache.kafka.clients.consumer.ConsumerConfig;
+import org.apache.kafka.clients.consumer.ConsumerRecord;
+import org.apache.kafka.clients.consumer.ConsumerRecords;
+import org.apache.kafka.clients.consumer.KafkaConsumer;
+import org.junit.Assert;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class TestUtils {
+
+  private static final Logger log = LoggerFactory.getLogger(TestUtils.class);
+  private static final ObjectMapper jsonParser = new ObjectMapper();
+
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/controllers/BrokerManagerImplTest.java

@@ -1,0 +1,135 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.controllers;
+
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertFalse;
+import static org.junit.Assert.fail;
+
+import io.confluent.kafkarest.entities.Broker;
+import io.confluent.kafkarest.entities.Cluster;
+import java.util.Arrays;
+import java.util.List;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+import java.util.concurrent.ExecutionException;
+import javax.ws.rs.NotFoundException;
+import org.easymock.EasyMockRule;
+import org.easymock.Mock;
+import org.junit.Before;
+import org.junit.Rule;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+@RunWith(JUnit4.class)
+public class BrokerManagerImplTest {
+
+  private static final String CLUSTER_ID = "cluster-1";
+
+  private static final Broker BROKER_1 = Broker.create(CLUSTER_ID, 1, "1.0.0.1", 1, null);
+  private static final Broker BROKER_2 = Broker.create(CLUSTER_ID, 2, "1.0.0.2", 2, null);
+  private static final Broker BROKER_3 = Broker.create(CLUSTER_ID, 2, "1.0.0.3", 3, "rack-3");
+
+  private static final Cluster CLUSTER =
+      Cluster.create(CLUSTER_ID, BROKER_1, Arrays.asList(BROKER_1, BROKER_2, BROKER_3));
+
+  @Rule
+  public final EasyMockRule mocks = new EasyMockRule(this);
+
+  @Mock
+  private ClusterManager clusterManager;
+
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/controllers/ClusterManagerImplTest.java

@@ -1,0 +1,253 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.controllers;
+
+import static io.confluent.kafkarest.common.KafkaFutures.failedFuture;
+import static java.util.Collections.emptyList;
+import static java.util.Collections.singletonList;
+import static org.easymock.EasyMock.anyObject;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertFalse;
+import static org.junit.Assert.fail;
+
+import io.confluent.kafkarest.entities.Broker;
+import io.confluent.kafkarest.entities.Cluster;
+import io.confluent.kafkarest.exceptions.UnsupportedProtocolException;
+import java.util.Arrays;
+import java.util.List;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+import java.util.concurrent.ExecutionException;
+import org.apache.kafka.clients.admin.Admin;
+import org.apache.kafka.clients.admin.DescribeClusterResult;
+import org.apache.kafka.common.KafkaFuture;
+import org.apache.kafka.common.Node;
+import org.apache.kafka.common.errors.TimeoutException;
+import org.easymock.EasyMockRule;
+import org.easymock.Mock;
+import org.junit.Before;
+import org.junit.Rule;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+@RunWith(JUnit4.class)
+public class ClusterManagerImplTest {
+
+  private static final String CLUSTER_ID = "cluster-1";
+  private static final Node NODE_1 = new Node(1, "broker-1", 9091);
+  private static final Node NODE_2 = new Node(2, "broker-2", 9092);
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/controllers/PartitionManagerImplTest.java

@@ -1,0 +1,451 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.controllers;
+
+import static io.confluent.kafkarest.common.CompletableFutures.failedFuture;
+import static org.easymock.EasyMock.anyObject;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertFalse;
+import static org.junit.Assert.fail;
+
+import io.confluent.kafkarest.entities.Partition;
+import io.confluent.kafkarest.entities.PartitionReplica;
+import io.confluent.kafkarest.entities.Topic;
+import java.util.Arrays;
+import java.util.List;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+import java.util.concurrent.ExecutionException;
+import javax.ws.rs.NotFoundException;
+import org.apache.kafka.clients.admin.Admin;
+import org.apache.kafka.clients.admin.ListOffsetsResult;
+import org.apache.kafka.clients.admin.ListOffsetsResult.ListOffsetsResultInfo;
+import org.apache.kafka.common.KafkaFuture;
+import org.apache.kafka.common.TopicPartition;
+import org.easymock.EasyMockRule;
+import org.easymock.Mock;
+import org.junit.Before;
+import org.junit.Rule;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+@RunWith(JUnit4.class)
+public class PartitionManagerImplTest {
+
+  private static final String CLUSTER_ID = "cluster-1";
+  private static final String TOPIC_NAME = "topic-1";
+
+  private static final Partition PARTITION_1 =
+      Partition.create(
+          CLUSTER_ID,
+          TOPIC_NAME,
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/controllers/TopicConfigManagerImplTest.java

@@ -1,0 +1,628 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.controllers;
+
+import static java.util.Collections.emptyList;
+import static java.util.Collections.singletonList;
+import static java.util.Collections.singletonMap;
+import static java.util.concurrent.CompletableFuture.completedFuture;
+import static org.easymock.EasyMock.anyObject;
+import static org.easymock.EasyMock.eq;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.easymock.EasyMock.verify;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertFalse;
+import static org.junit.Assert.fail;
+
+import io.confluent.kafkarest.common.KafkaFutures;
+import io.confluent.kafkarest.entities.AlterConfigCommand;
+import io.confluent.kafkarest.entities.Cluster;
+import io.confluent.kafkarest.entities.ConfigSource;
+import io.confluent.kafkarest.entities.TopicConfig;
+import java.util.Arrays;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Optional;
+import java.util.concurrent.ExecutionException;
+import javax.ws.rs.NotFoundException;
+import org.apache.kafka.clients.admin.Admin;
+import org.apache.kafka.clients.admin.AlterConfigOp;
+import org.apache.kafka.clients.admin.AlterConfigsResult;
+import org.apache.kafka.clients.admin.Config;
+import org.apache.kafka.clients.admin.ConfigEntry;
+import org.apache.kafka.clients.admin.DescribeConfigsOptions;
+import org.apache.kafka.clients.admin.DescribeConfigsResult;
+import org.apache.kafka.common.KafkaFuture;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/AbstractConsumerTest.java

@@ -1,0 +1,262 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+package io.confluent.kafkarest.integration;
+
+import static io.confluent.kafkarest.TestUtils.assertErrorResponse;
+import static io.confluent.kafkarest.TestUtils.assertOKResponse;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertNotNull;
+import static org.junit.Assert.assertTrue;
+
+import io.confluent.kafkarest.Errors;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.TestUtils;
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.entities.ConsumerRecord;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.v2.BinaryConsumerRecord;
+import io.confluent.kafkarest.entities.v2.CommitOffsetsResponse;
+import io.confluent.kafkarest.entities.v2.ConsumerSubscriptionRecord;
+import io.confluent.kafkarest.entities.v2.CreateConsumerInstanceRequest;
+import io.confluent.kafkarest.entities.v2.CreateConsumerInstanceResponse;
+import java.net.MalformedURLException;
+import java.net.URL;
+import java.time.Instant;
+import java.time.format.DateTimeFormatter;
+import java.util.Collections;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+import java.util.function.Function;
+import java.util.stream.Collectors;
+import javax.ws.rs.client.Entity;
+import javax.ws.rs.core.GenericType;
+import javax.ws.rs.core.Response;
+import javax.ws.rs.core.Response.Status;
+import org.apache.kafka.clients.producer.ProducerRecord;
+import org.junit.Assert;
+
+public class AbstractConsumerTest extends ClusterTestHarness {
+
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/AbstractProducerTest.java

@@ -1,0 +1,162 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.integration;
+
+import static io.confluent.kafkarest.TestUtils.assertOKResponse;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertNotNull;
+
+import io.confluent.kafkarest.Errors;
+import io.confluent.kafkarest.TestUtils;
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.entities.ProduceRecord;
+import io.confluent.kafkarest.entities.v2.PartitionOffset;
+import io.confluent.kafkarest.entities.v2.ProduceResponse;
+import java.util.Collections;
+import java.util.List;
+import java.util.Map;
+import javax.ws.rs.client.Entity;
+import javax.ws.rs.core.Response;
+
+public class AbstractProducerTest<TopicRequestT, PartitionRequestT> extends ClusterTestHarness {
+
+  protected <K, V> void testProduceToTopic(
+      String topicName,
+      TopicRequestT request,
+      String keyDeserializerClassName,
+      String valueDeserializerClassName,
+      List<PartitionOffset> offsetResponses,
+      boolean matchPartitions,
+      List<ProduceRecord<K, V>> expected
+  ) {
+    testProduceToTopic(topicName,
+        request,
+        keyDeserializerClassName,
+        valueDeserializerClassName,
+        offsetResponses,
+        matchPartitions,
+        Collections.emptyMap(),
+        expected);
+  }
+
+  protected <K, V> void testProduceToTopic(
+      String topicName,
+      TopicRequestT request,
+      String keyDeserializerClassName,
+      String valueDeserializerClassName,
+      List<PartitionOffset> offsetResponses,
+      boolean matchPartitions,
+      Map<String, String> queryParams,
+      List<ProduceRecord<K, V>> expected
+  ) {
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/ClusterTestHarness.java

@@ -1,0 +1,526 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+package io.confluent.kafkarest.integration;
+
+import static java.util.stream.Collectors.toList;
+import static org.junit.Assert.fail;
+
+import io.confluent.common.utils.IntegrationTest;
+import io.confluent.kafka.schemaregistry.avro.AvroCompatibilityLevel;
+import io.confluent.kafka.schemaregistry.rest.SchemaRegistryConfig;
+import io.confluent.kafka.schemaregistry.rest.SchemaRegistryRestApplication;
+import io.confluent.kafka.serializers.KafkaAvroSerializer;
+import io.confluent.kafka.serializers.KafkaJsonSerializer;
+import io.confluent.kafkarest.KafkaRestApplication;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.common.CompletableFutures;
+import java.io.File;
+import java.io.IOException;
+import java.net.ServerSocket;
+import java.net.URI;
+import java.net.URISyntaxException;
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+import java.util.Optional;
+import java.util.Properties;
+import java.util.Set;
+import java.util.concurrent.CompletableFuture;
+import java.util.concurrent.ExecutionException;
+import java.util.stream.IntStream;
+import javax.ws.rs.client.Client;
+import javax.ws.rs.client.ClientBuilder;
+import javax.ws.rs.client.Invocation;
+import javax.ws.rs.client.WebTarget;
+import kafka.server.KafkaConfig;
+import kafka.server.KafkaServer;
+import kafka.utils.CoreUtils;
+import kafka.utils.MockTime;
+import kafka.utils.TestUtils;
+import kafka.zk.EmbeddedZookeeper;
+import kafka.zk.KafkaZkClient;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/ConsumerBinaryTest.java

@@ -1,0 +1,191 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+package io.confluent.kafkarest.integration;
+
+import static io.confluent.kafkarest.TestUtils.assertErrorResponse;
+
+import io.confluent.kafkarest.Errors;
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.v2.BinaryConsumerRecord;
+import io.confluent.kafkarest.entities.v2.CreateConsumerInstanceRequest;
+import io.confluent.rest.exceptions.ConstraintViolationExceptionMapper;
+import java.util.Arrays;
+import java.util.List;
+import javax.ws.rs.client.Entity;
+import javax.ws.rs.core.GenericType;
+import javax.ws.rs.core.Response;
+import org.apache.kafka.clients.producer.ProducerRecord;
+import org.junit.Before;
+import org.junit.Test;
+
+public class ConsumerBinaryTest extends AbstractConsumerTest {
+
+  private static final String topicName = "topic1";
+  private static final String groupName = "testconsumergroup";
+
+  private final List<ProducerRecord<byte[], byte[]>> recordsOnlyValues = Arrays.asList(
+      new ProducerRecord<>(topicName, "value".getBytes()),
+      new ProducerRecord<>(topicName, "value2".getBytes()),
+      new ProducerRecord<>(topicName, "value3".getBytes()),
+      new ProducerRecord<>(topicName, "value4".getBytes())
+  );
+
+  private final List<ProducerRecord<byte[], byte[]>> recordsWithKeys = Arrays.asList(
+      new ProducerRecord<>(topicName, "key".getBytes(), "value".getBytes()),
+      new ProducerRecord<>(topicName, "key".getBytes(), "value2".getBytes()),
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/JsonProducerTest.java

@@ -1,0 +1,173 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+package io.confluent.kafkarest.integration;
+
+import io.confluent.kafka.serializers.KafkaJsonDeserializer;
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.entities.v2.JsonPartitionProduceRequest;
+import io.confluent.kafkarest.entities.v2.JsonPartitionProduceRequest.JsonPartitionProduceRecord;
+import io.confluent.kafkarest.entities.v2.JsonTopicProduceRequest;
+import io.confluent.kafkarest.entities.v2.JsonTopicProduceRequest.JsonTopicProduceRecord;
+import io.confluent.kafkarest.entities.v2.PartitionOffset;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+import java.util.Properties;
+import org.junit.Before;
+import org.junit.Test;
+import scala.collection.JavaConverters;
+
+public class JsonProducerTest
+    extends AbstractProducerTest<JsonTopicProduceRequest, JsonPartitionProduceRequest> {
+
+  private String topicName = "topic1";
+
+  @Before
+  @Override
+  public void setUp() throws Exception {
+    super.setUp();
+    final int numPartitions = 3;
+    final int replicationFactor = 1;
+    kafka.utils.TestUtils.createTopic(zkClient, topicName, numPartitions, replicationFactor,
+        JavaConverters.asScalaBuffer(this.servers),
+        new Properties());
+  }
+
+  @Override
+  protected String getEmbeddedContentType() {
+    return Versions.KAFKA_V2_JSON_JSON;
+  }
+
+  private Map<String, Object> exampleMapValue() {
+    Map<String, Object> res = new HashMap<String, Object>();
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/ProducerTest.java

@@ -1,0 +1,231 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+package io.confluent.kafkarest.integration;
+
+import static org.junit.Assert.assertEquals;
+
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.entities.v2.BinaryPartitionProduceRequest;
+import io.confluent.kafkarest.entities.v2.BinaryPartitionProduceRequest.BinaryPartitionProduceRecord;
+import io.confluent.kafkarest.entities.v2.BinaryTopicProduceRequest;
+import io.confluent.kafkarest.entities.v2.BinaryTopicProduceRequest.BinaryTopicProduceRecord;
+import io.confluent.kafkarest.entities.v2.PartitionOffset;
+import java.util.Arrays;
+import java.util.List;
+import java.util.Properties;
+import javax.ws.rs.client.Entity;
+import javax.ws.rs.core.Response;
+import org.apache.kafka.common.serialization.ByteArrayDeserializer;
+import org.junit.Before;
+import org.junit.Test;
+import scala.collection.JavaConverters;
+
+public class ProducerTest
+    extends AbstractProducerTest<BinaryTopicProduceRequest, BinaryPartitionProduceRequest> {
+
+  private static final String topicName = "topic1";
+
+  // Produce to topic inputs & results
+
+  private final List<BinaryTopicProduceRecord> topicRecordsWithKeys = Arrays.asList(
+      new BinaryTopicProduceRecord("key", "value", null),
+      new BinaryTopicProduceRecord("key", "value2", null),
+      new BinaryTopicProduceRecord("key", "value3", null),
+      new BinaryTopicProduceRecord("key", "value4", null)
+  );
+
+  private final List<BinaryTopicProduceRecord> topicRecordsWithPartitions = Arrays.asList(
+      new BinaryTopicProduceRecord(null, "value", 0),
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v2/AvroProduceConsumeTest.java

@@ -1,0 +1,83 @@
+package io.confluent.kafkarest.integration.v2;
+
+import com.fasterxml.jackson.databind.node.IntNode;
+import io.confluent.kafka.schemaregistry.ParsedSchema;
+import io.confluent.kafka.schemaregistry.avro.AvroSchema;
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.converters.AvroConverter;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.v2.SchemaTopicProduceRequest.SchemaTopicProduceRecord;
+import java.util.Arrays;
+import java.util.List;
+import org.apache.avro.Schema;
+import org.apache.avro.generic.GenericRecordBuilder;
+
+public final class AvroProduceConsumeTest extends SchemaProduceConsumeTest {
+
+  private static final AvroConverter AVRO_CONVERTER = new AvroConverter();
+
+  private static final Schema KEY_SCHEMA =
+      new Schema.Parser().parse(""
+          + "{"
+          + "  \"type\": \"int\","
+          + "  \"name\": \"key\""
+          + "}");
+
+  private static final Schema VALUE_SCHEMA =
+      new Schema.Parser().parse(""
+          + "{"
+          + "  \"type\": \"record\", "
+          + "  \"name\": \"ValueRecord\","
+          + "  \"fields\":[{"
+          + "    \"name\": \"value\", "
+          + "    \"type\": \"int\""
+          + "  }]"
+          + "}");
+
+  private static final List<SchemaTopicProduceRecord> PRODUCE_RECORDS =
+      Arrays.asList(
+          new SchemaTopicProduceRecord(
+              new IntNode(1),
+              AVRO_CONVERTER.toJson(
+                  new GenericRecordBuilder(VALUE_SCHEMA).set("value", 11).build()).getJson(),
+              /* partition= */ 0),
+          new SchemaTopicProduceRecord(
+              new IntNode(2),
+              AVRO_CONVERTER.toJson(
+                  new GenericRecordBuilder(VALUE_SCHEMA).set("value", 12).build()).getJson(),
+              /* partition= */ 0),
+          new SchemaTopicProduceRecord(
+              new IntNode(3),
+              AVRO_CONVERTER.toJson(
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v2/JsonSchemaProduceConsumeTest.java

@@ -1,0 +1,77 @@
+package io.confluent.kafkarest.integration.v2;
+
+import com.fasterxml.jackson.databind.JsonNode;
+import com.fasterxml.jackson.databind.ObjectMapper;
+import com.fasterxml.jackson.databind.node.IntNode;
+import com.fasterxml.jackson.databind.node.ObjectNode;
+import io.confluent.kafka.schemaregistry.ParsedSchema;
+import io.confluent.kafka.schemaregistry.json.JsonSchema;
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.converters.JsonSchemaConverter;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.v2.SchemaTopicProduceRequest.SchemaTopicProduceRecord;
+
+import java.util.Arrays;
+import java.util.List;
+
+public final class JsonSchemaProduceConsumeTest extends SchemaProduceConsumeTest {
+
+  private static final JsonSchemaConverter JSON_SCHEMA_CONVERTER = new JsonSchemaConverter();
+
+  private static final JsonSchema KEY_SCHEMA =
+      new JsonSchema("{\"type\":\"number\"}");
+
+  private static final JsonSchema VALUE_SCHEMA =
+      new JsonSchema("{\"type\":\"object\",\"properties\":{\"value\":{\"type\":\"number\"}}}");
+
+  private static final List<SchemaTopicProduceRecord> PRODUCE_RECORDS =
+      Arrays.asList(
+          new SchemaTopicProduceRecord(
+              new IntNode(1),
+              JSON_SCHEMA_CONVERTER.toJson(getMessage(11)).getJson(),
+              /* partition= */ 0),
+          new SchemaTopicProduceRecord(
+              new IntNode(2),
+              JSON_SCHEMA_CONVERTER.toJson(getMessage(12)).getJson(),
+              /* partition= */ 0),
+          new SchemaTopicProduceRecord(
+              new IntNode(3),
+              JSON_SCHEMA_CONVERTER.toJson(getMessage(13)).getJson(),
+              /* partition= */ 0));
+
+  private static JsonNode getMessage(int value) {
+    ObjectMapper objectMapper = new ObjectMapper();
+    ObjectNode root = objectMapper.createObjectNode();
+    root.put("value", value);
+    return root;
+  }
+
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v2/ProtobufProduceConsumeTest.java

@@ -1,0 +1,77 @@
+package io.confluent.kafkarest.integration.v2;
+
+import com.google.protobuf.Descriptors;
+import com.google.protobuf.DynamicMessage;
+import com.google.protobuf.Message;
+import io.confluent.kafka.schemaregistry.ParsedSchema;
+import io.confluent.kafka.schemaregistry.protobuf.ProtobufSchema;
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.converters.ProtobufConverter;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.v2.SchemaTopicProduceRequest.SchemaTopicProduceRecord;
+
+import java.util.Arrays;
+import java.util.List;
+
+public final class ProtobufProduceConsumeTest extends SchemaProduceConsumeTest {
+
+  private static final ProtobufConverter PROOTBUF_CONVERTER = new ProtobufConverter();
+
+  private static final ProtobufSchema KEY_SCHEMA =
+      new ProtobufSchema("syntax = \"proto3\"; message KeyRecord { int32 key = 1; }");
+
+  private static final ProtobufSchema VALUE_SCHEMA =
+      new ProtobufSchema("syntax = \"proto3\"; message ValueRecord { int32 value = 1; }");
+
+  private static final List<SchemaTopicProduceRecord> PRODUCE_RECORDS =
+      Arrays.asList(
+          new SchemaTopicProduceRecord(
+              PROOTBUF_CONVERTER.toJson(getMessage(KEY_SCHEMA, "key", 1)).getJson(),
+              PROOTBUF_CONVERTER.toJson(getMessage(VALUE_SCHEMA, "value", 11)).getJson(),
+              /* partition= */ 0),
+          new SchemaTopicProduceRecord(
+              PROOTBUF_CONVERTER.toJson(getMessage(KEY_SCHEMA, "key", 2)).getJson(),
+              PROOTBUF_CONVERTER.toJson(getMessage(VALUE_SCHEMA, "value", 12)).getJson(),
+              /* partition= */ 0),
+          new SchemaTopicProduceRecord(
+              PROOTBUF_CONVERTER.toJson(getMessage(KEY_SCHEMA, "key", 3)).getJson(),
+              PROOTBUF_CONVERTER.toJson(getMessage(VALUE_SCHEMA, "value", 13)).getJson(),
+              /* partition= */ 0));
+
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v2/SchemaProduceConsumeTest.java

@@ -1,0 +1,172 @@
+package io.confluent.kafkarest.integration.v2;
+
+import static java.util.Collections.singletonList;
+import static java.util.Collections.unmodifiableMap;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.fail;
+
+import com.fasterxml.jackson.databind.JsonNode;
+import io.confluent.kafka.schemaregistry.ParsedSchema;
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.v2.ConsumerSubscriptionRecord;
+import io.confluent.kafkarest.entities.v2.CreateConsumerInstanceRequest;
+import io.confluent.kafkarest.entities.v2.CreateConsumerInstanceResponse;
+import io.confluent.kafkarest.entities.v2.SchemaConsumerRecord;
+import io.confluent.kafkarest.entities.v2.SchemaTopicProduceRequest;
+import io.confluent.kafkarest.entities.v2.SchemaTopicProduceRequest.SchemaTopicProduceRecord;
+import io.confluent.kafkarest.integration.ClusterTestHarness;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Map;
+import java.util.Map.Entry;
+import javax.ws.rs.client.Entity;
+import javax.ws.rs.core.GenericType;
+import javax.ws.rs.core.Response;
+import javax.ws.rs.core.Response.Status;
+import org.junit.Test;
+
+public abstract class SchemaProduceConsumeTest extends ClusterTestHarness {
+
+  private static final String TOPIC = "topic-1";
+
+  private static final String CONSUMER_GROUP = "group-1";
+
+  public SchemaProduceConsumeTest(int numBrokers, boolean withSchemaRegistry) {
+    super(numBrokers, withSchemaRegistry);
+  }
+
+  protected abstract EmbeddedFormat getFormat();
+
+  protected abstract String getContentType();
+
+  protected abstract ParsedSchema getKeySchema();
+
+  protected abstract ParsedSchema getValueSchema();
+
+  protected abstract List<SchemaTopicProduceRecord> getProduceRecords();
+
+  @Test
+  public void produceThenConsume_returnsExactlyProduced() {
+    createTopic(TOPIC, /* numPartitions= */ 1, /* replicationFactor= */ (short) 1);
+
+    Response createConsumerInstanceResponse =
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v3/BrokersResourceIntegrationTest.java

@@ -1,0 +1,230 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.integration.v3;
+
+import static org.junit.Assert.assertEquals;
+
+import io.confluent.kafkarest.entities.v3.BrokerData;
+import io.confluent.kafkarest.entities.v3.BrokerDataList;
+import io.confluent.kafkarest.entities.v3.GetBrokerResponse;
+import io.confluent.kafkarest.entities.v3.ListBrokersResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.Resource.Metadata;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.integration.ClusterTestHarness;
+import java.util.ArrayList;
+import java.util.Arrays;
+import javax.ws.rs.core.MediaType;
+import javax.ws.rs.core.Response;
+import javax.ws.rs.core.Response.Status;
+import org.apache.kafka.common.Node;
+import org.junit.Test;
+
+public class BrokersResourceIntegrationTest extends ClusterTestHarness {
+
+  public BrokersResourceIntegrationTest() {
+    super(/* numBrokers= */ 3, /* withSchemaRegistry= */ false);
+  }
+
+  @Test
+  public void listBrokers_existingCluster_returnsBrokers() {
+    String baseUrl = restConnect;
+    String clusterId = getClusterId();
+    ArrayList<Node> nodes = getBrokers();
+
+    ListBrokersResponse expected =
+        ListBrokersResponse.create(
+            BrokerDataList.builder()
+                .setMetadata(
+                    ResourceCollection.Metadata.builder()
+                        .setSelf(baseUrl + "/v3/clusters/" + clusterId + "/brokers")
+                        .build())
+                .setData(
+                    Arrays.asList(
+                        BrokerData.builder()
+                            .setMetadata(
+                                Resource.Metadata.builder()
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v3/ConsumerGroupsResourceIntegrationTest.java

@@ -1,0 +1,244 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.integration.v3;
+
+import static java.util.Collections.singletonList;
+import static org.junit.Assert.assertEquals;
+
+import io.confluent.kafkarest.entities.ConsumerGroup.State;
+import io.confluent.kafkarest.entities.v3.ConsumerGroupData;
+import io.confluent.kafkarest.entities.v3.ConsumerGroupDataList;
+import io.confluent.kafkarest.entities.v3.GetConsumerGroupResponse;
+import io.confluent.kafkarest.entities.v3.ListConsumerGroupsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.Resource.Relationship;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.integration.ClusterTestHarness;
+import java.time.Duration;
+import java.util.Arrays;
+import java.util.Properties;
+import javax.ws.rs.core.MediaType;
+import javax.ws.rs.core.Response;
+import javax.ws.rs.core.Response.Status;
+import org.apache.kafka.clients.consumer.ConsumerConfig;
+import org.apache.kafka.clients.consumer.KafkaConsumer;
+import org.apache.kafka.common.serialization.BytesDeserializer;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+@RunWith(JUnit4.class)
+public class ConsumerGroupsResourceIntegrationTest extends ClusterTestHarness {
+
+  public ConsumerGroupsResourceIntegrationTest() {
+    super(/* numBrokers= */ 1, /* withSchemaRegistry= */ false);
+  }
+
+  @Test
+  public void listConsumerGroups_returnsConsumerGroups() {
+    String baseUrl = restConnect;
+    String clusterId = getClusterId();
+
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v3/PartitionsResourceIntegrationTest.java

@@ -1,0 +1,217 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.integration.v3;
+
+import static java.util.Collections.singletonList;
+import static org.junit.Assert.assertEquals;
+
+import io.confluent.kafkarest.entities.v3.GetPartitionResponse;
+import io.confluent.kafkarest.entities.v3.ListPartitionsResponse;
+import io.confluent.kafkarest.entities.v3.PartitionData;
+import io.confluent.kafkarest.entities.v3.PartitionDataList;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.integration.ClusterTestHarness;
+import javax.ws.rs.core.MediaType;
+import javax.ws.rs.core.Response;
+import javax.ws.rs.core.Response.Status;
+import org.junit.Before;
+import org.junit.Test;
+
+public class PartitionsResourceIntegrationTest extends ClusterTestHarness {
+
+  private static final String TOPIC_NAME = "topic-1";
+
+  public PartitionsResourceIntegrationTest() {
+    super(/* numBrokers= */ 1, /* withSchemaRegistry= */ false);
+  }
+
+  @Before
+  @Override
+  public void setUp() throws Exception {
+    super.setUp();
+
+    createTopic(TOPIC_NAME, 1, (short) 1);
+  }
+
+  @Test
+  public void listPartitions_existingTopic_returnPartitions() {
+    String baseUrl = restConnect;
+    String clusterId = getClusterId();
+
+    ListPartitionsResponse expected =
+        ListPartitionsResponse.create(
+            PartitionDataList.builder()
+                .setMetadata(
+                    ResourceCollection.Metadata.builder()
+                        .setSelf(
+                            baseUrl
+                                + "/v3/clusters/" + clusterId
+                                + "/topics/" + TOPIC_NAME
+                                + "/partitions")
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v3/ReplicasResourceIntegrationTest.java

@@ -1,0 +1,218 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.integration.v3;
+
+import static java.util.Collections.singletonList;
+import static org.junit.Assert.assertEquals;
+
+import io.confluent.kafkarest.entities.v3.GetReplicaResponse;
+import io.confluent.kafkarest.entities.v3.ListReplicasResponse;
+import io.confluent.kafkarest.entities.v3.ReplicaData;
+import io.confluent.kafkarest.entities.v3.ReplicaDataList;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.integration.ClusterTestHarness;
+import javax.ws.rs.core.MediaType;
+import javax.ws.rs.core.Response;
+import javax.ws.rs.core.Response.Status;
+import org.junit.Before;
+import org.junit.Test;
+
+public class ReplicasResourceIntegrationTest extends ClusterTestHarness {
+
+  private static final String TOPIC_NAME = "topic-1";
+
+  public ReplicasResourceIntegrationTest() {
+    super(/* numBrokers= */ 1, /* withSchemaRegistry= */ false);
+  }
+
+  @Before
+  @Override
+  public void setUp() throws Exception {
+    super.setUp();
+
+    createTopic(TOPIC_NAME, 1, (short) 1);
+  }
+
+  @Test
+  public void listReplicas_existingPartition_returnsReplicas() {
+    String baseUrl = restConnect;
+    String clusterId = getClusterId();
+
+    ListReplicasResponse expected =
+        ListReplicasResponse.create(
+            ReplicaDataList.builder()
+                .setMetadata(
+                    ResourceCollection.Metadata.builder()
+                        .setSelf(
+                            baseUrl
+                                + "/v3/clusters/" + clusterId
+                                + "/topics/" + TOPIC_NAME
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v3/TopicConfigsResourceIntegrationTest.java

@@ -1,0 +1,650 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.integration.v3;
+
+import static io.confluent.kafkarest.TestUtils.testWithRetry;
+import static java.util.Collections.singletonList;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertTrue;
+
+import io.confluent.kafkarest.entities.ConfigSource;
+import io.confluent.kafkarest.entities.v3.ConfigSynonymData;
+import io.confluent.kafkarest.entities.v3.GetTopicConfigResponse;
+import io.confluent.kafkarest.entities.v3.ListTopicConfigsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.entities.v3.TopicConfigData;
+import io.confluent.kafkarest.integration.ClusterTestHarness;
+import java.util.Arrays;
+import javax.ws.rs.client.Entity;
+import javax.ws.rs.core.MediaType;
+import javax.ws.rs.core.Response;
+import javax.ws.rs.core.Response.Status;
+import org.junit.Before;
+import org.junit.Test;
+
+public class TopicConfigsResourceIntegrationTest extends ClusterTestHarness {
+
+  private static final String TOPIC_1 = "topic-1";
+
+  public TopicConfigsResourceIntegrationTest() {
+    super(/* numBrokers= */ 1, /* withSchemaRegistry= */ false);
+  }
+
+  @Before
+  @Override
+  public void setUp() throws Exception {
+    super.setUp();
+
+    createTopic(TOPIC_1, 1, (short) 1);
+  }
+
+  @Test
+  public void listTopicConfigs_existingTopic_returnsConfigs() {
+    String baseUrl = restConnect;
+    String clusterId = getClusterId();
+
+    ResourceCollection.Metadata expectedMetadata =
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/integration/v3/TopicsResourceIntegrationTest.java

@@ -1,0 +1,641 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.integration.v3;
+
+import static io.confluent.kafkarest.TestUtils.*;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertFalse;
+import static org.junit.Assert.assertTrue;
+
+import io.confluent.kafkarest.entities.ConfigSource;
+import io.confluent.kafkarest.entities.v3.ConfigSynonymData;
+import io.confluent.kafkarest.entities.v3.CreateTopicResponse;
+import io.confluent.kafkarest.entities.v3.GetTopicConfigResponse;
+import io.confluent.kafkarest.entities.v3.GetTopicResponse;
+import io.confluent.kafkarest.entities.v3.ListTopicsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.entities.v3.TopicConfigData;
+import io.confluent.kafkarest.entities.v3.TopicData;
+import io.confluent.kafkarest.entities.v3.TopicDataList;
+import io.confluent.kafkarest.integration.ClusterTestHarness;
+import java.util.Arrays;
+import java.util.Properties;
+import javax.ws.rs.client.Entity;
+import javax.ws.rs.core.MediaType;
+import javax.ws.rs.core.Response;
+import javax.ws.rs.core.Response.Status;
+import org.junit.Before;
+import org.junit.Test;
+
+public class TopicsResourceIntegrationTest extends ClusterTestHarness {
+
+  private static final String TOPIC_1 = "topic-1";
+  private static final String TOPIC_2 = "topic-2";
+  private static final String TOPIC_3 = "topic-3";
+
+  public TopicsResourceIntegrationTest() {
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/resources/v2/RootResourceTest.java

@@ -1,0 +1,77 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v2;
+
+import static io.confluent.kafkarest.TestUtils.assertErrorResponse;
+import static io.confluent.kafkarest.TestUtils.assertOKResponse;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertNull;
+
+import io.confluent.kafkarest.KafkaRestApplication;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.TestUtils;
+import io.confluent.kafkarest.Versions;
+import io.confluent.rest.EmbeddedServerTestHarness;
+import io.confluent.rest.RestConfigException;
+import java.util.Map;
+import javax.ws.rs.client.Entity;
+import javax.ws.rs.core.GenericType;
+import javax.ws.rs.core.Response;
+import org.junit.Test;
+
+public class RootResourceTest
+    extends EmbeddedServerTestHarness<KafkaRestConfig, KafkaRestApplication> {
+
+  public RootResourceTest() throws RestConfigException {
+    addResource(RootResource.class);
+  }
+
+  @Test
+  public void testRootResource() {
+    Response response = request("/", Versions.KAFKA_V2_JSON).get();
+    assertOKResponse(response, Versions.KAFKA_V2_JSON);
+    Map<String, String> decoded = TestUtils.tryReadEntityOrLog(response, new GenericType<Map<String, String>>() {
+    });
+  }
+
+  @Test
+  public void testInvalidAcceptMediatype() {
+    Response response = request("/", "text/plain").get();
+    // We would like to check for a normal error response, but Jersey/JAX-RS and possibly the
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/resources/v2/TopicsResourceBinaryProduceTest.java

@@ -1,0 +1,327 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v2;
+
+import static io.confluent.kafkarest.TestUtils.assertErrorResponse;
+import static io.confluent.kafkarest.TestUtils.assertOKResponse;
+import static org.easymock.EasyMock.eq;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.isA;
+import static org.easymock.EasyMock.replay;
+import static org.easymock.EasyMock.verify;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertNull;
+
+import com.fasterxml.jackson.databind.node.NullNode;
+import com.fasterxml.jackson.databind.node.TextNode;
+import com.google.protobuf.ByteString;
+import io.confluent.kafkarest.Errors;
+import io.confluent.kafkarest.KafkaRestApplication;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.TestUtils;
+import io.confluent.kafkarest.Versions;
+import io.confluent.kafkarest.common.CompletableFutures;
+import io.confluent.kafkarest.controllers.ProduceController;
+import io.confluent.kafkarest.controllers.RecordSerializer;
+import io.confluent.kafkarest.controllers.SchemaManager;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.ProduceResult;
+import io.confluent.kafkarest.entities.v2.PartitionOffset;
+import io.confluent.kafkarest.entities.v2.ProduceRequest;
+import io.confluent.kafkarest.entities.v2.ProduceRequest.ProduceRecord;
+import io.confluent.kafkarest.entities.v2.ProduceResponse;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/resources/v3/BrokersResourceTest.java

@@ -1,0 +1,214 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static io.confluent.kafkarest.common.CompletableFutures.failedFuture;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.junit.Assert.assertEquals;
+
+import io.confluent.kafkarest.controllers.BrokerManager;
+import io.confluent.kafkarest.entities.Broker;
+import io.confluent.kafkarest.entities.v3.BrokerData;
+import io.confluent.kafkarest.entities.v3.BrokerDataList;
+import io.confluent.kafkarest.entities.v3.GetBrokerResponse;
+import io.confluent.kafkarest.entities.v3.ListBrokersResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.Resource.Metadata;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.response.CrnFactoryImpl;
+import io.confluent.kafkarest.response.FakeAsyncResponse;
+import io.confluent.kafkarest.response.FakeUrlFactory;
+import java.util.Arrays;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+import javax.ws.rs.NotFoundException;
+import org.easymock.EasyMockRule;
+import org.easymock.Mock;
+import org.junit.Before;
+import org.junit.Rule;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+@RunWith(JUnit4.class)
+public final class BrokersResourceTest {
+
+  private static final String CLUSTER_ID = "cluster-1";
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/resources/v3/ConsumerAssignmentsResourceTest.java

@@ -1,0 +1,232 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static java.util.concurrent.CompletableFuture.completedFuture;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.junit.Assert.assertEquals;
+
+import io.confluent.kafkarest.controllers.ConsumerAssignmentManager;
+import io.confluent.kafkarest.entities.ConsumerAssignment;
+import io.confluent.kafkarest.entities.v3.ConsumerAssignmentData;
+import io.confluent.kafkarest.entities.v3.ConsumerAssignmentDataList;
+import io.confluent.kafkarest.entities.v3.GetConsumerAssignmentResponse;
+import io.confluent.kafkarest.entities.v3.ListConsumerAssignmentsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.Resource.Relationship;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.response.CrnFactoryImpl;
+import io.confluent.kafkarest.response.FakeAsyncResponse;
+import io.confluent.kafkarest.response.FakeUrlFactory;
+import java.util.Arrays;
+import java.util.Optional;
+import javax.ws.rs.NotFoundException;
+import org.easymock.EasyMockRule;
+import org.easymock.Mock;
+import org.junit.Before;
+import org.junit.Rule;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+@RunWith(JUnit4.class)
+public class ConsumerAssignmentsResourceTest {
+
+  private static final String CLUSTER_ID = "cluster-1";
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/resources/v3/PartitionsResourceTest.java

@@ -1,0 +1,311 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static io.confluent.kafkarest.common.CompletableFutures.failedFuture;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.junit.Assert.assertEquals;
+
+import io.confluent.kafkarest.controllers.PartitionManager;
+import io.confluent.kafkarest.entities.Partition;
+import io.confluent.kafkarest.entities.PartitionReplica;
+import io.confluent.kafkarest.entities.v3.GetPartitionResponse;
+import io.confluent.kafkarest.entities.v3.ListPartitionsResponse;
+import io.confluent.kafkarest.entities.v3.PartitionData;
+import io.confluent.kafkarest.entities.v3.PartitionDataList;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.response.CrnFactoryImpl;
+import io.confluent.kafkarest.response.FakeAsyncResponse;
+import io.confluent.kafkarest.response.FakeUrlFactory;
+import java.util.Arrays;
+import java.util.Optional;
+import java.util.concurrent.CompletableFuture;
+import javax.ws.rs.NotFoundException;
+import org.easymock.EasyMockRule;
+import org.easymock.Mock;
+import org.junit.Before;
+import org.junit.Rule;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+@RunWith(JUnit4.class)
+public class PartitionsResourceTest {
+
+  private static final String CLUSTER_ID = "cluster-1";
+  private static final String TOPIC_NAME = "topic-1";
+
+  private static final Partition PARTITION_1 =
+      Partition.create(
+          CLUSTER_ID,
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/resources/v3/ReplicasResourceTest.java

@@ -1,0 +1,242 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static io.confluent.kafkarest.common.CompletableFutures.failedFuture;
+import static java.util.concurrent.CompletableFuture.completedFuture;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.junit.Assert.assertEquals;
+
+import io.confluent.kafkarest.controllers.ReplicaManager;
+import io.confluent.kafkarest.entities.PartitionReplica;
+import io.confluent.kafkarest.entities.v3.GetReplicaResponse;
+import io.confluent.kafkarest.entities.v3.ListReplicasResponse;
+import io.confluent.kafkarest.entities.v3.ReplicaData;
+import io.confluent.kafkarest.entities.v3.ReplicaDataList;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.response.CrnFactoryImpl;
+import io.confluent.kafkarest.response.FakeAsyncResponse;
+import io.confluent.kafkarest.response.FakeUrlFactory;
+import java.util.Arrays;
+import java.util.Optional;
+import javax.ws.rs.NotFoundException;
+import org.easymock.EasyMockRule;
+import org.easymock.Mock;
+import org.junit.Before;
+import org.junit.Rule;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+@RunWith(JUnit4.class)
+public class ReplicasResourceTest {
+
+  private static final String CLUSTER_ID = "cluster-1";
+  private static final String TOPIC_NAME = "topic-1";
+  private static final int PARTITION_ID = 0;
+
+  private static final PartitionReplica REPLICA_1 =
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/resources/v3/TopicConfigsResourceTest.java

@@ -1,0 +1,359 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.resources.v3;
+
+import static io.confluent.kafkarest.common.CompletableFutures.failedFuture;
+import static java.util.Collections.emptyList;
+import static java.util.concurrent.CompletableFuture.completedFuture;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertNull;
+import static org.junit.Assert.assertTrue;
+
+import io.confluent.kafkarest.controllers.TopicConfigManager;
+import io.confluent.kafkarest.entities.ConfigSource;
+import io.confluent.kafkarest.entities.TopicConfig;
+import io.confluent.kafkarest.entities.v3.ConfigSynonymData;
+import io.confluent.kafkarest.entities.v3.GetTopicConfigResponse;
+import io.confluent.kafkarest.entities.v3.ListTopicConfigsResponse;
+import io.confluent.kafkarest.entities.v3.Resource;
+import io.confluent.kafkarest.entities.v3.ResourceCollection;
+import io.confluent.kafkarest.entities.v3.TopicConfigData;
+import io.confluent.kafkarest.entities.v3.TopicConfigDataList;
+import io.confluent.kafkarest.entities.v3.UpdateTopicConfigRequest;
+import io.confluent.kafkarest.response.CrnFactoryImpl;
+import io.confluent.kafkarest.response.FakeAsyncResponse;
+import io.confluent.kafkarest.response.FakeUrlFactory;
+import java.util.Arrays;
+import java.util.Optional;
+import java.util.stream.Collectors;
+import javax.ws.rs.NotFoundException;
+import org.easymock.EasyMockRule;
+import org.easymock.Mock;
+import org.junit.Before;
+import org.junit.Rule;
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/response/UrlFactoryImplTest.java

@@ -1,0 +1,259 @@
+/*
+ * Copyright 2020 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.response;
+
+import static java.util.Collections.emptyList;
+import static java.util.Collections.singletonList;
+import static org.easymock.EasyMock.expect;
+import static org.easymock.EasyMock.replay;
+import static org.junit.Assert.assertEquals;
+
+import java.net.URI;
+import javax.ws.rs.core.UriInfo;
+import org.easymock.EasyMockRule;
+import org.easymock.Mock;
+import org.junit.Rule;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+@RunWith(JUnit4.class)
+public class UrlFactoryImplTest {
+
+  @Rule
+  public final EasyMockRule mocks = new EasyMockRule(this);
+
+  @Mock
+  private UriInfo requestUriInfo;
+
+  @Test
+  public void create_withHostNameAndPortConfig_returnsUrlRelativeToHostNameAndPortConfig() {
+    expect(requestUriInfo.getAbsolutePath())
+        .andStubReturn(URI.create("http://1.2.3.4:1000/xxx/yyy"));
+    expect(requestUriInfo.getBaseUri()).andReturn(URI.create("http://1.2.3.4:1000/"));
+    replay(requestUriInfo);
+
+    UrlFactory urlFactory =
+        new UrlFactoryImpl("hostname", 2000, emptyList(), emptyList(), requestUriInfo);
+
+    String url = urlFactory.create("foo", "bar");
+
+    assertEquals("http://hostname:2000/foo/bar", url);
+  }
+
+  @Test
+  public void
+  create_withAdvertisedListenerSameScheme_returnsUrlRelativeToAdvertisedListenerSameScheme() {
+    expect(requestUriInfo.getAbsolutePath())
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/unit/AvroConverterTest.java

@@ -1,0 +1,202 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.unit;
+
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertNotNull;
+import static org.junit.Assert.assertTrue;
+import static org.junit.Assert.fail;
+
+import com.fasterxml.jackson.databind.node.JsonNodeFactory;
+import io.confluent.kafkarest.converters.AvroConverter;
+import io.confluent.kafkarest.converters.ConversionException;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import java.util.HashMap;
+import java.util.Map;
+import org.apache.avro.Schema;
+import org.apache.avro.generic.GenericData;
+import org.apache.avro.generic.GenericRecord;
+import org.apache.avro.generic.GenericRecordBuilder;
+import org.junit.Test;
+
+public class AvroConverterTest {
+
+  private static final Schema recordSchema = new Schema.Parser().parse(
+      "{\"namespace\": \"namespace\",\n"
+      + " \"type\": \"record\",\n"
+      + " \"name\": \"test\",\n"
+      + " \"fields\": [\n"
+      + "     {\"name\": \"null\", \"type\": \"null\"},\n"
+      + "     {\"name\": \"boolean\", \"type\": \"boolean\"},\n"
+      + "     {\"name\": \"int\", \"type\": \"int\"},\n"
+      + "     {\"name\": \"long\", \"type\": \"long\"},\n"
+      + "     {\"name\": \"float\", \"type\": \"float\"},\n"
+      + "     {\"name\": \"double\", \"type\": \"double\"},\n"
+      + "     {\"name\": \"bytes\", \"type\": \"bytes\"},\n"
+      + "     {\"name\": \"string\", \"type\": \"string\", \"aliases\": [\"string_alias\"]},\n"
+      + "     {\"name\": \"null_default\", \"type\": \"null\", \"default\": null},\n"
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/unit/DefaultKafkaRestContextTest.java

@@ -1,0 +1,79 @@
+package io.confluent.kafkarest.unit;
+
+import io.confluent.kafkarest.DefaultKafkaRestContext;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.KafkaRestContext;
+import java.util.concurrent.CopyOnWriteArraySet;
+import org.junit.Before;
+import org.junit.Test;
+import java.util.Properties;
+import java.util.Set;
+import java.util.concurrent.ExecutorService;
+import java.util.concurrent.Executors;
+import java.util.concurrent.TimeUnit;
+import org.junit.runner.RunWith;
+import org.junit.runners.JUnit4;
+
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertTrue;
+
+@RunWith(JUnit4.class)
+public class DefaultKafkaRestContextTest {
+
+    private KafkaRestContext context;
+
+    @Before
+    public void setUp() {
+        Properties props = new Properties();
+        // Required to satisfy config definition
+        props.put(KafkaRestConfig.BOOTSTRAP_SERVERS_CONFIG, "localhost:5234");
+        KafkaRestConfig restConfig = new KafkaRestConfig(props);
+
+        context = new DefaultKafkaRestContext(restConfig);
+    }
+
+    @Test
+    public void testGetProducerThreadSafety() throws InterruptedException {
+        Set<Object> refs = new CopyOnWriteArraySet<>();
+
+        ExecutorService executor = Executors.newFixedThreadPool(100);
+        // Captures reference as it's invoked.
+        for (int i = 0; i < 100; i++) {
+            executor.submit(() -> refs.add(context.getProducer()));
+        }
+        executor.shutdown();
+        assertTrue(executor.awaitTermination(60, TimeUnit.SECONDS));
+
+        assertEquals(1, refs.size());
+    }
+
+    @Test
+    public void testGetKafkaConsumerManagerThreadSafety() throws InterruptedException {
+        Set<Object> refs = new CopyOnWriteArraySet<>();
+
+        ExecutorService executor = Executors.newFixedThreadPool(100);
+        // Captures reference as it's invoked.
+        for (int i = 0; i < 100; i++) {
+            executor.submit(() -> refs.add(context.getKafkaConsumerManager()));
+        }
+        executor.shutdown();
+        assertTrue(executor.awaitTermination(60, TimeUnit.SECONDS));
+
+        assertEquals(1, refs.size());
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/unit/ProtobufConverterTest.java

@@ -1,0 +1,218 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+
+package io.confluent.kafkarest.unit;
+
+import com.fasterxml.jackson.databind.JsonNode;
+import com.fasterxml.jackson.databind.node.JsonNodeFactory;
+import com.google.protobuf.ByteString;
+import com.google.protobuf.Descriptors.Descriptor;
+import com.google.protobuf.Descriptors.FieldDescriptor;
+import com.google.protobuf.DynamicMessage;
+import io.confluent.kafka.schemaregistry.protobuf.ProtobufSchema;
+import io.confluent.kafkarest.TestUtils;
+import io.confluent.kafkarest.converters.ProtobufConverter;
+import io.confluent.kafkarest.converters.SchemaConverter;
+import org.junit.Test;
+
+import java.util.Arrays;
+import java.util.List;
+
+import static org.junit.Assert.assertArrayEquals;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertNotNull;
+import static org.junit.Assert.assertTrue;
+
+public class ProtobufConverterTest {
+
+  private static final String recordSchemaString =
+          "syntax = \"proto3\";\n" +
+          "\n" +
+          "option java_package = \"io.confluent.kafka.serializers.protobuf.test\";\n" +
+          "option java_outer_classname = \"TestMessageProtos\";\n" +
+          "\n" +
+          "import \"google/protobuf/descriptor.proto\";\n" +
+          "\n" +
+          "message TestMessage {\n" +
+          "    string test_string = 1 [json_name = \"test_str\"];\n" +
+          "    bool test_bool = 2;\n" +
+          "    bytes test_bytes = 3;\n" +
+          "    double test_double = 4;\n" +
+          "    float test_float = 5;\n" +
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/kafka-rest/src/test/java/io/confluent/kafkarest/v2/KafkaConsumerManagerTest.java

@@ -1,0 +1,643 @@
+/*
+ * Copyright 2018 Confluent Inc.
+ *
+ * Licensed under the Confluent Community License (the "License"); you may not use
+ * this file except in compliance with the License.  You may obtain a copy of the
+ * License at
+ *
+ * http://www.confluent.io/confluent-community-license
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS, WITHOUT
+ * WARRANTIES OF ANY KIND, either express or implied.  See the License for the
+ * specific language governing permissions and limitations under the License.
+ */
+package io.confluent.kafkarest.v2;
+
+import static java.util.Collections.singletonMap;
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertFalse;
+import static org.junit.Assert.assertNotNull;
+import static org.junit.Assert.assertNull;
+import static org.junit.Assert.assertTrue;
+import static org.junit.Assert.fail;
+
+import com.google.protobuf.ByteString;
+import io.confluent.kafkarest.ConsumerReadCallback;
+import io.confluent.kafkarest.KafkaRestConfig;
+import io.confluent.kafkarest.entities.ConsumerInstanceConfig;
+import io.confluent.kafkarest.entities.ConsumerRecord;
+import io.confluent.kafkarest.entities.EmbeddedFormat;
+import io.confluent.kafkarest.entities.TopicPartitionOffset;
+import io.confluent.kafkarest.entities.v2.ConsumerOffsetCommitRequest;
+import io.confluent.kafkarest.entities.v2.ConsumerSubscriptionRecord;
+import java.time.Duration;
+import java.time.Instant;
+import java.util.Arrays;
+import java.util.Collections;
+import java.util.List;
+import java.util.Properties;
+import java.util.concurrent.ExecutionException;
+import java.util.concurrent.TimeUnit;
+import org.apache.kafka.clients.consumer.ConsumerConfig;
+import org.apache.kafka.clients.consumer.OffsetResetStrategy;
+import org.apache.kafka.common.TopicPartition;
+import org.easymock.Capture;
+import org.easymock.EasyMock;
+import org.easymock.EasyMockRunner;
+import org.easymock.Mock;
+import org.junit.After;
+import org.junit.Before;
+import org.junit.Ignore;
+import org.junit.Test;
+import org.junit.runner.RunWith;
+
+/**
[…]

### 2021-04-15 Code/benchmarks/realworld/FFI/kafka-rest/testing/environments/minimal/run.sh

@@ -1,0 +1,58 @@
+#!/bin/bash
+#
+# Copyright 2020 Confluent Inc.
+#
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+# http://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+set -euo pipefail
+
+# Use -d to start containers in detached mode.
+detach=
+
+while getopts "d" opt
+do
+  case "$opt" in
+    d) detach=-d;;
+    *) echo "Usage: $0 [-d]" >&2
+       exit 1 ;;
+  esac
+done
+shift "$((OPTIND - 1))"
+
+env_dir=$(dirname "$0")
+base_dir=$env_dir/../../..
+
+# Login to nightly docker repository.
+aws ecr get-login-password --region us-west-2 \
+ | docker login --username AWS --password-stdin 368821881613.dkr.ecr.us-west-2.amazonaws.com/confluentinc/
+
+# Download latest cp-zookeeper image.
+docker pull 368821881613.dkr.ecr.us-west-2.amazonaws.com/confluentinc/cp-zookeeper:master-latest
+
+# Download latest cp-server image.
+docker pull 368821881613.dkr.ecr.us-west-2.amazonaws.com/confluentinc/cp-server:master-latest
+
+# Download latest cp-schema-registry image.
+docker pull 368821881613.dkr.ecr.us-west-2.amazonaws.com/confluentinc/cp-schema-registry:master-latest
+
+# Download latest cp-kafka-rest image.
+docker pull 368821881613.dkr.ecr.us-west-2.amazonaws.com/confluentinc/cp-kafka-rest:master-latest
+
+# Make sure kafka-rest is packaged.
+mvn -f "$base_dir"/kafka-rest/pom.xml -Dmaven.test.skip=true clean package
+
+# For some reason `up --build --force-recreate` is not enough. Make sure everything is clean.
+docker-compose -f "$env_dir"/docker-compose.yml rm -fsv
+
+# Start all containers.
+docker-compose -f "$env_dir"/docker-compose.yml up --build --force-recreate $detach

### 2021-04-15 My-Papers/SpecHunter/overview.tex
paper stuffs

--- 2021-04-04 My-Papers/SpecHunter/overview.tex
@@
 
-\paragraph{Motivation}
+% SAVER보다는 MemFix를 참고하는 게 더 나을 것
+% Overview에 약 2 페이지가 사용되었다.
+% - 약 40%는 motivating example로 채웠고,
+% - 나머지 60%는 concrete한 동작 방식으로 채웠다.
 
-% TODO
-Swan sucks: too much variance on its performance depending on dataset quality/quantity
+\subsection{A Simple Example}
 
-\subsection{Overview of our System}
+\lstinputlisting[language=Java]{./Codes/OverviewExample.java}
 
-% 적당한 figure 하나 넣자
+We illustrate our approach with a simple example. Figure \emph{xx} contains a
+Spring program that interacts with a DBMS via APIs provided bySpring's
+\texttt{JdbcTemplate}. (We assume that necessary modules are imported
+beforehand.) Although the program is short, There are two kinds of
+data flows present in this program. First is one that starts from
+the standart input and comes into the program via \texttt{Scanner.nextLine()},
+flows into \texttt{RelationalData.run()}, which passes it to
+\texttt{JdbcTemplate.batchUpdate()} for database insertion. The another comes from
+the DBMS via \texttt{JdbcTemplate.queryForMap()} for database querying, and then
+flows to the \texttt{Logger.info()} function, which emits this information
+outside the program, to the standard output.
 
-Figure 1 shows the overall workflow of SpecHunter. Given a Java application's
-source code, SpecHunter labels all API methods provided by the library the application
-uses. There are three main issues regarding building an effective interactive system:
-namely, constructing the network, effectively propagating the evidence given from the
-oracle, and making the system scale to run on large input applications.
-% Question: Should we define what "API" means?
+These data flows pose two security risks: one is an SQL injection (CWE-89),
+and another is insertion of sensitive information into log file (CWE-532).
+Therefore, for a taint analyzer to detect these data flows, one must mark
+\texttt{Scanner.nextLine()} and \texttt{JdbcTemplate.queryForMap()} as sources,
+\texttt{JdbcTemplate.batchUpdate()} and \texttt{Logger.info()} as their respective
+sinks.
 
-\subsection{Network Construction}
-
-\paragraph{Determining Edges}
-
-% Network Construction은 반드시 Scalability and Efficiency와 연관되게 되어 있다.
-% 그 점을 유념하면서 쓰자: 적절한 pointer 달아 주기.
-Here we describe how we represent the input java project into a large graph form, which will
-later be turned into a series of Bayesian networks. How we splitt this large
-graph into several Bayesian networks will be discussed in the next section. % TODO 좀 더 자연스러운 포인터??
-We hope to create a graph $G=(V, E)$,
-where $V$ is the set of all methods used or defined in the given application, and $E$ is a
-subset of $V\times V$, whose elements are gathered in three different ways.
-
-First, there are data-flow-edges. We perform a variant of a data-flow analysis on the
-given input application to calculate lifetimes of all access paths found in the
-entire codes, starting from being defined and ending by being ``dead'', between
-which the access path may be ``redefined''.
-% 여기서 간단한 예제 넣어주기
-
-\lstinputlisting[language=Java]{./Codes/SimpleExample.java}
-
-In the above example, a variable \texttt{x} is being defined to hold the value \texttt{1} in the method
-\texttt{f}, using another method \texttt{m1}. This value flows to \texttt{g}, where this
-value is redefined as \texttt{2} using the method \texttt{m2}. After this redefined
-value flows to method \texttt{m3} via \texttt{h}, it is no longer used after the call to
-\texttt{println}. Here, our goal is to capture this lifecycle. To compute these
-for all access paths in the program, we first run a static analysis designed as follows:
-
-\begin{align*}
-  A &\in \mathbb{D} &= \mathbb{C}\rightarrow\mathcal{P}(State)\\
-  s &\in State &= Procname\times Var\times Loc\times Alias\\
-  p &\in Procname &\subseteq Var\\
-  a &\in Alias &\subseteq \mathcal{P}(Var)
-\end{align*}
-
-For example, for an assignment statement \texttt{int a = b;} inside a procedure
-\texttt{f} at line 3, we obtain the tuple set \texttt{\{(f, a, 3, \{a, b\})\}}.
-The fourth component of the tuple means that \texttt{a} and \texttt{b} are
-aliases. After we create such tuples for each program point, we finally construct
-\emph{propagation chains} by threading the tuples via alias relations. The
-relevant generated tuples for our goal is:
+There are 6 APIs in this program, and we would like to label the APIs with 
+as least number of hints given from the oracle as possible:
 
 \begin{itemize}
-\item \texttt{\{(f, x, 14, \{x, y\})\}}
-\item \texttt{\{(g, y, 18, \{y, u1\})\}}
-\item \texttt{\{(m2, u1, 5, \{u1\})\}}
-\item \texttt{\{(m2, u1, 6, \{u1\})\}}
-\item \texttt{\{(g, z, 6, \{z, u1, w\})\}}
-\item \texttt{\{(g, w, 23, \{w, u2\})\}}
-\item \texttt{\{(m3, u2, 9, \{u2, println\_1\})\}}
+\item \texttt{RelationalData.run()} is a source,
+\item \texttt{JdbcTemplate.batchUpdate()} is a sink,
+\item \texttt{JdbcTemplate.queryForMap()} is a source,
+\item \texttt{Logger.info()} is a sink, and
+\item \texttt{Map.get()} and \texttt{SpringApplication.run()} are none of the three.
 \end{itemize}
 
->
-where \texttt{println\_1} is a Mangled parameter variable of \texttt{println}.
-Now, connecting the tuples with the aliases, we get two chains:
-\texttt{x -> y -> u1} and \texttt{u1 -> z -> w -> u2 -> println\_1}. Since \texttt{u1} is
-redefined in \texttt{m2}, we glue the two together to get the originally desired
-information: \texttt{x -> y -> u1 -> z -> w -> u2 -> println\_1}. This translates
-into data-flow edges: \texttt{(f, g)}, \texttt{(f, h)}, and \texttt{(m3, println)}.
-
-% TODO 아 이거 실제로 돌려봐서 확인해야 할 거 같은데.. 실제로 이렇게 나오나...?
-
-% TODO static callee가 무엇인지를 좀 알아와서 디테일을 추가할 것.
-Second, there are call-edges. Since we used Facebook's Infer (fbinfer.com/) to
-implement our static analysis, we used Infer's facility to compute static
-callees of a given method to draw the entire callgraph of a given application
-code. For each caller \texttt{f} and its callee \texttt{g}, we add an edge
-\texttt{(f, g)}.
-
-Last but not least, there are similarity-edges. The idea is to take any two
-methods and score its pairwise similarity, and leave only the pairs with score
-above a predefined threshold. We measure them against two large groups of
-criteria: the ``syntactic features'' and ``semantic features''. For the
-syntactic features, we borrrowed largely from \textbf{Swan}'s features that
-check how names of methods or their return types are composed. The below
-figure % TODO: Figure 번호 달기...
-shows all the features we used.
-
-% TODO 표 삐져나간다..!!!!
-\begin{center}
-  \begin{tabular} { |c|c|c| }
-    \hline
-    Syntactic & Semantic\\
-    \hline
-    \hline
-    Both has parameters? & Both has at least one same callee?\\
-    Both has return type? & Both are making calls but not passing data?\\
-    Both contains same word in method name? & Both are being called but not being passed data?\\
-    Both contains same word in class name? & Both are making data flow calls?\\
-    Both has return type contained in parameter type? & Both are being passed data and passing data simultaneously?\\
-    Both has same return type? & Both are being passed data which gets dead in them?\\
-    Both has return type contained in method name? & Both has variable redefinitions?\\
-    \hline
-  \end{tabular}
-\end{center}
-
-By combining all three kinds of edges, we get a finished graph where every node
-is represents a node, and every edge represent how one method relates to another.
-
-\paragraph{Determining CPTs}
-
-After we determine which and which methods should be connected with a directed
-edge, we then define a conditional probability table (CPT) for each directed
-edge. This step is essential since CPTs are essential components of Bayesian
-Networks and we want our big graph to be broken down into small
-Bayesian networks. Each node should have its own CPT, and it express how the
-node's marginal distribution depends
-on those of the parent nodes. We use largely two different CPT schemas:
-that of the dataflow-edges and those of the call- and similarity-edges.
-Regardless of the schemas, the CPT's size is $4\times 4^n$, where $n$ is the
-number of parent nodes of a node. The below figure demonstrates a CPT of a node
-with two parent nodes, each shooting a data-flow edge to this node.
-
-% TODO 텍스트로만 써 놓은 걸 실제로 색칠하기.
-% VH -> Red, High -> Orange,
-% Low -> Green, VL -> Blue
-\begin{center}
-  \begin{tabular} { |c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c| }
-    \hline
-    vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl  \\
-    high & vl   & high & high & vl   & vl   & vl   & vl   & high & vl   & high & high & high & vl   & high & high\\
-    high & vl   & vl   & high & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & high & vl   & vl   & high\\
-    high & vl   & high & high & vl   & vl   & vl   & vl   & high & vl   & high & high & high & vl   & high & high\\
-    \hline
-  \end{tabular}
-\end{center}
-
-Let us first start with the data-flow schemas. In the above table, red cells
-should contain very high probabilities, orange
-cells should contain relatively high probabilities, whereas green cells should
-be assigned low probabilities, and blue cells should be of very low probabilities.
-The idea is this: by the definitions of ``source'', ``sanitizer'', and ``sink'',
-data must flow from a source to a sink through possibly a sanitizer, but it
-cannot flow in any other sequence of such methods. (For example, data cannot
-possibly flow from a sink through a source to a sanitizer.) Also, we note that
-any number of ``none'' methods, which are none of the three, can be interleaved
-freely between a source and a sanitizer, and between a sanitizer and a sink.
-Therefore, we encode these possibilities into a tabular form containing probabilities
-like the above.
-
-For the call-edges and similarity-edges, we use the same schema for both. The
-below figure shows how we assign probabilities when a node has two parents, each
-shooting call-edges or similarity-edges to the node.
-
-% TODO 텍스트로만 써 놓은 걸 실제로 색칠하기.
-% VH -> Red, High -> Orange,
-% Low -> Green, VL -> Blue
-\begin{center}
-  \begin{tabular} { |c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c| }
-    \hline
-    high & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl  & vl   & vl   & vl  \\
-    vl   & vl   & vl   & vl   & vl   & high & vl   & vl   & vl   & vl   & vl   & vl   & vl  & vl   & vl   & vl  \\
-    vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & high & vl   & vl  & vl   & vl   & vl  \\
-    vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl   & vl  & vl   & vl   & high\\
-    \hline
-  \end{tabular}
-\end{center}
-% TODO 구현 상으로는 위의 high cell이 low cell로 되어 있는데, 나중에 *꼭*
-% 바꾸자. high cell로 두는 게 맞는 것 같다.
-
-% explanation: why do we make similarity edges share this schema with call edges?
-Combining these together, we can express the case of a node with two parents,
-one shooting a data-flow edge while another shoots a call- or similarity edge.
-
-% TODO 텍스트로만 써 놓은 걸 실제로 색칠하기.
-% VH -> Red, High -> Orange,
-% Low -> Green, VL -> Blue
-\begin{center}
-  \begin{tabular} { |c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c| }
-    \hline
-    low  & vl   & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & vl   & vl  \\
-    high & low  & high & high & vl   & low  & vl   & vl   & high & low  & cell & high & high & low  & high & high\\
-    high & vl   & low  & high & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & high & vl   & low  & high\\
-    high & vl   & high & vh   & vl   & vl   & vl   & low  & high & vl   & high & vh   & high & vl   & high & vh  \\
-    \hline
-  \end{tabular}
-\end{center}
-% TODO 여기도 구현 상으로는 위의 high cell이 low cell로 되어 있는데, 나중에 *꼭*
-% 바꾸자. high cell로 두는 게 맞는 것 같다.
-
-Since a CPT has a constraint that the sum of probabilities assigned to each cell
-of a column is 1, we can come up with the following formula to calculate a
-concrete probability value for a cell's relative magnitude of probability.
-Suppose we call four cells of a column $cell_1$, $cell_2$, $cell_3$, $cell_4$,
-then the probability value of one of the four cells is:
-
-\begin{equation*}
-  prob(cell) = \frac{mag(cell)\times coeff(mag(cell))}{\sum_{i=1}^{4}mag(cell)\times coeff(mag(cell_i))}
-\end{equation*}
-
-where $mag$ is the score based on relative magnitude: we give $1$ to cells whose
-probability should be ``very low'', and $4$ to cells whose probability should be
-``very high''. $coeff$ of a relative magnitude is a constant that is multiplied
-to the magnitude score. It helps to widen the gap between probabilities assigned
-to cells in a column, bearing different relative magnitudes.
-
-\subsection{Graph Manipulation}
-
-% TODO cite networkx 
-Here, we explain how we cut the big graph into a handful of small ones, and
-further preprocess them before turning each into a Bayesian network. We used
-\emph{networkx}'s implementation for each core algorithms: Kernighan-Lin
-bisection and cycle detection.
-
-\paragraph{Splitting Graphs}
-
-% TODO: self_question_n_answer.py가 interaction 한번에 얼마나 걸리는지를 측정해
-% 그래프로 그리기
-After we are done making the initial graph, we chop it down to small graphs of
-size under a certain threshold, which will later be converted into Bayesian
-networks. This breaking down is necessary since the time consumed during loopy
-belief propagation and D-separation algorithms, which will be discussed later
-in the next section, gets increasingly inefficient as the graph size increases. Since we are aiming
-to reduce the time for a single interaction under \emph{xx??} seconds, we
-decided that the optimal threshold for a graph is \emph{180??}. The algorithm
-for this task is described in figure \emph{??}. This algorithm relies heavily on
-the Kernighan-Lin partitioning algorithm, % TODO: should we cite the algorithm's paper?
-which partitions the given graph $G=(V, E)$ into two graphs $G_1=(V_1,E_1)$ and
-$G_2=(V_2, E_2)$, such that $V_1$ and $V_2$ are almost equal and the edges
-connecting $G_1$ and $G_2$ are minimized. % TODO: at least skim the Kernighan-Lin paper!
-% is it really 'minimized'??
-
-\paragraph{Decycling, and Controlling in-edges}
-
-Since Bayesian networks are directed acyclic graphs (DAGs), we need to eliminate
-all cycles before we turn the splitted graphs into Bayesian networks. We first
-use \emph{networkx}'s cycle
-detection algorithm which pinpoints the set of edges forming a cycle by
-searching the graph in a depth-manner for this task. We then randomly pick one of
-such edges causing a cycle and delete it. Repeatedly applying the two
-operations until the algorithm fails to detect a cycle, we transform the
-splitted graphs into DAGs.
-
-Next, we control the number of incoming edges of each node. It is already
-mentioned that the size of a node's CPT is exponential to the number of its
-parent nodes. To our empirical knowledge, if the number of incoming edges (hence
-the number of parent nodes) becomes more than 6, the process of converting the
-graph into a Bayesian network becomes drastically intractable. Therefore, we
-reduce the number of parents of such ``rich nodes'' by making the parents of the
-rich node shoot a similarity edge not to the rich node in question, but to some
-other node that is not yet rich.
-
-Also, we minimize the number of ``isolated nodes'' that have no incoming edges
-nor outgoing edges. Since these nodes' marginal probabilities are independent of
-those of any other nodes, their marginals never get updated if any other nodes'
-marginals get updated. Thus, they are one of the major factors that make the
-inference inefficient. We control the number of isolated nodes of a splitted
-graph by sticking the isolated node $n_1$ to a node $n_2$ of other graph if both
-were connected in the initial graph either by edge $(n_1, n_2)$ or $(n_2, n_1)$.
-
-After all these preprocessing, we are finally ready to turn chopped graphs into
-small, yet full-blown Bayesian networks. Each node corresponds to a random
-variable $\text{The taint specification of method} M$, whose possible values are
-$source$, $sink$, $sanitizer$, and $none$. Now, they are waiting for an external
-oracle to instantiate its value to one of these four.
-
-\subsection{Information Propagation}
-
-Here, we expound on the core inference algorithm. Inference on the Bayesian
-network is divided into two parts: local propagation and global propagation.
-Local propagations pass information given by the oracle within a single graph,
-whereas global propagations pass the information from one graph to another.
+\subsection{How SpecHunter works}

### 2021-04-15 My-Papers/SpecHunter/Codes/OverviewExample.java

@@ -1,0 +1,38 @@
+@SpringBootApplication
+public class RelationalData {
+
+    @Autowired
+    JdbcTemplate jdbcTemplate;
+    Logger log = LoggerFactory.getLogger(RelationalDataAccessApplication.class);
+
+    public static void main(String[] args) {
+        SpringApplication.run(RelationalDataAccessApplication.class, args);
+    }
+
+    public String create() {
+        Scanner scanner = new Scanner(System.in);
+        String name = scanner.nextLine();
+        return name;
+    }
+
+    public void run() throws Exception {
+        String name = create();
+        String sql = "INSERT INTO customers VALUES (" + name + ")";
+        jdbcTemplate.batchUpdate(sql);
+    }
+
+    public Map<String, Object> query() throws Exception {
+        Map<String, Object> results = jdbcTemplate.queryForMap("SELECT id, first_name, FROM customers WHERE first_name = ?", new Object[] { "John" });
+        return results;
+    }
+
+    public void printer(Map<String, Object> results) throws Exception {
+       Object elem = results.get("John");
+       log.info(elem);
+    }
+
+    public void bridge() throws Exception {
+        Map<String, Object> queryResult = query();
+        printer(queryResult);
+    }
+}

### 2021-04-15 My-Papers/SpecHunter/Codes/SimpleExample.java

@@ -1,0 +1,25 @@
+public int m1() {
+    return 1;
+}
+
+public int m2(int u1) {
+    return ++u1;
+}
+
+public void m3(int u2) {
+    System.out.println(u2);
+}
+
+public void f() {
+    int x = m1();
+    g(x);
+}
+
+public void g(int y) {
+    int z = m2(y);
+    h(z);
+}
+
+public void h(int w) {
+    m3(w);
+}

### 2021-04-15 My-Papers/SpecHunter/paper.tex
paper updates

--- 2021-04-01 My-Papers/SpecHunter/paper.tex
@@
 
-\section{Introduction}
-Taint analysis, whether static or dynamic, aims to find security vulnerabilities lurking
-in the given program. These vulnerabilities include SQL injection, cross-site
-scripting, and abused printf-arguments. They are typically formulated as a
-data flow starting from a `source' method to a `sink' method, without the
-flowing data being `sanitized' by a relevant method. For such search to be
-precise enough, the analyzer must first be told which methods are sources,
-sinks, sanitizers, or none of them. However, going through the codebase
-searching for imported APIs and labelling every one of them by hand quickly becomes tedious
-thing to do as the codebase gets larger.
+\input{introduction.tex}
 
-% TODO BibTeX을 쓸 줄 모르므로 일단 툴 이름으로 Reference로의 링크를 대신함
-% Boldface들을 BibTeX으로 바꿀 것.
-To aid such manpower, previous studies proposed methods such as supervised
-learning (\textbf{SuSI}, \textbf{SWAN}), and semi-supervised learning (\textbf{Seldon}, \textbf{Merlin}).
-However, works belonging to each camp suffers from their own limitations.
+\input{overview.tex}
 
-\paragraph{Shortcomings of Supervised Learning Camp.}
+\input{approach_details.tex}
 
-\textbf{SuSI} and \textbf{SWAN} both work in a similar way: they first train a learning model
-such as a support vector machine with the actual library codes implementing
-APIs. Here, the function bodies are interprocedurally analyzed with a Java
-static analyzer to get the vectors of feature values. Then, they take a whole
-library codebase into the pre-trained learning
-model, and get the mapping from all APIs in the library to their respective
-specifications. While they work nicely against libraries written in pure Java
-code such as Spring, they cannot work if a given application imports libraries
-written in other languages other than Java. This is because in order to extract
-the feature values they would have to be equipped with all the possible
-languages the libraries would be in, and this is practically difficult.
+\input{evaluation.tex}
 
-% TODO: add an additional shortcoming: features should also be updated if a new
-% library is provided
+\input{related_work.tex}
 
-\paragraph{Shortcomings of Semi-Supervised Learning Camp.}
+% Conclusion itself must be 
+\section{Conclusion}
 
-As a workaround to the above limitation, one can try a semi-supervised learning
-approach. The state-of-the-art belonging to this camp is \textbf{Seldon}.
-\textbf{Seldon} only takes the application code into consideration, thus it does
-not care which language the library is written in. So, for example, Seldon can
-figure out the label of an API function in a Python program, which is
-actually implemented in C++. However, Seldon suffers from a common problem of
-all machine-learning solutions, that it is largely dependent on quality dataset.
-In fact, the authors reports that \textbf{Seldon}'s precision dropped by 14
-percent-points by just providing half of the original specifications. Moreover,
-this problem is shared with supervised learning solutions, those are also
-data-driven solutions.
-% Seldon 논문의 부분을 인용하고 싶은데... 형식을 모르겠네
-% 해당 부분:
-% Q6: Impact of Seed Specification. We also evaluated Sel-
-% don’s precision for half the seed specification (considering
-% only odd line numbers in App. B). This significantly reduces
-% precision, by 14 percentage-points. Thus, we believe our
-% seed specification strikes a good balance between manual
-% effort and precision. We note that in the extreme case of an
-% empty seed specification, Seldon will predict 0 specifications,
-% because picking 0 for all variables is a trivial solution to its
-% constraint system.
-
-\paragraph{Our Tool: Real-Time Interactive Inference.}
-
-Our tool, SpecHunter, works in a different manner than data-driven
-approaches. Instead of training the model with some predetermined pairs of
-methods and their labels to predict other methods' labels, we analyze the given
-application to construct probabilistic graphical models of a certain type,
-called Bayesian networks. They are special in that they provide a model of
-conditional-probabilistic reasoning, which infers the marginal probabilities of
-each random variables when some of them are instantiated to a certain value by
-an external source. Therefore, we first determine a structure of a Bayesian network
-by running a static analysis on the given application code, and make the system ask
-the user, the external entity, for evidence. Then, SpecHunter picks the most
-influential node which has the most dependent nodes. This makes the interaction
-session both effective and efficient.
-
-The experiments show that SpecHunter effectively infers taint specifications for
-methods that are untold of its label, with \textbf{xx}\% precision when told only
-\textbf{17.7}\% of all APIs.
-
-\paragraph{Contributions.}
-
-\begin{itemize}
-  \item We provide SpecHunter
-  \item We provide src/sin/san/non ground truths
-  \item We provide a taint analyzer (is it possible?)
-  \item We make the tool open source (is it possible?)
-\end{itemize}
-
-\section{Overview}
-
-\paragraph{Motivation}
-
-Swan sucks: too much variance on its performance depending on dataset quality/quantity
-
-\subsection{Overview of our System}
-
-% 적당한 figure 하나 넣자
-
-Figure 1 shows the overall workflow of SpecHunter. Given a Java application's
-source code, SpecHunter labels all API methods provided by the library the application
-uses. There are three main issues regarding building an effective interactive system:
-namely, constructing the network, effectively propagating the evidence given from the
-oracle, and making the system scale to run on large input applications.
-% Question: Should we define what "API" means?
-
-\subsection{Network Construction}
-
-% Network Construction은 반드시 Scalability and Efficiency와 연관되게 되어 있다.
-% 그 점을 유념하면서 쓰자: 적절한 pointer 달아 주기.
-Here we describe how we represent the input java project into a graph form, which will
-later be turned into a series of Bayesian networks. We hope to create a graph G=(V, E),
-where V is the set of all methods used or defined in the given application, and E is a
-subset of V * V, whose elements are gathered in three different ways.
-
-First, there are data-flow-edges. We perform a variant of a data-flow analysis on the
-given input application to calculate lifetimes of all access paths found in the entire code.
-% 여기서 간단한 예제 넣어주기
-
-\begin{figure}[t]
-  \begin{lstlisting}
-
-    public int m1() {
-      return 1;
-    }
-
-    public int m2(int u1) {
-      return ++u1;
-    }
-
-    public void m3(int u2) {
-      System.out.println(u2);
-    }
-
-    public void f() {
-      int x = m1();
-      g(x);
-    }
-
-    public void g(int y) {
-      int z = m2(y);
-      h(z);
-    }
-
-    public void h(int w) {
-      m3(w);
-    }
-
-  \end{lstlisting}
-\caption{Example Java program with a data flow.}
-vspace{-0.6em}
-\label{fig:sca}
-\end{figure}
-
-Second, there are call-edges.
-
-Last but not least, there are similarity-edges.
-
-\subsection{Graph Splitting}
-
-\subsection{Information Propagation}
-
-\section{Evaluation}
-
-\subsection{RQs}
-\begin{itemize}
-  \item How effective is SH in finding src/sin/san?  % I am really really worried about this
-  \item How efficient is SH?
-  \item Interaction user-study % possible?
-\end{itemize}
-
-% why is this meaningful? (with/without comparison)
-% at least mention comparison
-
-\paragraph{Discussions}
-How well are propagations working? (Quant, Qualit) .
-How stable is SpecHunter over multiple iterations?
-\paragraph{Limitations}
-
-\paragraph{Threats to Validity.}
-
-\section{Related Work}
-
-\section{Conclusion}
+% TODO cite pomegranate in the BibTeX
 

### 2021-04-15 Code/BayesianNetwork/community_detection.py
bayesiannetwork updates

@@ -9,7 +9,7 @@ def compute_error(original_graph, graph_A, graph_B):
     return error_A+error_B
 
 
-def bisect_optimal(large_graph):
+def bisect_optimal(large_graph, mother_graph):
     acc = []
     for _ in range(100):
         A, B = bisect(large_graph)
@@ -21,34 +21,36 @@ def bisect_optimal(large_graph):
     return best_A, best_B
 
 
-def bisect_naive(large_graph):
+def bisect_naive(large_graph, mother_graph):
     """bisect the given graph"""
     node_set_A, node_set_B = community.kernighan_lin_bisection(large_graph.to_undirected())
-    naively_recovered_A = naive_recover_graph(node_set_A, large_graph)
-    naively_recovered_B = naive_recover_graph(node_set_B, large_graph)
+    naively_recovered_A = naive_recover_graph(node_set_A, large_graph, mother_graph)
+    naively_recovered_B = naive_recover_graph(node_set_B, large_graph, mother_graph)
 
     return naively_recovered_A, naively_recovered_B
 
 
-def bisect(large_graph):
+def bisect(large_graph, mother_graph):
     """bisect the given graph"""
     node_set_A, node_set_B = community.kernighan_lin_bisection(large_graph.to_undirected())
-    naively_recovered_A = naive_recover_graph(node_set_A, large_graph)
-    naively_recovered_B = naive_recover_graph(node_set_B, large_graph)
+    naively_recovered_A = naive_recover_graph(node_set_A, large_graph, mother_graph)
+    naively_recovered_B = naive_recover_graph(node_set_B, large_graph, mother_graph)
 
     recovered_A, recovered_B = minimize_isolated(naively_recovered_A, naively_recovered_B, large_graph)
     return recovered_A, recovered_B
 
 
-def naive_recover_graph(small_node_set, original_graph):
+def naive_recover_graph(small_node_set, original_graph, mother_graph):
     """small_node_set에서부터 small_graph를 복원해 낸다."""
-    edges = original_graph.edges
     # 각 엣지 안에 들어 있는 노드들이 small_node_set의 원소인지를 판단하는 것으로 충분하다.
     filterfunc = lambda edge: edge[0] in small_node_set and edge[1] in small_node_set
-    small_graph_edges = list(filter(filterfunc, edges))
+    small_graph_edges = list(filter(filterfunc, mother_graph.edges))
     G = nx.DiGraph()
[…]

### 2021-04-15 Code/BayesianNetwork/create_node.py

@@ -25,11 +25,7 @@ PROJECT_ROOT_DIR = retrieve_path()
 
 
 def flatten(ll):
-    flat_list = []
-    for sublist in ll:
-        for item in sublist:
-            flat_list.append(item)
-    return flat_list
+    return [elem for lst in ll for elem in lst]
 
 
 def filtermethod(string):

### 2021-04-15 Code/BayesianNetwork/deal_with_poor_nodes.py

@@ -1,9 +1,17 @@
-import modin.pandas as pd
+# import modin.pandas as pd
+import pandas as pd
 import networkx as nx
 import glob
 
+import pickle                   # TEMP
+
 from split_underlying_graph import decycle
 from functools import partial, update_wrapper
+from pandarallel import pandarallel
+from itertools import product
+
+
+pandarallel.initialize()
 
 
 def find_poor_node_files():
@@ -16,7 +24,7 @@ def find_poor_node_files():
 
 DF_EDGES = pd.read_csv("df.csv", index_col=0)
 CALL_EDGES = pd.read_csv("callg.csv", index_col=0)
-SIM_EDGES = pd.read_csv("sim.csv", index_col=0)
+SIM_EDGES = pd.read_csv("pairwise_sims.csv", index_col=0)
 
 
 # Methods ==========================================
@@ -32,78 +40,102 @@ def create_graph_without_edges(poor_nodes):
 
 
 def add_df_edges(G):
-    mapfunc = lambda row: row['id1'] in G.nodes and row['id2'] in G.nodes
+    """Given a graph G whose edge set E is empty, add DF edges to the nodes of G."""
+    nodes_df = pd.DataFrame(G.nodes)
 
-    # making original dataframe manageable by dropping irrelevant rows and columns
-    small_df_edges = DF_EDGES[['id1', 'id2']]
-    bool_df = small_df_edges.apply(mapfunc, axis=1)
-    small_df_edges['leave'] = bool_df
-    small_df_edges = small_df_edges[small_df_edges.leave != False]
+    # Warning: SQL Magic ahead!
 
-    # adding edges row by row
-    for rowtuple in small_df_edges.itertuples(index=False):
-        G.add_edge(rowtuple[0], rowtuple[1])  # id1, id2 respectively
+    # The Cartesian Product.
+    carpro = nodes_df.merge(nodes_df, how="cross")
+    carpro.columns = ["id1", "id2"]
+
+    # perform a left-join
+    left_join = pd.merge(carpro, DF_EDGES, on=["id1", "id2"], how="left", indicator="exists?")
+
+    # only select "id1", "id2", and "exists?"
+    projected = left_join.filter(["id1", "id2", "exists?"])
+
+    # only select the rows which exists in both DF_EDGES and carpro
+    selected = projected[projected["exists?"] == "both"]
+
+    # drop the column from sample_nodes_df
[…]

### 2021-04-15 Code/BayesianNetwork/deal_with_poor_nodes_new.py

@@ -1,0 +1,39 @@
+import pandas as pd
+import networkx as nx
+import glob
+
+import pickle                   # TEMP
+
+from split_underlying_graph import decycle
+from functools import partial, update_wrapper
+from pandarallel import pandarallel
+from itertools import product
+
+import make_underlying_graph
+import split_underlying_graph
+
+
+def find_poor_node_files():
+    return glob.glob("*_poor")
+
+
+def create_graph_without_edges(poor_nodes):
+    g = nx.DiGraph()
+    for poor_node in poor_nodes:
+        g.add_node(poor_node)
+    return g
+
+
+def main():
+    POOR_NODE_FILES = find_poor_node_files()
+    nodes = []
+    for poor_node_file in POOR_NODE_FILES:
+        G = nx.read_gpickle(poor_node_file)
+        nodes += list(G.nodes)
+
+    edgeless_graph = create_graph_without_edges(nodes)
+
+    mother_graph = make_underlying_graph.parameterized_main(edgeless_graph)
+    splitted_graphs = split_underlying_graph.parameterized_main(mother_graph)
+
+    return splitted_graphs

### 2021-04-15 Code/BayesianNetwork/deal_with_rich_nodes.py

@@ -1,29 +1,22 @@
 import networkx as nx
 import copy
+import pandas as pd
 from community_detection import isolated_nodes, rich_nodes
 from create_node import process
 from split_underlying_graph import decycle
 
 
-def scoring_function(info1, info2):
-    score = 0
-    if info1[0] == info2[0]:  # The two methods belong to the same class
-        score += 10
-    if info1[1] == info2[1]:  # The two methods have a same return type
-        score += 10
-    if (info1[2] in info2[2]) or (info2[2] in info1[2]) or \
-       (info1[2][0:2] == info2[2][0:2]) or (info1[2][0:2] == info2[2][0:2]):
-        score += 10  # The two methods start with a same prefix
-    if info1[3] == info2[3]:  # The two methods have a same input type
-        score += 10
-    return score
+SIMS = pd.read_csv("pairwise_sims.csv", index_col=0)
+
+
+def row_isin_dataframe(node1, node2):
+    return not SIMS[(SIMS["id1"] == node1) &
+                    (SIMS["id2"] == node2)].empty
 
 
 def can_stick_node_to(G, from_node, to_node):
     """node1을 node2에 붙일 수 있는가?"""
-    from_node_info = process(from_node)
-    to_node_info = process(to_node)
-    if scoring_function(from_node_info, to_node_info) > 20 and\
+    if row_isin_dataframe(from_node, to_node) and\
        len(G.in_edges(nbunch=to_node)) < 6:
         return True
     else:
@@ -52,7 +45,7 @@ def relocate_stashed_nodes(G, stash):
     for stashed_node in stash:
         for other_node in set(G.nodes)-set(stash):
             if can_stick_node_to(G, stashed_node, other_node):
-                G.add_edge(stashed_node, other_node)
+                G.add_edge(stashed_node, other_node, kind="sim")
                 break
 
 
@@ -84,7 +77,7 @@ def decompose_rich_node(G, rich_node):
         popped_node = edge_shooters.pop()
         stickable_node = find_stickable_node(G, popped_node, candidates, rich_node)
         if stickable_node is not None:
-            G.add_edge(popped_node, stickable_node)
+            G.add_edge(popped_node, stickable_node, kind="sim")
         else:
             stash.append(popped_node)
 

### 2021-04-15 Code/BayesianNetwork/make_BN.py

@@ -5,11 +5,22 @@ import networkx as nx
 import itertools as it
 import deal_with_rich_nodes
 import copy
+import modin.pandas as pd
+import random
 
 from pomegranate import *
 from make_underlying_graph import find_root, find_edge_labels
 from make_CPT import *
 from community_detection import isolated_nodes
+from pandarallel import pandarallel
+
+
+DF_EDGES = pd.read_csv("df.csv", index_col=0)[["id1", "id2"]]
+CALL_EDGES = pd.read_csv("callg.csv", index_col=0)[["id1", "id2"]]
+SIM_EDGES = pd.read_csv("pairwise_sims.csv", index_col=0)[["id1", "id2"]]
+
+
+mother = nx.read_gpickle("graph_for_reference")
 
 
 # Methods for BNs ====================================
@@ -29,7 +40,7 @@ def create_internal_node_for_BN(graph_for_reference, node_name, BN, prev_states)
     """BN에 internal node를 만들어 추가한다."""
     labels = [1, 2, 3, 4]       # src, sin, san, non
     parents_and_edges = find_edge_labels(graph_for_reference, node_name)
-    parents = list(map(lambda tup: tup[0], parents_and_edges)) 
+    parents = list(map(lambda tup: tup[0], parents_and_edges))
     edges = list(map(lambda tup: tup[1], parents_and_edges))
     parent_dist = list(map(lambda state: state.distribution, prev_states))
     probs = create_CPT(edges).transpose().flatten()
@@ -85,7 +96,7 @@ def add_edge_to_BN(graph_for_reference, BN, currently_defined_states):
 
 def init_BN(graph_for_reference):
     BN = BayesianNetwork("Interactive Inference of Taint Method Specifications")
-    root_states = create_roots_for_BN(graph_for_reference, BN) 
+    root_states = create_roots_for_BN(graph_for_reference, BN)
     states = create_internal_nodes_for_BN(graph_for_reference, BN, root_states)
     add_edge_to_BN(graph_for_reference, BN, states)
     BN.bake()
@@ -94,6 +105,7 @@ def init_BN(graph_for_reference):
 
 # Methods for Graphs =================================
 # ====================================================
+
 
 def exclude_rich(G):
     """incoming edge가 너무 많은 노드들을 그래프에서 삭제한다."""
@@ -152,38 +164,32 @@ def get_maximum_in_edges(G):
     if num_of_in_edges == []:
         return "empty graph"
     return max(num_of_in_edges)
-        
+
 
[…]

### 2021-04-15 Code/BayesianNetwork/make_CPT_lookup_table.py

@@ -8,6 +8,10 @@ SECOND_WEIGHT = 4
 THIRD_WEIGHT = 64
 FOURTH_WEIGHT = 256
 
+# FIRST_WEIGHT = 1
+# SECOND_WEIGHT = 1
+# THIRD_WEIGHT = 1
+# FOURTH_WEIGHT = 1
 
 def weight_mag(mag):
     """주어진 mag에 weight parameter를 곱한다."""

### 2021-04-15 Code/BayesianNetwork/pairwise_similarity.py

@@ -424,7 +424,7 @@ def get_similar_rows_score(this_row):
 
     scores_series = FEATURE_VECTORS_other.apply(scoring_function, axis=1)
 
-    threshold = 15              # TEMP
+    threshold = 17              # TEMP
 
     scores_series_above_thres = scores_series.where(lambda score: (score > threshold)).dropna()
     converted_to_dict = scores_series_above_thres.to_dict()
@@ -443,16 +443,16 @@ def get_similar_rows_ranking(this_row):
 
     scores_series = FEATURE_VECTORS_other.apply(scoring_function, axis=1)
 
-    threshold_score = 15
-    threshold_rank = 5
+    threshold_score = 17        # TEMP
+    # threshold_rank = 5
 
     scores_series_above_thres = scores_series.where(lambda score: (score > threshold_score)).dropna()
 
     converted_to_dict = scores_series_above_thres.to_dict()
     sorted_by_val = sort_dict_by_value_rev(converted_to_dict)
-    cut = dict(sorted_by_val[:threshold_rank])
+    # cut = dict(sorted_by_val[:threshold_rank])
 
-    return keymap(fetch_methname_by_id, cut)
+    return keymap(fetch_methname_by_id, converted_to_dict)
 
 
 def score_all_rows():
@@ -515,6 +515,11 @@ def main():
 
     pairwise_sims = no_symmetric(flatten_sim_df(score_all_rows()))
     pairwise_sims.to_csv("pairwise_sims.csv", mode="w+")
+
+    # now, concat DF, CALL, SIM and output them to a single csv
+    concatted = pd.concat([DF, CALL, pairwise_sims])
+
+    concatted.to_csv("edges.csv", mode="w+")
 
     print("elapsed time:", time.time()-start)
 

### 2021-04-15 Code/BayesianNetwork/self_question_n_answer_new.py

@@ -1,48 +1,38 @@
 import csv
-import itertools as it
 import json
-import os
 import os.path
 import random
 import time
 import argparse
 import re
-
-import pickle # TEMP
-from sys import exit
-
 import make_BN
-import matplotlib.axes as axes
-import matplotlib.patches as ptch
 import matplotlib.pyplot as plt
-import modin.pandas as pd
 import pandas as pd
 import networkx as nx
 import numpy as np
 import transfer_knowledge
-import deal_with_poor_nodes
+import networkx.algorithms as nxalg
 
 from datetime import datetime
-from create_node import process
-from make_CPT import *
-from make_underlying_graph import find_edge_labels
 from matplotlib.ticker import MaxNLocator
-from pomegranate import *
-from scrape_oracle_docs import *
-from toolz import valmap
 from functools import reduce
 from copy import deepcopy
+from make_BN import tame_rich
+from community_detection import rich_nodes
 
-from traceback_with_variables import activate_in_ipython_by_import, printing_exc
+# from traceback_with_variables import activate_in_ipython_by_import, printing_exc
+
+import pickle                   # TEMP
+
+# Constants ========================================
+# ==================================================
 
 
 parser = argparse.ArgumentParser()
 parser.add_argument("solution_file", help="path to the solution file. input 'None' if you don't have any.",
                     type=str)
-args = parser.parse_args()
-
-# Constants ========================================
-# ==================================================
+# args = parser.parse_args()
+args = parser.parse_args(["solutions/solution_decision.json"])  # For the REPL
 
 def retrieve_path():
     """paths.json을 읽고 path를 가져온다."""
@@ -52,7 +42,7 @@ def retrieve_path():
 
 PROJECT_ROOT_DIR = retrieve_path()
 
-if args.solution_file != "None":
+if args.solution_file != "None" or args.solution_file != "none":
     with open(args.solution_file, "r+") as solution_file:
         SOLUTION = json.load(solution_file)
 else:
@@ -77,16 +67,20 @@ CALL_EDGES = no_reflexive(map(lambda lst: (lst[5], lst[10]), list(call_reader)[1
 SIM_EDGES = no_reflexive(map(lambda lst: (lst[5], lst[10]), list(sim_reader)[1:]))
 
 WINDOW_SIZE = 4
-GLOBAL_GRAPH = nx.read_gpickle("graph_for_reference")
 
 with open(PROJECT_ROOT_DIR+"skip_func.txt", "r+") as skip_func:
     skip_funcs = skip_func.readlines()
[…]

### 2021-04-15 Code/BayesianNetwork/split_underlying_graph.py

@@ -147,23 +147,23 @@ def find_optimal_graph_size(G):
         max_graph_size -= 1
 
 
-def split_large_graph(G, max_graph_size):
+def split_large_graph(G, max_graph_size, mother_graph):
     worklist = [G]
     acc = []
     while worklist != []:
-        print(list(map(lambda graph: len(graph.nodes), worklist)))
+        # print(list(map(lambda graph: len(graph.nodes), worklist)))
         target = worklist.pop()
         if len(target.nodes) <= max_graph_size:
             acc.append(target)
         else:
-            small1, small2 = bisect(target)
-            print(len(isolated_nodes(small1)))
-            print(len(isolated_nodes(small2)))
+            small1, small2 = bisect(target, mother_graph)
+            # print(len(isolated_nodes(small1)))
+            # print(len(isolated_nodes(small2)))
 
             if len(small1.nodes) == 0 or len(small2.nodes) == 0:
-                small1, small2 = bisect_naive(target)  # give up minimizing isolated nodes
-                print(len(isolated_nodes(small1)))
-                print(len(isolated_nodes(small2)))
+                small1, small2 = bisect_naive(target, mother_graph)  # give up minimizing isolated nodes
+                # print(len(isolated_nodes(small1)))
+                # print(len(isolated_nodes(small2)))
             worklist.append(small1)
             worklist.append(small2)
     # print("acc: ", list(map(lambda graph: len(graph.nodes),acc)))
@@ -182,7 +182,7 @@ def main():
             masked_graph = mask_graph(graph_for_reference, all_methods)
             nx.write_gpickle(masked_graph, graph_name+"_graph")
             # optimal_max_graph_size = find_optimal_graph_size(masked_graph)
-            small_graphs = split_large_graph(masked_graph, 180)
+            small_graphs = split_large_graph(masked_graph, 150, graph_for_reference)
             i = 0
             for small_graph in small_graphs:
                 decycle(small_graph)
@@ -191,7 +191,7 @@ def main():
         nx.write_gpickle(callgraph, "callgraph")
 
     else:                       # There are no .jar files in PROJECT_ROOT
-        small_graphs = split_large_graph(graph_for_reference, 180)
+        small_graphs = split_large_graph(graph_for_reference, 150, graph_for_reference)
         graph_name = os.path.basename(os.path.normpath(PROJECT_ROOT_PATH))
         i = 0
[…]
